### Method

#### Participants

##### Power analysis {#power-analysis-alignment-8}

A power analysis was conducted through simulation of the effects hypothesised in
Experiment 3 (and the simple effects implied by them). The simulated data used
the same regression coefficients as Experiment 2 for the explicit condition, no
effects for the implicit condition (as shown in
Figure \@ref(fig:plot-simulation-alignment-8)), and the intercept and residual
variance of Experiment 2. The null effects were analysed using the two one-sided
tests (TOST) procedure, or *equivalence* testing [@lakens2018], and setting the
smallest effect size of interest to the smallest difference that leads to a
significant equivalence between low and high implicit reliability for low
alignment in Experiment 8 (see Appendix \@ref(alignment-7)).
Figure \@ref(fig:power-curve-alignment-8) shows the resulting power curve. The
analysis suggests a total sample size of `r alignment8::power$n_total`
(`r alignment8::power$n` $\cdot$ 4).

\newpage

\blandscape

(ref:power-curve-alignment-8) Alignment Experiment 3 power curve. Labels indicate lowest sample size above 80% power.

```{r power-curve-alignment-8, fig.width = 13, fig.height = 7, fig.cap = "(ref:power-curve-alignment-8)"}
alignment8::power$power_curve
```

\elandscape

\newpage


#### Materials

##### Instructions {#instructions-materials-alignment-8-appendix}

Figures \@ref(fig:instructions-reliability-explicit-materials-alignment-8)
and \@ref(fig:instructions-reliability-implicit-materials-alignment-8) show the
instructions for the verbal and numerical reliability conditions, respectively.

(ref:instructions-reliability-explicit-materials-alignment-8) Experiment 3 verbal reliability instructions. Border added for clarity.

```{r instructions-reliability-explicit-materials-alignment-8, fig.cap = "(ref:instructions-reliability-explicit-materials-alignment-8)"}
file.path(
  materials_alignment_8,
  "instructions_reliability_type_explicit.png"
) %>%
  image_read() %>%
  image_trim() %>%
  image_border(color = "white", geometry = "5x5") %>%
  image_border(color = "black", geometry = "5x5")
```

(ref:instructions-reliability-implicit-materials-alignment-8) Experiment 3 numerical reliability instructions. Border added for clarity.

```{r instructions-reliability-implicit-materials-alignment-8, fig.cap = "(ref:instructions-reliability-implicit-materials-alignment-8)"}
file.path(
  materials_alignment_8,
  "instructions_reliability_type_implicit.png"
) %>%
  image_read() %>%
  image_trim() %>%
  image_border(color = "white", geometry = "5x5") %>%
  image_border(color = "black", geometry = "5x5")
```

##### Interstitial display {#interstitial-materials-alignment-8}

Figure \@ref(fig:interstitial-materials-alignment-8) shows an example of an
interstitial display.

(ref:interstitial-materials-alignment-8) An example of an interstitial display in Experiment 3. Border added for clarity.

```{r interstitial-materials-alignment-8, fig.cap = "(ref:interstitial-materials-alignment-8)"}
file.path(
  materials_alignment_8,
  "interstitial_1.png"
) %>%
  image_read() %>%
  image_trim() %>%
  image_border(color = "white", geometry = "5x5") %>%
  image_border(color = "black", geometry = "5x5")
```
