### Method

#### Materials

##### Instructions

Participants were shown the instructions in
Figure \@ref(fig:instructions-materials-aggregation-1).

(ref:instructions-materials-aggregation-1) Experiment 1 instructions.

```{r instructions-materials-aggregation-1, fig.cap = "(ref:instructions-materials-aggregation-1)"}
file.path(
  materials_aggregation_1,
  "instructions.png"
) %>%
  image_read() %>%
  image_trim() %>%
  image_border(color = "white", geometry = "5x5") %>%
  image_border(color = "black", geometry = "5x5")
```

##### Outcome distribution decision

Figure \@ref(fig:project-choice-aggregated-aggregation-1) shows the outcome
distribution display that participants saw in Experiment 1.

(ref:project-choice-aggregated-aggregation-1) The outcome distribution of the 10 gambles used in Experiment 1.

```{r project-choice-aggregated-aggregation-1, fig.cap = "(ref:project-choice-aggregated-aggregation-1)"}
file.path(
  materials_aggregation_1,
  "project_choice_aggregated.png"
) %>%
  image_read() %>%
  image_trim() %>%
  image_border(color = "white", geometry = "5x5") %>%
  image_border(color = "black", geometry = "5x5")
```

##### Follow-up gambles {#follow-up-materials-aggregation-1-appendix}

###### Negative EV gambles

It was important to make sure that participants were generally making decisions
that were in line with EV theory and that the sample was not abnormally risk
tolerant. As such, participants saw two project decisions that had a negative
EV. Out of the `r descriptives_aggregation_1$total*2` negative EV gambles
included (two per participant), all but `r results_aggregation_1$neg_sum_apa`
were rejected.

###### @samuelson1963 gambles

Participants saw the original @samuelson1963 gamble, were asked whether they
would accept 10 of that gamble, and whether they would accept those 10 given the
associated outcome distribution. They then saw the same three questions, but
using outcome magnitudes that were similar to the ones in the risky investment
task. That is, $100 million instead of $100.

###### @redelmeier1992 gambles

Participants saw the same three types of gambles (single, 10, and aggregated),
but with the values from the gambles that were used by @redelmeier1992.
