### Method

#### Materials

##### Instructions {#instructions-materials-aggregation-1-appendix}

Participants were shown the instructions in
Figure \@ref(fig:instructions-materials-aggregation-1).

(ref:instructions-materials-aggregation-1) Experiment 1 instructions.

```{r instructions-materials-aggregation-1, fig.cap = "(ref:instructions-materials-aggregation-1)"}
here(
  materials_aggregation_1,
  "instructions.png"
) %>%
  image_read() %>%
  image_trim()
```

##### Outcome distribution decision {#outcome-distribution-materials-aggregation-1-appendix}

Figure \@ref(fig:project-choice-aggregated-aggregation-1) shows the outcome
distribution display that participants saw in Experiment 1.

(ref:project-choice-aggregated-aggregation-1) The outcome distribution of the 10 gambles used in Experiment 1.

```{r project-choice-aggregated-aggregation-1, fig.cap = "(ref:project-choice-aggregated-aggregation-1)"}
here(
  materials_aggregation_1,
  "project_choice_aggregated.png"
) %>%
  image_read() %>%
  image_trim()
```

##### Follow-up gambles {#follow-up-materials-aggregation-1-appendix}

###### Negative EV gambles

I wanted to make sure that participants were generally making decisions that
were in line with EV theory and that the sample was not abnormally risk
tolerant. As such, I presented participants two project decisions that had a
negative EV. Out of the `r descriptives_aggregation_1$total*2` negative EV
gambles included (two per participant), all but
`r results_aggregation_1$neg_sum_apa` were rejected.

###### @samuelson1963 gambles

I showed participants the original @samuelson1963 gamble, asked them whether
they would accept 10 of that gamble, and whether they would accept those 10
given the associated outcome distribution. I then showed them the same three
questions, but using outcome magnitudes that were similar to the ones in the
risky investment task. That is, instead of $100, $100 million.

###### @redelmeier1992 gambles

I then showed participants the same three types of gambles (single, 10, and
aggregated), but with the values from the gambles that were used by
@redelmeier1992.
