### Method

#### Participants

`r descriptives_aggregation_3$apa` Table \@ref(tab:condition-allocation-aggregation-3)
shows the between-subjects condition allocation.

```{r condition-allocation-aggregation-3}
descriptives_aggregation_3$condition_allocation_table %>%
  apa_table("Experiment 3 group allocation.")
```

#### Materials

##### Instructions

Participants were shown the same instructions as in
[Experiment 1](#instructions-materials-aggregation-1).

##### Risky investment task {#task-aggregation-3}

Participants saw displays with the same gamble values as those in
[Experiment 2](#task-aggregation-2), but with some changes in wording and
sentence structure. I kept the same gamble information, but added extra prose
describing the projects and randomised the order of the sentences, so that the
descriptions would not appear so similar. See
Figure \@ref(fig:project-choice-aggregation-3) for an example.

(ref:project-choice-aggregation-3) An example of a project display in Experiment 3.

```{r project-choice-aggregation-3, fig.cap = "(ref:project-choice-aggregation-3)"}
here(
  materials_aggregation_3,
  "project_choice_oil-well.png"
) %>%
  image_read() %>%
  image_trim()
```

The similarity manipulation was as in Experiment 1. However, here I varied
project domain so that in the high similarity condition participants saw one of
the ten project domains.

##### Follow-up {#follow-up-aggregation-3}

The follow-up questions were similar to those in
[Experiment 2](#follow-up-aggregation-2), except in the portfolio number
question I added the number of projects that they saw (10). Further, I added a
question asking how many projects participants were expecting to see at the
beginning of the experiment (see
Figure \@ref(fig:project-expectation-aggregation-3)).

(ref:project-expectation-aggregation-3) Experiment 3 project expectation question.

```{r project-expectation-aggregation-3, fig.cap = "(ref:project-expectation-aggregation-3)"}
here(
  materials_aggregation_3,
  "project_expectation.png"
) %>%
  image_read() %>%
  image_trim()
```

#### Procedure

Participants responded to demographic questions, read the instructions, and
completed the risky investment task in their respective conditions. After seeing
the individual projects, participants were then asked the four follow-up
questions.
