### Method

#### Participants

`r descriptives_aggregation_3$apa` Table \@ref(tab:condition-allocation-aggregation-3)
shows the allocation of participants to the different conditions.

```{r condition-allocation-aggregation-3}
descriptives_aggregation_3$condition_allocation_table %>%
  apa_table("Experiment 3 group allocation.")
```

#### Materials

##### Instructions

Participants were shown the same instructions as in Experiment 1 (see
Section \@ref(instructions-materials-aggregation-1)).

##### Risky Investment Task {#task-aggregation-3}

Participants saw displays with the same gamble values as those in Experiment 2
(see Section \@ref(task-aggregation-2)), but with some changes in wording and
sentence structure. The gamble information was the same, but extra prose was
added to describe the projects. Further, the order of the sentences was
randomised, so that the descriptions would not appear so similar. See
Figure \@ref(fig:project-choice-aggregation-3) for an example.

(ref:project-choice-aggregation-3) An example of a project display in Experiment 3.

```{r project-choice-aggregation-3, fig.cap = "(ref:project-choice-aggregation-3)"}
file.path(
  materials_aggregation_3,
  "project_choice_oil-well.png"
) %>%
  image_read() %>%
  image_trim() %>%
  image_border(color = "white", geometry = "5x5") %>%
  image_border(color = "black", geometry = "5x5")
```

The similarity manipulation was as in Experiment 1. However, project domain was
varied so that in the high similarity condition participants saw one of ten
project domains.

##### Follow-up {#follow-up-aggregation-3}

The follow-up questions were similar to those in Experiment 2 (see
Section \@ref(follow-up-aggregation-2)), except in the portfolio number question
participants were also shown the total number of projects that they saw (10).
Further, another question was added, asking how many projects participants were
expecting to see at the beginning of the experiment (see
Figure \@ref(fig:project-expectation-aggregation-3)).

(ref:project-expectation-aggregation-3) Experiment 3 project expectation question.

```{r project-expectation-aggregation-3, fig.cap = "(ref:project-expectation-aggregation-3)"}
file.path(
  materials_aggregation_3,
  "project_expectation.png"
) %>%
  image_read() %>%
  image_trim() %>%
  image_border(color = "white", geometry = "5x5") %>%
  image_border(color = "black", geometry = "5x5")
```

#### Procedure

Participants read the instructions and completed the risky investment task in
their respective conditions. After seeing the individual projects, participants
were then asked the four follow-up questions.
