### Results

#### Project investment

The project investment data were analysed as in Experiment 2 (see
Section \@ref(results-aggregation-2)).
Figures \@ref(fig:plot-aggregation-3-choice)
and \@ref(fig:plot-aggregation-3-proportion) show the choice and proportion
data, respectively. The difference between similarity conditions was not
significant, both in the logistic regression
`r results_aggregation_3$choice$full_result[[2]]`, and in the t-test,
`r results_aggregation_3$proportion`.

(ref:plot-aggregation-3-choice) Mean project acceptance for the similarity effect.

```{r plot-aggregation-3-choice, fig.cap = "(ref:plot-aggregation-3-choice)"}
plot_aggregation_3$choice_binary
```

(ref:plot-aggregation-3-proportion) Mean proportion of project acceptance for the similarity effect.

```{r plot-aggregation-3-proportion, fig.cap = "(ref:plot-aggregation-3-proportion)"}
plot_aggregation_3$choice_proportion
```

Further, Figure \@ref(fig:plot-aggregation-3-choice-trials) shows the choice
data as a function of the order of the project in the sequence. As
Table \@ref(tab:similarity-project-order) shows, there were no main effects or
interactions.

(ref:plot-aggregation-3-choice-trials) Mean project acceptance by similarity and trial.

```{r plot-aggregation-3-choice-trials, fig.cap = "(ref:plot-aggregation-3-choice-trials)"}
plot_aggregation_3$choice_trials
```

```{r similarity-project-order}
results_aggregation_3$similarity_project_order$table %>%
  apa_table("Logistic regression table of project acceptance by similarity and trial.")
```

#### Follow-up

##### Project expectation

Participants were asked how many projects they expected to see. As
Figure \@ref(fig:plot-aggregation-3-project-expectation) shows, the difference
between similarity conditions was not significant,
`r results_aggregation_3$project_expectation`.

(ref:plot-aggregation-3-project-expectation) Number of projects participants expected to see, by similarity.

```{r plot-aggregation-3-project-expectation, fig.cap = "(ref:plot-aggregation-3-project-expectation)"}
plot_aggregation_3$project_expectation
```

##### Project number

Participants were asked how many projects they thought they saw.
Figure \@ref(fig:plot-aggregation-3-project-number) shows that overall people
correctly estimate the number of projects.

(ref:plot-aggregation-3-project-number) Number of projects participants reported seeing, by similarity.

```{r plot-aggregation-3-project-number, fig.cap = "(ref:plot-aggregation-3-project-number)"}
plot_aggregation_3$project_number
```

##### Portfolio choice - binary

Participants were then asked if they would rather invest in all or none of the
projects. As Figure \@ref(fig:plot-aggregation-3-portfolio-binary) shows, those
in the low similarity condition were significantly more likely to want to invest
in all of the projects,
`r results_aggregation_3$portfolio_binary$full_result[[2]]`.

(ref:plot-aggregation-3-portfolio-binary) Mean choice of investing in all 10 projects for the similarity effect.

```{r plot-aggregation-3-portfolio-binary, fig.cap = "(ref:plot-aggregation-3-portfolio-binary)"}
plot_aggregation_3$portfolio_binary
```

##### Portfolio choice - number

Subsequently, participants were asked how many projects they would invest in out
of the 10 that they saw. As
Figure \@ref(fig:plot-aggregation-3-portfolio-number) shows, the difference
between similarity conditions was not significant,
`r results_aggregation_3$portfolio_number`.

(ref:plot-aggregation-3-portfolio-number) Mean number of projects chosen in the follow-up for the similarity effect.

```{r plot-aggregation-3-portfolio-number, fig.cap = "(ref:plot-aggregation-3-portfolio-number)"}
plot_aggregation_3$portfolio_number
```

#### Gambles

Figures \@ref(fig:plot-aggregation-3-trials)
and \@ref(fig:plot-aggregation-3-gamble-values) show the
overall people seemed to prefer gambles with higher probabilities of gain,
sometimes regardless of expected value or value of the gain.

(ref:plot-aggregation-3-trials) Mean project acceptance for the 10 gambles. The format of the labels indicate: (gain probability, gain value; loss probability, loss value).

```{r plot-aggregation-3-trials, fig.cap = "(ref:plot-aggregation-3-trials)"}
plot_aggregation_3$trials
```

(ref:plot-aggregation-3-gamble-values) Mean project acceptance for the gambles'
expected value, positive probability, and positive outcome.

```{r plot-aggregation-3-gamble-values, fig.cap = "(ref:plot-aggregation-3-gamble-values)"}
plot_aggregation_3$gamble_values
```
