### Method

#### Participants

`r descriptives_alignment_6$apa` Table \@ref(tab:condition-allocation-alignment-6)
shows the between-subjects condition allocation.

```{r condition-allocation-alignment-6}
descriptives_alignment_6$condition_allocation_table %>%
  apa_table("Experiment 7 group allocation.")
```

#### Materials

The materials were similar to Experiment 3, as the same laptop displays were
used, but I added the *Cash inflow range* row to the table (see
Figure \@ref(fig:projects-alignment-6)). Further, participants in the No Hint
condition saw the same instructions as in Experiment 3, those in the Salience
Only condition saw the instructions along with a sentence that draws attention
to the *Cash inflow range* row, and those in the Salience + Hint condition saw
the instructions along with a specific description of how to use the variance
information in their allocation decisions.

(ref:projects-alignment-6) The projects display.

```{r projects-alignment-6, fig.cap = "(ref:projects-alignment-6)"}
here(
  materials_alignment_6,
  "alignment_high_reliability_amount_high.png"
) %>%
  image_read() %>%
  image_trim()
```

#### Procedure

Participants completed a demographics page, read the instruction page as per
their Hint condition, and then proceeded to complete one set of allocations.

