### Method

#### Participants

`r descriptives_alignment_6$apa` Table \@ref(tab:condition-allocation-alignment-6)
shows the between-subjects condition allocation.

```{r condition-allocation-alignment-6}
descriptives_alignment_6$condition_allocation_table %>%
  apa_table("Experiment 7 group allocation.")
```

#### Instructions

As seen in Figure \@ref(fig:instructions-no-hint-alignment-6), participants in
the no hint condition saw the same instructions as in Experiment 1. As seen in
Figure \@ref(fig:instructions-salience-only-alignment-6), those in the salience
only condition saw the instructions along with a sentence that drew attention to
the *Cash inflow range* row. As seen in
Figure \@ref(fig:instructions-salience-hint-alignment-6), those in the
salience + hint condition saw the instructions along with a specific description
of how to use the variance information in their allocation decisions.

(ref:instructions-no-hint-alignment-6) Instructions for the no hint condition. Border added for clarity.

```{r instructions-no-hint-alignment-6, fig.cap = "(ref:instructions-no-hint-alignment-6)"}
file.path(
  materials_alignment_6,
  "instructions_no_hint.png"
) %>%
  image_read() %>%
  image_contrast() %>%
  image_trim() %>%
  image_border(color = "white", geometry = "5x5") %>%
  image_border(color = "black", geometry = "5x5")
```

(ref:instructions-salience-only-alignment-6) Instructions for the salience only condition. Border added for clarity.

```{r instructions-salience-only-alignment-6, fig.cap = "(ref:instructions-salience-only-alignment-6)"}
file.path(
  materials_alignment_6,
  "instructions_salience_only.png"
) %>%
  image_read() %>%
  image_trim() %>%
  image_border(color = "white", geometry = "5x5") %>%
  image_border(color = "black", geometry = "5x5")
```

(ref:instructions-salience-hint-alignment-6) Instructions for the salience + hint condition. Border added for clarity.

```{r instructions-salience-hint-alignment-6, fig.cap = "(ref:instructions-salience-hint-alignment-6)"}
no_hint <-
  file.path(
    materials_alignment_6,
    "instructions_no_hint.png"
  ) %>%
  image_read() %>%
  image_trim()

salience_hint <-
  file.path(
    materials_alignment_6,
    "instructions_salience_hint.png"
  ) %>%
  image_read() %>%
  image_trim() %>%
  image_border(color = "white", geometry = "0x30")

c(
  no_hint,
  salience_hint
) %>%
  image_append(stack = TRUE) %>%
  image_trim() %>%
  image_border(color = "white", geometry = "5x5") %>%
  image_border(color = "black", geometry = "5x5")
```

#### Project display

The project displays were the same as Experiment 2 (see
Figure \@ref(fig:projects-alignment-6)).

(ref:projects-alignment-6) The projects display.

```{r projects-alignment-6, fig.cap = "(ref:projects-alignment-6)"}
file.path(
  materials_alignment_6,
  "alignment_high_reliability_amount_high.png"
) %>%
  image_read() %>%
  image_trim()
```

#### Procedure

Participants read the instruction page as per their hint condition, and then
proceeded to complete one set of ranking and allocations.

