### Method

#### Participants

`r descriptives_aggregation_2$apa` Table \@ref(tab:condition-allocation-aggregation-2)
shows the between-subjects condition allocation.
Appendix \@ref(power-analysis-aggregation-2) describes the power analysis
conducted to arrive at this sample size.

```{r condition-allocation-aggregation-2}
descriptives_aggregation_2$condition_allocation_table %>%
  apa_table("Experiment 2 group allocation.")
```

#### Materials

##### Instructions

Participants were shown the same instructions as in Experiment 1 (see
Section \@ref(instructions-materials-aggregation-1)).

##### Risky investment task {#task-aggregation-2}

Participants saw a similar display to the one in Experiment 1 (see
Section \@ref(task-aggregation-1)), but with new gamble values, in order to fix
the mistake in the Experiment 1 gamble value calculation (detailed above in
Section \@ref(outcome-distribution-aggregation-1)).

The presentation and awareness manipulations were as in Experiment 1. However,
in the distribution-present condition participants saw the outcome probability
distribution of all the projects alongside the description, rather than after
all the projects were seen (see
Figure \@ref(fig:separate-distribution-present-aggregation-2)).

(ref:separate-distribution-present-aggregation-2) An example of a display seen by those in the separate distribution-present condition of Experiment 2.

```{r separate-distribution-present-aggregation-2, fig.cap = "(ref:separate-distribution-present-aggregation-2)"}
file.path(
  materials_aggregation_2,
  "project_choice_oil-well_separate_distribution_present_1.png"
) %>%
  image_read() %>%
  image_trim()
```

##### Follow-up {#follow-up-aggregation-2}

Participants were asked how many projects they think they saw, whether they were
willing to accept all or none of the projects, and how many they would be
willing to accept if they had to choose a number. See
Appendix \@ref(follow-up-materials-aggregation-2-appendix) for screenshots of
these questions.

#### Procedure

Participants read the instructions and completed the risky investment task in
their respective conditions. After seeing the individual projects, participants
were then asked the three follow-up questions.
