### Method

#### Participants

`r descriptives_aggregation_2$apa` Table \@ref(tab:condition-allocation-aggregation-2)
shows the between-subjects condition allocation.

```{r condition-allocation-aggregation-2}
descriptives_aggregation_2$condition_allocation_table %>%
  apa_table("Experiment 2 group allocation.")
```

#### Materials

##### Instructions

Participants were shown the same instructions as in
[Experiment 1](#instructions-materials-aggregation-1).

##### Risky investment task {#task-aggregation-2}

Participants saw a similar display to the one in
[Experiment 1](#task-aggregation-1), but with new gamble values, in order to fix
the mistake in the Experiment 1 gamble value calculation (detailed
[above](#outcome-distribution-aggregation-1)).

The presentation and awareness manipulations were as in Experiment 1. However,
for the distribution variable, participants either saw the project descriptions
as is, or saw an outcome probability distribution of all the projects alongside
the description (see
Figure \@ref(fig:separate-distribution-present-aggregation-2)).

(ref:separate-distribution-present-aggregation-2) An example of a display seen by those in the separate distribution-present condition of Experiment 2.

```{r separate-distribution-present-aggregation-2, fig.cap = "(ref:separate-distribution-present-aggregation-2)"}
here(
  materials_aggregation_2,
  "project_choice_oil-well_separate_distribution_present_1.png"
) %>%
  image_read() %>%
  image_trim()
```

##### Follow-up {#follow-up-aggregation-2}

I asked participants how many projects they think they saw, whether they were
willing to accept all or none of the projects, and how many they would
be willing to accept if they had to choose a number. See
Appendix \@ref(follow-up-materials-aggregation-2-appendix) for screenshots.

#### Procedure

Participants responded to demographic questions, read the instructions, and
completed the risky investment task in their respective conditions. After seeing
the individual projects, participants were then asked the three follow-up
questions.
