### Results {#results-aggregation-2}

#### Project investment

The project investment data was analysed in two ways: as binary choice per trial
(using logistic regression), and as proportions of choice per participant (using
t-test). In each case I compared the relevant comparison condition to the same
control condition (separate naive distribution absent).
Figures \@ref(fig:plot-aggregation-2-choice)
and \@ref(fig:plot-aggregation-2-proportion) show the choice and proportion
data, respectively. The difference between presentation conditions was not
significant, both in the logistic regression
`r results_aggregation_2$choice$presentation$full_result[[2]]`, and in the
t-test, `r results_aggregation_2$proportion$presentation`. Similarly, the
difference between awareness conditions was not significant, both in the
logistic regression `r results_aggregation_2$choice$awareness$full_result[[2]]`,
and in the t-test, `r results_aggregation_2$proportion$awareness`. However,
those that that saw a distribution tended to choose to invest significantly more
(`r results_aggregation_2$distribution_mean$present$choice`) than those that did
not see a distribution
(`r results_aggregation_2$distribution_mean$absent$choice`), seen both in the
logistic regression, `r results_aggregation_2$choice_distribution`, and the
t-test `r results_aggregation_2$proportion$distribution`.

(ref:plot-aggregation-2-choice) Mean project acceptance for the presentation, awareness, and distribution effects. Note, the condition on the left of each effect is the reference condition (separate presentation, naive awareness, distribution absent). As such, it is identical for the three effects.

```{r plot-aggregation-2-choice, fig.cap = "(ref:plot-aggregation-2-choice)"}
plot_aggregation_2$choice_binary
```

(ref:plot-aggregation-2-proportion) Mean proportion of project acceptance for the presentation, awareness, and distribution effects. Note, the condition on the left of each effect is the reference condition (separate presentation, naive awareness, distribution absent). As such, it is identical for the three effects.

```{r plot-aggregation-2-proportion, fig.cap = "(ref:plot-aggregation-2-proportion)"}
plot_aggregation_2$choice_proportion
```

Further, as Figure \@ref(fig:plot-aggregation-2-choice-trials) shows, it
doesn't seem as if the previous awareness by trial effect was replicated.

(ref:plot-aggregation-2-choice-trials) Mean project acceptance for separate presentation, distribution absent condition, by awareness and trial.

```{r plot-aggregation-2-choice-trials, fig.cap = "(ref:plot-aggregation-2-choice-trials)"}
plot_aggregation_2$choice_trials
```

#### Follow-up

The portfolio choice data from both the number and binary questions were
congruent with the above, finding that those in the distribution condition were
more likely to invest (see Appendix \@ref(results-aggregation-2-appendix)).
