### Results {#results-aggregation-2}

#### Project investment

The project investment data was analysed as proportions of choice per
participant, as in Experiment 1. Each experimental condition was compared to the
same control condition (separate presentation, naive awareness, and distribution
absent). Figure \@ref(fig:plot-aggregation-2-proportion) shows this data. The
difference between presentation conditions was not significant,
`r results_aggregation_2$proportion$presentation`. Similarly, the
difference between awareness conditions was not significant,
`r results_aggregation_2$proportion$awareness`. However, those that that saw a
distribution tended to choose to invest significantly more
(`r results_aggregation_2$distribution_mean$present$choice`) than those that did
not see a distribution
(`r results_aggregation_2$distribution_mean$absent$choice`),
`r results_aggregation_2$proportion$distribution`.

(ref:plot-aggregation-2-proportion) Mean proportion of project acceptance for the presentation, awareness, and distribution effects. Note, the condition on the left of each effect is the reference condition (separate presentation, naive awareness, distribution absent). As such, it is identical for the three effects. Error bars represent 95% confidence intervals.

```{r plot-aggregation-2-proportion, fig.cap = "(ref:plot-aggregation-2-proportion)"}
plot_aggregation_2$choice_proportion
```

Further, as Figure \@ref(fig:plot-aggregation-2-choice-trials) shows, it
doesn't seem as if the previous awareness by trial effect was replicated.

(ref:plot-aggregation-2-choice-trials) Mean project acceptance for separate presentation, distribution absent condition, by awareness and trial. LOESS is used for smoothing over trials and the shading represents 95% confidence intervals.

```{r plot-aggregation-2-choice-trials, fig.cap = "(ref:plot-aggregation-2-choice-trials)"}
plot_aggregation_2$choice_trials
```

#### Follow-up

The portfolio choice data from both the number and binary questions were
congruent with the above, finding that those in the distribution condition were
more likely to invest (see Appendix \@ref(results-aggregation-2-appendix)).
