### Method

#### Participants

`r descriptives_alignment_8$apa` Table \@ref(tab:condition-allocation-alignment-8)
shows the between-subjects condition allocation. The two reliability amount
conditions (low and high) were presented within subjects and the order of their
presentation was randomised. As before, NPV amount was varied within subjects.
Therefore, each participant saw two separate project displays.
Appendix \@ref(power-analysis-alignment-8) describes the power analysis
conducted to arrive at the sample size.

```{r condition-allocation-alignment-8}
descriptives_alignment_8$condition_allocation_table %>%
  apa_table("Experiment 3 group allocation.")
```

#### Materials

##### Instructions

Participants saw similar instructions to the previous experiments, with an added
explanation of the NPV reliability information for each reliability type
condition (see Appendix \@ref(instructions-materials-alignment-8-appendix)).
Further, they completed a test of basic NPV understanding. This test was
functioned also as an attention check as, although it was required to answer,
the response should only be one of two letters.

##### Project display

The project displays were similar to the previous experiments. However, here
participants saw the same presentation style in both alignment conditions. Each
display had a table describing the projects in the set, with ranking and
allocation inputs. The project details were presented as dot points within the
relevant cells of the table.
Figure \@ref(fig:projects-alignment-low-reliability-explicit-low-materials-alignment-8)
shows an example of a low alignment, low verbal reliability display and
Figure \@ref(fig:projects-alignment-high-reliability-implicit-high-materials-alignment-8)
shows an example of a high alignment, high numerical reliability display.

(ref:projects-alignment-low-reliability-explicit-low-materials-alignment-8) An example of a low alignment, low verbal reliability display in Experiment 3.

```{r projects-alignment-low-reliability-explicit-low-materials-alignment-8, fig.cap = "(ref:projects-alignment-low-reliability-explicit-low-materials-alignment-8)"}
file.path(
  materials_alignment_8,
  "project_allocation_alignment_low_reliability_type_explicit_reliability_amount_low_variation_1.png"
) %>%
  image_read() %>%
  image_trim()
```

(ref:projects-alignment-high-reliability-implicit-high-materials-alignment-8) An example of a high alignment, high numerical reliability display in Experiment 3.

```{r projects-alignment-high-reliability-implicit-high-materials-alignment-8, fig.cap = "(ref:projects-alignment-high-reliability-implicit-high-materials-alignment-8)"}
file.path(
  materials_alignment_8,
  "project_allocation_alignment_high_reliability_type_implicit_reliability_amount_high_variation_1.png"
) %>%
  image_read() %>%
  image_trim()
```

Three elements were counterbalanced: 1. the association of reliability amount
and project set (two variations), 2. the association of business name with NPV
(five latin square variations), and 3. project variation (five variations per
alignment condition). Project variation meant the project type for the high
alignment condition. For low alignment this meant the intrinsic feature variant
for the relevant project type. Table column order and project display order were
both randomised.

##### Interstitial

Before each project display, participants saw an "interstitial" page, whose role
was to 1. introduce the next display, and 2. check the participant's attention
(not required to answer, so can be skipped if the interstitial text isn't read).
See Figure \@ref(fig:interstitial-materials-alignment-8) in the appendix for an
example.

