### Method

#### Participants

`r descriptives_alignment_8$apa` Table \@ref(tab:condition-allocation-alignment-8)
shows the allocation of participants to the different conditions. The two
reliability level conditions (low and high) were presented within subjects and
the order of their presentation was randomised. Similar to the previous
experiments, NPV varied within subjects. Therefore, each participant saw two
separate project displays. Appendix \@ref(power-analysis-alignment-8) describes
the power analysis conducted to arrive at the sample size.

```{r condition-allocation-alignment-8}
descriptives_alignment_8$condition_allocation_table %>%
  apa_table("Experiment 3 group allocation.")
```

#### Materials

##### Instructions

Participants were given instructions similar to those in the previous
experiments, with an added explanation about the NPV reliability information for
each reliability type (see
Appendix \@ref(instructions-materials-alignment-8-appendix)). Further, they
completed a test of basic NPV understanding. Further, they completed a test on
basic NPV understanding, which also functioned as an attention check.

##### Project Display

The project displays were similar to those used in the previous experiments.
However, participants were given the same presentation style for both alignment
conditions. Each display had a table describing the projects in the set,
including ranking and allocation inputs. Project details were presented as
bullet points within the relevant cells of the table.
Figure \@ref(fig:projects-alignment-low-reliability-explicit-low-materials-alignment-8)
shows an example of a low alignment, low verbal reliability display; and
Figure \@ref(fig:projects-alignment-high-reliability-implicit-high-materials-alignment-8)
shows an example of a high alignment, high numerical reliability display.

(ref:projects-alignment-low-reliability-explicit-low-materials-alignment-8) An example of a low alignment, low verbal reliability display in Experiment 3.

```{r projects-alignment-low-reliability-explicit-low-materials-alignment-8, fig.cap = "(ref:projects-alignment-low-reliability-explicit-low-materials-alignment-8)"}
file.path(
  materials_alignment_8,
  "project_allocation_alignment_low_reliability_type_explicit_reliability_amount_low_variation_1.png"
) %>%
  image_read() %>%
  image_trim()
```

(ref:projects-alignment-high-reliability-implicit-high-materials-alignment-8) An example of a high alignment, high numerical reliability display in Experiment3.

```{r projects-alignment-high-reliability-implicit-high-materials-alignment-8, fig.cap = "(ref:projects-alignment-high-reliability-implicit-high-materials-alignment-8)"}
file.path(
  materials_alignment_8,
  "project_allocation_alignment_high_reliability_type_implicit_reliability_amount_high_variation_1.png"
) %>%
  image_read() %>%
  image_trim()
```

Three elements were counterbalanced: (a) the association between reliability
level and project set (two variations), (b) the association between business
name and NPV (five latin square variations), and (c) project variation (five
variations per alignment condition). When counterbalancing for the high
alignment group, projects varied by project type (e.g., whether the five
projects all described oil wells or microchips). When counterbalancing for the
low alignment group, projects varied by their intrinsic features (e.g., whether
the oil well project in the set indicated a probability of finding oil of 96% or
90%). Table column order and project display order were both randomised.

##### Interstitial Page

Prior to each project being displayed, participants were shown an interstitial
page, which was used to (a) introduce the next display, and (b) check the
participant's attention (given that no input was required, participants could
easily skip the page without reading the text). See
Appendix \@ref(interstitial-materials-alignment-8) for an example.

