### Results {#results-alignment-2-appendix}

#### Ranking

A mixed factorial ANOVA was conducted to investigate the effects of alignment
and verbally-instructed NPV reliability on participants’ rankings of the
target project. As shown in Figure \@ref(fig:plot-alignment-2-ranking), the
alignment $\times$ reliability amount $\times$ NPV interaction was
significant,
`r results_alignment_2$ranking$alignment_reliability_amount_npv_amount`. This
effect seems to be driven by the differences between the no NPV condition and
the conditions with NPV across the two alignment conditions. Specifically, in
the low alignment condition, the linear NPV trend was significantly lower in the
no NPV condition than both the low reliability condition,
`r results_alignment_2$ranking$low_noNPV_linear_low`, and the high
reliability condition, `r results_alignment_2$ranking$high_noNPV_linear_low`.
However, in the high alignment condition, the linear NPV trend was only
significantly lower in the no NPV condition than the high reliability condition,
`r results_alignment_2$ranking$high_noNPV_linear_high`, and not the low
reliability condition, `r results_alignment_2$ranking$low_noNPV_linear_high`.

(ref:plot-alignment-2-ranking) Mean ranking.

```{r plot-alignment-2-ranking, fig.cap = "(ref:plot-alignment-2-ranking)"}
plot_alignment_2$ranking
```

#### Confidence

A mixed factorial ANOVA was conducted to investigate the effects of alignment
and verbally-instructed NPV reliability on participants’ confidence rating of
their decisions. As shown in Figure \@ref(fig:plot-alignment-2-confidence), the
alignment $\times$ reliability amount $\times$ NPV interaction was not
significant,
`r results_alignment_2$confidence$alignment_reliability_amount_npv_amount`.
Contrary to the allocation and ranking data, in
the low alignment condition, there were no significant differences in the linear
NPV trend between the no NPV condition and low reliability condition,
`r results_alignment_2$confidence$low_noNPV_linear_low`, nor the high
reliability condition, `r results_alignment_2$confidence$high_noNPV_linear_low`.
However, as above, in the high alignment condition, the linear NPV trend was
significantly lower in the no NPV condition than the high reliability condition,
`r results_alignment_2$confidence$high_noNPV_linear_high`, and not the low
reliability condition, `r results_alignment_2$confidence$low_noNPV_linear_high`.

(ref:plot-alignment-2-confidence) Mean confidence.

```{r plot-alignment-2-confidence, fig.cap = "(ref:plot-alignment-2-confidence)"}
plot_alignment_2$confidence
```

#### Forecast mean

A mixed factorial ANOVA was conducted to investigate the effects of alignment
and verbally-instructed NPV reliability on participants’ forecast means. As seen
in Figure \@ref(fig:plot-alignment-2-forecast-mean), the alignment $\times$
reliability amount $\times$ NPV interaction was not significant,
`r results_alignment_2$forecast_mean$alignment_reliability_amount_npv_amount`.
However, the alignment $\times$ NPV interaction was significant,
`r results_alignment_2$forecast_mean$alignment_npv_amount`; as well as the
reliability amount $\times$ NPV interaction,
`r results_alignment_2$forecast_mean$reliability_amount_npv_amount`. The simple
effects appear to be as above. Specifically, in the low alignment condition, the
linear NPV trend was significantly lower in the no NPV condition than both the
low reliability condition,
`r results_alignment_2$forecast_mean$low_noNPV_linear_low`, and the high
reliability condition,
`r results_alignment_2$forecast_mean$high_noNPV_linear_low`. However, in the
high alignment condition, the linear NPV trend was only significantly lower in
the no NPV condition than the high reliability condition,
`r results_alignment_2$forecast_mean$high_noNPV_linear_high`, and not the low
reliability condition,
`r results_alignment_2$forecast_mean$low_noNPV_linear_high`.

(ref:plot-alignment-2-forecast-mean) Mean forecasts.

```{r plot-alignment-2-forecast-mean, fig.cap = "(ref:plot-alignment-2-forecast-mean)"}
plot_alignment_2$forecast_mean
```

#### Forecast SD {#forecast-sd-alignment-2}

A mixed factorial ANOVA was conducted to investigate the effects of alignment
and verbally-instructed NPV reliability on participants’ forecast SDs. As seen
in Figure \@ref(fig:plot-alignment-2-forecast-sd), the alignment $\times$
reliability amount $\times$ NPV interaction was significant,
`r results_alignment_2$forecast_sd$alignment_reliability_amount_npv_amount`.
However, none of the linear NPV trends were significantly different from each
other as above. Of relevance, the low alignment condition on average had higher
SDs than those in the high alignment condition,
`r results_alignment_2$forecast_sd$alignment`.

(ref:plot-alignment-2-forecast-sd) Mean forecast SD.

```{r plot-alignment-2-forecast-sd, fig.cap = "(ref:plot-alignment-2-forecast-sd)"}
plot_alignment_2$forecast_sd
```
