### Method

#### Participants

`r descriptives_alignment_2$apa` Table \@ref(tab:condition-allocation-alignment-2)
shows the between-subjects condition allocation. NPV amount was varied within
subjects.

```{r condition-allocation-alignment-2}
descriptives_alignment_2$condition_allocation_table %>%
  apa_table("Experiment 1 group allocation.")
```

#### Materials {#materials-alignment-2}

##### Instructions {#instructions-materials-alignment-2}

The instructions page explained to the participants, who did not necessarily
have business experience, about the task and NPV. However, this page was also
used to manipulate whether participants were told that NPV was reliable or
unreliable as a financial measure. Participants in the low NPV reliability
condition were told that NPV is an unreliable metric, whereas those in the high
NPV reliability condition were told that NPV is a reliable metric. Those in the
no NPV condition saw instructions that did not include the NPV explanation.
Critically, participants were told to invest in products with a high objective
value (because a better quality product is not always better in a consumer goods
market). Since participants might still not use this instruction when directly
viewing the projects, Experiment 3 used projects with attributes that more
inherently conveyed quality.
Appendix \@ref(instructions-materials-alignment-2-appendix) shows the
instructions used in Experiment 1.

##### Project display {#projects-materials-alignment-2}

Participants read sets of fictional business projects for which to potentially
allocate capital. The high alignment display was a table that listed various
attributes for five projects (see
Figure \@ref(fig:projects-alignment-high-materials-alignment-2)). The low
alignment display had each project expressed as individual paragraphs that
described the relevant attributes through full sentences (see
Figure \@ref(fig:projects-alignment-low-materials-alignment-2)). For the high
alignment display, the product was the same, and the concrete attributes were
consistent, while in the low alignment display, each project was a different
product with concrete attributes relevant to that project. For both alignment
conditions each project description included an NPV.

This alignment manipulation was reinforced by visual presentation. The table
format is better afforded by the high alignment condition because all the
dimensions are shared. However, this confounds alignment with presentation
style. This is addressed in Experiment 3 by equating the table format across
both alignment conditions.

(ref:projects-alignment-high-materials-alignment-2) An example of a high alignment display in Experiment 1.

```{r projects-alignment-high-materials-alignment-2, fig.cap = "(ref:projects-alignment-high-materials-alignment-2)"}
file.path(
  materials_alignment_2,
  "projects_alignment_high.png"
) %>%
  image_read() %>%
  image_trim() %>%
  image_convert(type = "grayscale") %>%
  image_contrast()
```

(ref:projects-alignment-low-materials-alignment-2) An example of a low alignment display in Experiment 1. Border added for clarity.

```{r projects-alignment-low-materials-alignment-2, fig.cap = "(ref:projects-alignment-low-materials-alignment-2)"}
file.path(
  materials_alignment_2,
  "projects_alignment_low.png"
) %>%
  image_read() %>%
  image_trim() %>%
  image_convert(type = "grayscale") %>%
  image_contrast() %>%
  image_border(color = "white", geometry = "5x5") %>%
  image_border(color = "black", geometry = "5x5")
```

Critically, the value of the concrete attributes were always in conflict with
the NPV. For instance, Project 4 always had the lowest value for each of the
concrete attributes for laptops, but always had the highest NPV. This meant that
participants’ allocations could be used as a proxy measure for an individual’s
degree of dependence on NPV.

##### Allocation

Participants completed a capital allocation task (see
Figure \@ref(fig:allocation-alignment-2)), adapted from @bardolet2011, in which
they were asked to allocate a hypothetical yearly budget across the given five
projects.

(ref:allocation-alignment-2) The allocation task. Border added for clarity.

```{r allocation-alignment-2, fig.cap = "(ref:allocation-alignment-2)"}
file.path(
  materials_alignment_2,
  "allocation.png"
) %>%
  image_read() %>%
  image_trim() %>%
  image_convert(type = "grayscale") %>%
  image_contrast() %>%
  image_border(color = "white", geometry = "5x5") %>%
  image_border(color = "black", geometry = "5x5")
```

##### Additional measures

Other measures were included apart from allocation. The stimuli and analyses for
these are reported in the appendix. Specifically, participants were asked to
forecast the future returns of the projects (see
Appendix \@ref(forecasting-materials-alignment-2)), rank the projects (see
Appendix \@ref(ranking-materials-alignment-2)), indicate their confidence in
their decisions (see Appendix \@ref(confidence-materials-alignment-2)), and
justify their decisions (see
Appendix \@ref(justification-materials-alignment-2)).

#### Procedure

After reading the relevant instruction page, participants completed the
forecasting task directly after each project display in the low alignment
condition. For the high alignment condition this was done directly under all
projects. Participants then ranked the projects and subsequently answered the
allocation, confidence, and justification questions.

