### Method

#### Participants

`r descriptives_alignment_2$apa` Table \@ref(tab:condition-allocation-alignment-2)
shows the allocation of participants to the different conditions. NPV was varied
within subjects.

```{r condition-allocation-alignment-2}
descriptives_alignment_2$condition_allocation_table %>%
  apa_table("Experiment 1 group allocation.")
```

#### Materials {#materials-alignment-2}

##### Instructions {#instructions-materials-alignment-2}

Participants, who did not necessarily have business experience, were first shown
an instructions page with information about the task and NPV. These instructions
also informed participants about whether NPV as a financial measure was reliable
or unreliable for the specific project. Participants in the low NPV reliability
conditions were told that NPV was an unreliable metric, while those in the high
NPV reliability conditions were told that NPV was a reliable metric.
Instructions provided to participants in the no NPV condition did not include an
explanation of NPV or its reliability. Critically, participants were asked to
invest in products with a high objective value (because a higher-quality product
is not always better in the consumer goods market). Given that participants may
not use this instruction when directly viewing the projects, Experiment 3 used
projects whose attributes inherently expressed their quality.
Appendix \@ref(instructions-materials-alignment-2-appendix) shows the
instructions used in Experiment 1.

##### Project Display {#projects-materials-alignment-2}

Participants were provided with a set of fictional business projects to which
they were asked to allocate capital. Alignment manipulation was reinforced
through visual presentation. Projects with high alignment were displayed in a
table listing their various attributes (see
Figure \@ref(fig:projects-alignment-high-materials-alignment-2)). In this group,
each project involved the same product type with consistent concrete attributes.
The table format was more appropriate for the high alignment condition because
all dimensions were shared. In contrast, projects with low alignment were
presented as paragraphs describing their relevant attributes (see
Figure \@ref(fig:projects-alignment-low-materials-alignment-2)). In this group,
each project was a different product with concrete attributes specific to that
product. In both alignment conditions, each project description included an NPV.
Critically, the values of the concrete attributes were always in conflict with
the NPV. For instance, Project 4 always had the lowest value for each concrete
attribute but always had the highest NPV. This meant that participants'
allocations could be used as a proxy for their degree of dependence on NPV.

Presentation style was potentially a confounding factor. This was addressed in
Experiment 3 by using the table format for both alignment conditions.

(ref:projects-alignment-high-materials-alignment-2) An example of a high alignment display in Experiment 1.

```{r projects-alignment-high-materials-alignment-2, fig.cap = "(ref:projects-alignment-high-materials-alignment-2)"}
file.path(
  materials_alignment_2,
  "projects_alignment_high.png"
) %>%
  image_read() %>%
  image_trim() %>%
  image_convert(type = "grayscale") %>%
  image_contrast()
```

(ref:projects-alignment-low-materials-alignment-2) An example of a low alignment display in Experiment 1.

```{r projects-alignment-low-materials-alignment-2, fig.cap = "(ref:projects-alignment-low-materials-alignment-2)"}
file.path(
  materials_alignment_2,
  "projects_alignment_low.png"
) %>%
  image_read() %>%
  image_trim() %>%
  image_convert(type = "grayscale") %>%
  image_contrast() %>%
  image_border(color = "white", geometry = "5x5") %>%
  image_border(color = "black", geometry = "5x5")
```

##### Allocation

Participants completed a capital allocation task (see
Figure \@ref(fig:allocation-alignment-2)) adapted from @bardolet2011 in which
they were asked to allocate a hypothetical yearly budget across the given five
projects.

(ref:allocation-alignment-2) The allocation task.

```{r allocation-alignment-2, fig.cap = "(ref:allocation-alignment-2)"}
file.path(
  materials_alignment_2,
  "allocation.png"
) %>%
  image_read() %>%
  image_trim() %>%
  image_convert(type = "grayscale") %>%
  image_contrast() %>%
  image_border(color = "white", geometry = "5x5") %>%
  image_border(color = "black", geometry = "5x5")
```

##### Additional Measures

Other measures apart from allocation were included. The stimuli for and analyses
of these measures are reported in
Appendices \@ref(materials-alignment-2-appendix)
and \@ref(results-alignment-2-appendix), respectively. Specifically,
participants were asked to forecast the future returns of the projects (see
Figure \@ref(fig:forecasting-materials-alignment-2)), rank the projects (see
Figure \@ref(fig:ranking-materials-alignment-2)), indicate their confidence in
their decisions (see Figure \@ref(fig:confidence-materials-alignment-2)), and
justify their decisions (see
Figure \@ref(fig:justification-materials-alignment-2)).

#### Procedure

After reading the relevant instruction page, participants allocated to the low
alignment conditions completed the forecasting task directly beneath each
project display. For the high alignment conditions, this was done directly
beneath all projects. Participants were then asked to rank the projects and
subsequently answer the allocation, confidence, and justification questions.
