### Method

#### Participants

`r descriptives_alignment_7$apa` All conditions were presented within-subjects:
alignment (low and high), NPV reliability type (numerical and verbal), NPV
amount (low and high), and NPV reliability amount (low and high).

#### Materials

##### Instructions

Participants saw instructions similar to the previous experiments.

##### Project display

Participants saw and responded to four webpage displays. At the top of each
display was a text preamble, and underneath this a table that contained project
descriptions. The two columns to the right of each description contained text
boxes for participants to enter a value for the project ranking and budget
allocation. Alignment was manipulated by asking participants to either compare
between each of the project pairs (high alignment), or across all eight projects
in the display (low alignment). For instance, in the high alignment display,
participants had to compare between two railway projects, and then separately
between two logistics projects, etc. However, in the low alignment display,
participants had to compare railway projects to logistics projects directly.
This was manipulated within-subjects, such that project descriptions were
identical across alignment conditions and only the type of comparison (and the
associated preamble text) varied.

Figures \@ref(fig:alignment-low-reliability-explicit), \@ref(fig:alignment-low-reliability-implicit), \@ref(fig:alignment-high-reliability-explicit), \@ref(fig:alignment-high-reliability-implicit)
show the four conditions that participants saw (counterbalanced). Each
description provided the name of the business involved in the project, the type
of project, three specific features of the project, an NPV, and an indication of
reliability (either numerical through ranges or verbal through explicit labels).


```{r alignment-low-reliability-explicit, fig.cap = "Experiment 8 low alignment, verbal reliability display. Cropped for space (full display had eight projects)."}
file.path(
  materials_alignment_7,
  "alignment_low_reliability_type_explicit.png"
) %>%
  image_read() %>%
  image_crop(
    geometry_area(width = 2560, height = 3000, y_off = 100)
  ) %>%
  image_trim()
```

```{r alignment-low-reliability-implicit, fig.cap = "Experiment 8 low alignment, numerical reliability display. Cropped for space (full display had eight projects)."}
file.path(
  materials_alignment_7,
  "alignment_low_reliability_type_implicit.png"
) %>%
  image_read() %>%
  image_crop(
    geometry_area(width = 2560, height = 3000, y_off = 100)
  ) %>%
  image_trim()
```

```{r alignment-high-reliability-explicit, fig.cap = "Experiment 8 high alignment, verbal reliability display. Cropped for space (full display had eight projects)."}
file.path(
  materials_alignment_7,
  "alignment_high_reliability_type_explicit.png"
) %>%
  image_read() %>%
  image_crop(
    geometry_area(width = 2560, height = 3000, y_off = 100)
  ) %>%
  image_trim()
```

```{r alignment-high-reliability-implicit, fig.cap = "Experiment 8 high alignment, numerical reliability display. Cropped for space (full display had eight projects)."}
file.path(
  materials_alignment_7,
  "alignment_high_reliability_type_implicit.png"
) %>%
  image_read() %>%
  image_crop(
    geometry_area(width = 2560, height = 3000, y_off = 100)
  ) %>%
  image_trim()
```

The value of each type of reliability was also manipulated. Explicit reliability
was manipulated by varying whether participants were told that a project pair
was in an industry in which NPV is considered a reliable or unreliable measure.
Implicit reliability was manipulated by presenting NPVs alongside numerical
ranges instead of verbal reliability information about them, and varying whether
the range was high or low. Both of these were manipulated within-display, such
that NPV was reliable for four projects in each display, and NPV was unreliable
for the other four.

Each project had an associated NPV, which was crossed with each project pair's
intrinsic features. That is, each pair had one project with a high NPV and low
intrinsic feature values, and one project with a low NPV and high intrinsic
feature values. As such, a reliance on NPV was inferred if participants
allocated the high NPV project more capital, or a reliance on the intrinsic
features if participants allocated the low NPV project more capital.

#### Procedure

Participants viewed the instructions and then completed the ranking and
allocation tasks in the four sets of project descriptions. The order of the
display was counterbalanced, and the order of the project pairs on each page was
randomised.
