### Results

A mixed factorial ANOVA was conducted to investigate the effects of alignment
and NPV reliability type on participants project allocations. I was unable to
conduct a direct comparison of the two alignment conditions due to the different
allocation input scales, so I compared the NPV reliability amount $\times$ NPV
amount interaction separately in each alignment condition (see
Figures \@ref(fig:plot-alignment-7-allocation-alignment-low)
and \@ref(fig:plot-alignment-7-allocation-alignment-high)). This interaction was
significant for both the high alignment condition,
`r results_alignment_7$allocation$alignment_high$reliability_type_reliability_amount_npv_cond`;
and the low alignment condition,
`r results_alignment_7$allocation$alignment_low$reliability_type_reliability_amount_npv_cond`.
However, there was a significant effect of NPV in the low verbal reliability
condition in the high alignment condition, `r results_alignment_7$allocation$alignment_high$exp_lowlow_lowhigh`; but not for the low alignment
condition, `r results_alignment_7$allocation$alignment_high$imp_lowlow_lowhigh`.

(ref:plot-alignment-7-allocation-alignment-low) Mean project allocation, for the low alignment condition. Error bars represent 95% confidence intervals.

```{r plot-alignment-7-allocation-alignment-low, fig.cap = "(ref:plot-alignment-7-allocation-alignment-low)"}
plot_alignment_7$allocation$alignment_low
```

(ref:plot-alignment-7-allocation-alignment-high) Mean project allocation, for the high alignment condition. Error bars represent 95% confidence intervals.

```{r plot-alignment-7-allocation-alignment-high, fig.cap = "(ref:plot-alignment-7-allocation-alignment-high)"}
plot_alignment_7$allocation$alignment_high
```
