### Results

A mixed factorial ANOVA was conducted to investigate the effects of alignment
and NPV reliability type on participants project allocations. A direct
comparison of the two alignment conditions was not possible due to the different
allocation input scales, so the NPV reliability amount $\times$ NPV
interaction was tested separately in each alignment condition (see
Figures \@ref(fig:plot-alignment-7-allocation-alignment-low)
and \@ref(fig:plot-alignment-7-allocation-alignment-high)). This interaction was
significant for both the high alignment condition,
`r results_alignment_7$allocation$alignment_high$reliability_type_npv_cond_reliability_amount`;
and the low alignment condition,
`r results_alignment_7$allocation$alignment_low$reliability_type_npv_cond_reliability_amount`.
However, there was a significant effect of NPV in the low verbal reliability
condition in high alignment,
`r results_alignment_7$allocation$alignment_high$exp_lowlow_lowhigh`; but not in
low alignment,
`r results_alignment_7$allocation$alignment_low$exp_lowlow_lowhigh`.

(ref:plot-alignment-7-allocation-alignment-low) Mean project allocation, for the low alignment condition. Error bars represent 95% confidence intervals.

```{r plot-alignment-7-allocation-alignment-low, fig.cap = "(ref:plot-alignment-7-allocation-alignment-low)"}
plot_alignment_7$allocation$alignment_low
```

(ref:plot-alignment-7-allocation-alignment-high) Mean project allocation, for the high alignment condition. Error bars represent 95% confidence intervals.

```{r plot-alignment-7-allocation-alignment-high, fig.cap = "(ref:plot-alignment-7-allocation-alignment-high)"}
plot_alignment_7$allocation$alignment_high
```
