### Method

#### Participants

`r descriptives_alignment_3$apa` Both the reliability amount conditions (low and
high) and alignment conditions (low and high) were presented within subjects and
their order of presentation was counterbalanced.

#### Materials

##### Instructions

Participants were shown similar instructions to [Experiment
1](#instructions-materials-alignment-2). However, here they were given more
information about NPV (about the discount rate and initial investment). See
Appendix \@ref(instructions-materials-alignment-3-appendix) for screenshots of
the instructions.

##### NPV test

Participants were presented with a short and simple test of their understanding
of NPV (see Appendix \@ref(npv-test-materials-alignment-3)).

##### Project display

As seen in Figures \@ref(fig:projects-alignment-low-materials-alignment-3)
and \@ref(fig:projects-alignment-high-materials-alignment-3), the project
display was as in [Experiment 1](#projects-materials-alignment-2), except for
the addition of another set of projects that differed in semantic content. That
is, the projects were about different types of projects (to allow for a
within-subjects manipulation). Along with the single NPV, the forecasted ranges
of cash flow that the NPV was calculated from were presented. In the low
numerical reliability condition, the ranges were $\pm85$% around the mean (e.g.,
$150-$1850, where the forecast mean is $1000); whereas in the high numerical
reliability condition, the ranges were $\pm5$% around the mean (e.g.,
$950-$1050, where the forecast mean is $1000). Wide ranges should indicate low
reliability in the measure, while narrow ranges should indicate high
reliability. Between the four displays, participants were told to treat each new
set of projects as independent to the other sets.

(ref:projects-alignment-low-materials-alignment-3) An example of a low alignment low reliability display in Experiment 2. Border added for clarity.

```{r projects-alignment-low-materials-alignment-3, fig.cap = "(ref:projects-alignment-low-materials-alignment-3)"}
here(
  materials_alignment_3,
  "alignment_low_reliability_low.png"
) %>%
  image_read() %>%
  image_trim() %>%
  image_contrast() %>%
  image_border(color = "white", geometry = "5x5") %>%
  image_border(color = "black", geometry = "5x5")
```

(ref:projects-alignment-high-materials-alignment-3) An example of a high alignment high reliability display in Experiment 2.

```{r projects-alignment-high-materials-alignment-3, fig.cap = "(ref:projects-alignment-high-materials-alignment-3)"}
here(
  materials_alignment_3,
  "alignment_high_reliability_high.png"
) %>%
  image_read() %>%
  image_trim() %>%
  image_contrast()
```

##### NPV knowledge ratings

I was interested if the participants would be overconfident in their knowledge
of NPV, so asked them to rate this at multiple points in the experiment (see
Appendix \@ref(npv-knowledge-materials-alignment-3)).

##### Variance lecture

Participants were shown a short lecture on the importance of paying attention to
variance information, in an attempt to facilitate a subsequent increased use of
the numerical reliability information in their allocations (see
Appendix \@ref(variance-lecture-materials-alignment-3) for more details and the
lecture slides).

#### Procedure {#procedure-alignment-3}

Participants saw the instructions, NPV explanation, and completed a simple test
to demonstrate their understanding of NPV. They then completed four
counterbalanced resource allocation trials (equivalent to each condition
combination), and saw a brief presentation about the importance of paying
attention to variance in financial decision-making. Subsequently, participants
completed a further two resource allocation trials, of two of the trials that
they subsequently saw earlier. They were shown the allocations they provided
earlier, and given the opportunity to change them. With the knowledge ratings,
participants rated once before the NPV test, re-rated after the test, and after
the four project displays. They were then asked to rate their knowledge of NPV
as they believe it had been both before and after the variance presentation.
