### Method

#### Participants

`r descriptives_alignment_3$apa` Both the reliability amount conditions (low and
high) and alignment conditions (low and high) were presented within subjects and
the order of their presentation was counterbalanced.

#### Materials

##### Instructions

Participants were shown similar instructions to Experiment 1 (see
Section \@ref(instructions-materials-alignment-2)). However, here they were
given more information about NPV (about the discount rate and initial
investment). The appendix shows the full instructions (see
Figure \@ref(fig:instructions-materials-alignment-3)).

##### NPV test

Participants were presented with a short and simple test of their understanding
of NPV (see Appendix \@ref(npv-test-materials-alignment-3)).

##### Project display

As seen in Figures \@ref(fig:projects-alignment-low-materials-alignment-3)
and \@ref(fig:projects-alignment-high-materials-alignment-3), the project
display was as in Experiment 1, except for the addition of another set of
projects that differed in semantic content. That is, the projects were about
different types of products (to allow for a within-subjects manipulation). Along
with the single NPV, participants saw the forecasted ranges of cash flow that
were used to calculate the NPV. In the low numerical reliability condition, the
ranges were $\pm85$% around the mean (e.g., $150-$1850 if the forecast mean was
$1000); whereas in the high numerical reliability condition, the ranges were
$\pm5$% around the mean (e.g., $950-$1050 if the forecast mean was $1000). Wide
ranges should indicate low reliability in the measure, while narrow ranges
should indicate high reliability. Between the four displays, participants were
told to treat each new set of projects as independent to the other sets.

(ref:projects-alignment-low-materials-alignment-3) An example of a low alignment low reliability display in Experiment 2. Border added for clarity.

```{r projects-alignment-low-materials-alignment-3, fig.cap = "(ref:projects-alignment-low-materials-alignment-3)"}
file.path(
  materials_alignment_3,
  "alignment_low_reliability_low.png"
) %>%
  image_read() %>%
  image_trim() %>%
  image_contrast() %>%
  image_border(color = "white", geometry = "5x5") %>%
  image_border(color = "black", geometry = "5x5")
```

(ref:projects-alignment-high-materials-alignment-3) An example of a high alignment high reliability display in Experiment 2.

```{r projects-alignment-high-materials-alignment-3, fig.cap = "(ref:projects-alignment-high-materials-alignment-3)"}
file.path(
  materials_alignment_3,
  "alignment_high_reliability_high.png"
) %>%
  image_read() %>%
  image_trim() %>%
  image_contrast()
```

##### NPV knowledge ratings

Participants were asked to rate the confidence of their knowledge of NPV at
multiple points in the experiment. The appendix shows an example of this display
(see Figure \@ref(fig:npv-knowledge-materials-alignment-3)).

##### Variance lecture

Participants were shown a short lecture on the importance of paying attention to
variance information, in an attempt to facilitate a subsequent increased use of
the numerical reliability information in their allocations (see
Appendix \@ref(variance-lecture-materials-alignment-3) for more details and the
lecture slides).

#### Procedure {#procedure-alignment-3}

Participants saw the instructions and NPV explanation, and completed a simple
test to demonstrate their understanding of NPV. They then completed four
counterbalanced capital allocation trials (equivalent to each condition
combination), and subsequently saw a brief presentation about the importance of
paying attention to variance in financial decision-making. Participants then
completed a further two capital allocation trials of two of the trials that they
saw earlier. They were shown the allocation values that they provided earlier,
and were given the opportunity to change them. Participants rated their
knowledge of NPV once before the NPV test, re-rated after the test, and again
after the four project displays. They were then asked to rate their knowledge of
NPV as they believe it had been both before and after the variance presentation.
