### Method {#method-alignment-2}

#### Participants

`r descriptives_alignment_3$apa` Both the reliability (low and high) and
alignment (low and high) conditions were presented to subjects, and the order of
presentation was counterbalanced.

#### Materials

##### Instructions

Participants were shown similar instructions to those used in Experiment 1 (see
Section \@ref(instructions-materials-alignment-2)). However, they were given
more NPV information (including discount rate and initial investment).
Appendix \@ref(instructions-materials-alignment-3-appendix) shows the full
instructions.

##### NPV Test

Participants were asked to complete a short, simple test to check their
understanding of NPV (see Appendix \@ref(npv-test-materials-alignment-3)).

##### Project Display

As shown in Figures \@ref(fig:projects-alignment-low-materials-alignment-3)
and \@ref(fig:projects-alignment-high-materials-alignment-3), projects were
displayed as they were in Experiment 1. However, a second set of projects with
different product types and descriptions was added to enable within-subjects
manipulation. Along with the single numerical NPV, participants were provided
with the forecasted cash flow ranges used to calculate the NPV. In the low NPV
reliability condition, ranges were $\pm85$% around the mean (e.g., $150--$1,850
if forecast mean was $1,000); while in the high NPV reliability condition,
ranges were $\pm5$% around the mean (e.g., $950--$1,050 if the forecast mean was
$1,000). A wide range indicated that the measure had low reliability, while a
narrow range indicated that the measure had high reliability. Participants were
told to treat each set of projects independently.

(ref:projects-alignment-low-materials-alignment-3) An example of a low alignment, low reliability display in Experiment 2.

```{r projects-alignment-low-materials-alignment-3, fig.cap = "(ref:projects-alignment-low-materials-alignment-3)"}
file.path(
  materials_alignment_3,
  "alignment_low_reliability_low.png"
) %>%
  image_read() %>%
  image_trim() %>%
  image_contrast() %>%
  image_border(color = "white", geometry = "5x5") %>%
  image_border(color = "black", geometry = "5x5")
```

(ref:projects-alignment-high-materials-alignment-3) An example of a high alignment, high reliability display in Experiment 2.

```{r projects-alignment-high-materials-alignment-3, fig.cap = "(ref:projects-alignment-high-materials-alignment-3)"}
file.path(
  materials_alignment_3,
  "alignment_high_reliability_high.png"
) %>%
  image_read() %>%
  image_trim() %>%
  image_contrast()
```

##### NPV Knowledge Ratings

Participants were asked to rate their confidence in knowledge of NPV at multiple
points in the experiment. Appendix \@ref(npv-knowledge-materials-alignment-3)
shows an example of this display.

##### Variance Lecture

Participants were given a short lecture on the importance of paying attention to
variance information in an attempt to increase their use of numerical
reliability information in their allocations (see
Appendix \@ref(variance-lecture-materials-alignment-3) for more details and the
lecture slides).

#### Procedure {#procedure-alignment-3}

Participants were provided with the instructions and an explanation of NPV
before completing a simple test to demonstrate their understanding of NPV. They
then completed four counterbalanced capital allocation trials (one for each
condition combination) before viewing a brief presentation on the importance of
paying attention to variance in financial decision-making. Participants then
repeated two of the trials that they had completed earlier. They were shown the
allocation values they had provided earlier and were given the opportunity to
change them. Participants rated their knowledge of NPV before and after
completing the NPV test and then rated it again after completing the four
project displays. They were then asked to rate their knowledge of NPV before and
after the variance presentation.
