### Method

#### Materials

##### Instructions {#instructions-materials-alignment-3-appendix}

Figure \@ref(fig:instructions-materials-alignment-3) shows the instructions.

(ref:instructions-materials-alignment-3) Experiment 2 instructions. Border added for clarity.

```{r instructions-materials-alignment-3, fig.cap = "(ref:instructions-materials-alignment-3)"}
file.path(
  materials_alignment_3,
  "instructions.png"
) %>%
  image_read() %>%
  image_trim() %>%
  image_contrast() %>%
  image_border(color = "white", geometry = "5x5") %>%
  image_border(color = "black", geometry = "5x5")
```

##### NPV test {#npv-test-materials-alignment-3}

Participants were given more extensive information about NPV than in the
previous experiment and were tested on their ability to calculate simple
averages from given numerical ranges, as seen in
Figures \@ref(fig:npv-test-1-materials-alignment-3)
and \@ref(fig:npv-test-2-materials-alignment-3).

(ref:npv-test-1-materials-alignment-3) Experiment 2 NPV test. Border added for clarity.

```{r npv-test-1-materials-alignment-3, fig.cap = "(ref:npv-test-1-materials-alignment-3)", out.width = "90%"}
npv_test_1 <- file.path(
  materials_alignment_3,
  "npv_test_1.png"
) %>%
  image_read()

npv_test_2 <- file.path(
  materials_alignment_3,
  "npv_test_2.png"
) %>%
  image_read()

c(
  npv_test_1,
  npv_test_2
) %>%
  image_trim() %>%
  image_append(stack = TRUE) %>%
  image_contrast() %>%
  image_border(color = "white", geometry = "5x5") %>%
  image_border(color = "black", geometry = "5x5")
```

(ref:npv-test-2-materials-alignment-3) Experiment 2 NPV test answers. Border added for clarity.

```{r npv-test-2-materials-alignment-3, fig.cap = "(ref:npv-test-2-materials-alignment-3)", out.width = "60%"}
file.path(
  materials_alignment_3,
  "npv_test_3.png"
) %>%
  image_read() %>%
  image_trim() %>%
  image_contrast() %>%
  image_border(color = "white", geometry = "5x5") %>%
  image_border(color = "black", geometry = "5x5")
```

##### NPV knowledge ratings {#npv-knowledge-materials-alignment-3}

A similar design to @long2018 [Study 1] was used to test whether this sample may
be overconfident in their understanding on NPV. Therefore, participants were
asked to rate their knowledge of NPV in various points in the study (see the
procedure in Section \@ref(procedure-alignment-3)).

(ref:npv-knowledge-materials-alignment-3) Experiment 2 NPV knowledge rating task. Border added for clarity.

```{r npv-knowledge-materials-alignment-3, fig.cap = "(ref:npv-knowledge-materials-alignment-3)"}
file.path(
  materials_alignment_3,
  "npv_knowledge_1.png"
) %>%
  image_read() %>%
  image_trim() %>%
  image_contrast() %>%
  image_border(color = "white", geometry = "5x5") %>%
  image_border(color = "black", geometry = "5x5")
```

\newpage
\newpage

##### Variance lecture {#variance-lecture-materials-alignment-3}

See below the slides for the variance lecture.

```{r, eval=knitr::is_html_output(), out.width='100%', out.height='1000px'}
file.path(
  materials_alignment_3,
  "variance_lecture.pdf"
) %>%
  include_graphics()
```

```{r, results='asis', eval=knitr::is_latex_output(), linewidth = 70}
## From https://ulyngs.github.io/oxforddown/customisations-and-extensions.html#embed-pdf
## \fbox added from https://tex.stackexchange.com/a/20641/233976

pdf_width <- 1.2

split_path <-
  file.path(
    materials_alignment_3,
    "variance_lecture_split/"
  )

slides <-
  split_path %>%
  list.files(full.names = TRUE)

slides %>%
  # for each PDF page, insert it nicely and
  # end with a page break
  paste0(
    "\\begin{figure} \\makebox[\\linewidth][c]{\\fbox{\\includegraphics[width=",
    pdf_width,
    "\\linewidth]{",
    .,
    "}}} \\caption{Variance lecture slide ",
    seq_along(slides),
    ".} \\end{figure}\n"
  ) %>%
  cat()
```
