### Results {#results-alignment-3-appendix}

#### Ranking

A mixed factorial ANOVA was conducted to investigate the effects of NPV,
alignment, and numerical NPV reliability on participants’ project rankings.
Figure \@ref(fig:plot-alignment-3-ranking) shows these data. The alignment
$\times$ reliability amount $\times$ NPV interaction was not
significant,
`r results_alignment_3$ranking$alignment_reliability_amount_npv_amount`.
However, the alignment $\times$ NPV interaction was significant,
`r results_alignment_2$ranking$alignment_npv_amount`; as well as the reliability
amount $\times$ NPV interaction,
`r results_alignment_2$ranking$reliability_amount_npv_amount`. As in the
allocation data, the linear NPV trend did not differ between reliability amount
condition in neither the low alignment condition,
`r results_alignment_3$ranking$linear_low_high_low`, nor the high alignment
condition, `r results_alignment_3$ranking$linear_low_high_high`. However,
averaging over reliability amount, the linear NPV trend was higher in the low
alignment condition than in the high alignment condition,
`r results_alignment_3$ranking$linear_low_high`.

(ref:plot-alignment-3-ranking) Mean ranking.

```{r plot-alignment-3-ranking, fig.cap = "(ref:plot-alignment-3-ranking)"}
plot_alignment_3$ranking
```

#### Confidence

A mixed factorial ANOVA was conducted to investigate the effects of NPV,
alignment, and numerical NPV reliability on participants’ confidence ratings.
Figure \@ref(fig:plot-alignment-3-confidence) shows these data. Only the main
effect of NPV was significant,
`r results_alignment_3$confidence$npv_amount`.

(ref:plot-alignment-3-confidence) Mean confidence.

```{r plot-alignment-3-confidence, fig.cap = "(ref:plot-alignment-3-confidence)"}
plot_alignment_3$confidence
```

#### NPV knowledge

A repeated-measures ANOVA was conducted to investigate the effects of experiment
phase condition on participants’ NPV knowledge rating.
Figure \@ref(fig:plot-alignment-3-npv-knowledge) shows these data. The main
effect of phase was significant, `r results_alignment_3$npv_knowledge$rating`.
The post-explanation rating was significantly higher than the pre-explanation
rating,
`r results_alignment_3$npv_knowledge$X1_X2`. However, there were no significant
differences in rating between any of the later phases.

(ref:plot-alignment-3-npv-knowledge) Mean NPV knowledge rating.

```{r plot-alignment-3-npv-knowledge, fig.cap = "(ref:plot-alignment-3-npv-knowledge)"}
plot_alignment_3$npv_knowledge
```

