### Method {#method-alignment-1}

#### Participants

`r descriptives_alignment_1$apa` Table \@ref(tab:condition-allocation-alignment-1)
shows the between-subjects condition allocation. The two alignment conditions
(low and high) were presented within subjects and the order of their
presentation was randomised. Further, NPV amount was varied within subjects.

```{r condition-allocation-alignment-1}
descriptives_alignment_1$condition_allocation_table %>%
  apa_table("Experiment 4 group allocation.")
```

#### Materials

The project display, allocation task, and confidence task were the same as in
[Experiment 1](#materials-alignment-2).

##### Instructions

Participants were shown similar instructions to [Experiment
1](#instructions-materials-alignment-2), except for the addition of references
to the multiple displays and the removal of an explanation about the forecasting
task. Figures \@ref(fig:instructions-reliability-low-materials-alignment-1)
or \@ref(fig:instructions-reliability-high-alignment-1) show the instructions,
depending on NPV reliability condition.

(ref:instructions-reliability-low-materials-alignment-1) Experiment 4 low reliability instructions. Border added for clarity.

```{r instructions-reliability-low-materials-alignment-1, fig.cap = "(ref:instructions-reliability-low-materials-alignment-1)"}
here(
  materials_alignment_1,
  "instructions_reliability_low.png"
) %>%
  image_read() %>%
  image_trim() %>%
  image_convert(type = "grayscale") %>%
  image_contrast() %>%
  image_border(color = "white", geometry = "5x5") %>%
  image_border(color = "black", geometry = "5x5")
```

(ref:instructions-reliability-high-alignment-1) Experiment 4 high reliability instructions. Border added for clarity.

```{r instructions-reliability-high-alignment-1, fig.cap = "(ref:instructions-reliability-high-alignment-1)"}
here(
  materials_alignment_1,
  "instructions_reliability_high.png"
) %>%
  image_read() %>%
  image_trim() %>%
  image_convert(type = "grayscale") %>%
  image_contrast() %>%
  image_border(color = "white", geometry = "5x5") %>%
  image_border(color = "black", geometry = "5x5")
```

#### Procedure

The procedure was the same as in Experiment 1, except that there was no
forecasting or ranking tasks.
