### Results {#results-alignment-1}

A mixed factorial ANOVA was conducted to investigate the effects of alignment,
verbal NPV reliability, and NPV on participants’ project allocations. As
seen in Figure \@ref(fig:plot-alignment-1-allocation), the alignment $\times$
reliability level $\times$ NPV interaction was not significant,
`r results_alignment_1$allocation$reliability_amount_npv_amount_alignment`. This
is most likely due to the fact that the reliability level $\times$ NPV
interaction was significant in the high alignment condition,
`r results_alignment_1$allocation$low_high_linear_high`, the low alignment
condition, `r results_alignment_1$allocation$low_high_linear_low`, as well as
averaging over alignment conditions,
`r results_alignment_1$allocation$reliability_amount_npv_amount`. Despite this,
the alignment $\times$ NPV interaction was significant,
`r results_alignment_1$allocation$npv_amount_alignment`, such that the linear
trend of NPV was stronger in the low alignment,
`r results_alignment_1$allocation$linear_low` than in the high alignment
condition, `r results_alignment_1$allocation$linear_high`. However, neither of
these trends were individually significant.

(ref:plot-alignment-1-allocation) Mean project allocation in Experiment 4. Error bars represent 95% confidence intervals based on the multivariate model. Note that this mixed factorial design does not allow for using confidence intervals to make inferences by "eye" across conditions.

```{r plot-alignment-1-allocation, fig.cap = "(ref:plot-alignment-1-allocation)"}
plot_alignment_1$allocation
```

<!-- #### Target project -->

#### Confidence

A mixed factorial ANOVA was conducted to investigate the effects of alignment,
verbal NPV reliability, and NPV on participants’ confidence in their
allocations. As shown in Figure \@ref(fig:plot-alignment-1-confidence), the
difference between alignment conditions was not significant,
`r results_alignment_1$confidence$alignment`. However, the reliability $\times$
alignment interaction was significant, as well as the NPV $\times$
alignment interaction. An exploratory analysis was conducted of the relevant
simple effects for each interaction, applying a Šidák correction to the p values
for each effect. None of the simple effects were significant after the
correction.

The raw mean differences indicated that there was a greater difference between
reliability conditions in the low alignment condition,
`r results_alignment_1$confidence$low_high_low` compared to the high alignment
condition, `r results_alignment_1$confidence$low_high_high`. Further, there was
a stronger linear trend of NPV in the low alignment condition,
`r results_alignment_1$confidence$linear_low` compared to the high alignment
condition, `r results_alignment_1$confidence$linear_high`.

(ref:plot-alignment-1-confidence) Mean confidence. Error bars represent 95% confidence intervals based on the multivariate model. Note that this mixed factorial design does not allow for using confidence intervals to make inferences by "eye" across conditions.

```{r plot-alignment-1-confidence, fig.cap = "(ref:plot-alignment-1-confidence)"}
plot_alignment_1$confidence
```
