### Method

#### Participants

##### Power analysis {#power-analysis-aggregation-2}

The power analysis was conducted using the `pwr` package [@champely2020], based
on the presentation effect size from Experiment 1, since it was the smallest
effect. The analysis suggested that a minimum sample size of
`r aggregation2::power * 4` (`r aggregation2::power` $\cdot$ 4) was required for
the presentation effect with an expected power of at least 80%.

#### Materials

##### Follow-up {#follow-up-materials-aggregation-2-appendix}

Figure \@ref(fig:project-number-aggregation-2) shows the project number
question. The maximum value that they could enter was set to 20.
Figures \@ref(fig:portfolio-binary-aggregation-2)
and \@ref(fig:portfolio-number-aggregation-2) ask participants whether they are
willing to take all or none of the projects; and how many projects would they
choose if they could pick randomly (maximum value was set to 20). Those in the
distribution absent condition were asked the same questions, but without the
distribution and its explanation.

(ref:project-number-aggregation-2) Experiment 2 project number question. Border added for clarity.

```{r project-number-aggregation-2, fig.cap = "(ref:project-number-aggregation-2)", out.width = "50%"}
file.path(
  materials_aggregation_2,
  "project_number.png"
) %>%
  image_read() %>%
  image_trim() %>%
  image_border(color = "white", geometry = "5x5") %>%
  image_border(color = "black", geometry = "5x5")
```

(ref:portfolio-binary-aggregation-2) Experiment 2 binary portfolio question. Border added for clarity.

```{r portfolio-binary-aggregation-2, fig.cap = "(ref:portfolio-binary-aggregation-2)"}
file.path(
  materials_aggregation_2,
  "porfolio_binary_distribution_present.png"
) %>%
  image_read() %>%
  image_trim() %>%
  image_border(color = "white", geometry = "5x5") %>%
  image_border(color = "black", geometry = "5x5")
```

(ref:portfolio-number-aggregation-2) Experiment 2 numerical portfolio question. Border added for clarity.

```{r portfolio-number-aggregation-2, fig.cap = "(ref:portfolio-number-aggregation-2)"}
file.path(
  materials_aggregation_2,
  "porfolio_number_distribution_present.png"
) %>%
  image_read() %>%
  image_trim() %>%
  image_border(color = "white", geometry = "5x5") %>%
  image_border(color = "black", geometry = "5x5")
```

