### Method

#### Materials

##### Follow-up {#follow-up-materials-aggregation-2-appendix}

Figure \@ref(fig:project-number-aggregation-2) shows the project number
question (maximum value was set to 20).
Figures \@ref(fig:portfolio-binary-aggregation-2)
and \@ref(fig:portfolio-number-aggregation-2) ask participants whether they are
willing to take all or none of the projects; and how many projects would they
choose if they could pick randomly (maximum value was set to 20). Those in the
distribution absent condition were asked the same questions, but without the
distribution and its explanation.

(ref:project-number-aggregation-2) Experiment 2 project number question.

```{r project-number-aggregation-2, fig.cap = "(ref:project-number-aggregation-2)", out.width = "50%"}
here(
  materials_aggregation_2,
  "project_number.png"
) %>%
  image_read() %>%
  image_trim()
```

(ref:portfolio-binary-aggregation-2) Experiment 2 binary portfolio question.

```{r portfolio-binary-aggregation-2, fig.cap = "(ref:portfolio-binary-aggregation-2)"}
here(
  materials_aggregation_2,
  "porfolio_binary_distribution_present.png"
) %>%
  image_read() %>%
  image_trim()
```

(ref:portfolio-number-aggregation-2) Experiment 2 numerical portfolio question.

```{r portfolio-number-aggregation-2, fig.cap = "(ref:portfolio-number-aggregation-2)"}
here(
  materials_aggregation_2,
  "porfolio_number_distribution_present.png"
) %>%
  image_read() %>%
  image_trim()
```

#### Procedure

Participants responded to demographic questions, read the instructions, and
completed the risky investment task in their respective conditions. After seeing
the individual projects, participants were then asked the three follow-up
questions.
