### Results {#results-aggregation-2-appendix}

#### Follow-up

##### Project number

Participants were asked how many projects they thought they saw.
Figure \@ref(fig:plot-aggregation-2-project-number) shows that overall people
correctly estimated the number of projects, with more accuracy for those in the
aware condition.

(ref:plot-aggregation-2-project-number) Number of projects participants reported seeing, by condition.

```{r plot-aggregation-2-project-number, fig.cap = "(ref:plot-aggregation-2-project-number)"}
plot_aggregation_2$project_number
```

##### Portfolio choice - binary

Participants were then asked if they would rather invest in all or none of the
projects. As Figure \@ref(fig:plot-aggregation-2-portfolio-binary) shows, the
difference between presentation conditions was not significant,
`r results_aggregation_2$portfolio_binary$presentation$full_result[[2]]`. The
awareness effect was also not significant,
`r results_aggregation_2$portfolio_binary$awareness$full_result[[2]]`. However,
those that that saw a distribution chose to invest in all 10 projects
significantly more
(`r results_aggregation_2$distribution_mean$present$portfolio_binary`) than
those that did not see a distribution
(`r results_aggregation_2$distribution_mean$absent$portfolio_binary`),
`r results_aggregation_2$portfolio_binary_distribution`.

(ref:plot-aggregation-2-portfolio-binary) Mean choice of investing in all 10 projects for the presentation, awareness, and distribution effects. Note, the condition on the left of each effect is the reference condition (separate presentation, naive awareness, distribution absent). As such, it is identical for the three effects.

```{r plot-aggregation-2-portfolio-binary, fig.cap = "(ref:plot-aggregation-2-portfolio-binary)"}
plot_aggregation_2$portfolio_binary
```

##### Portfolio choice - number

Subsequently, participants were asked how many projects they would invest in out
of the 10 that they saw. As
Figure \@ref(fig:plot-aggregation-2-portfolio-number) shows, the difference
between presentation conditions was not significant,
`r results_aggregation_2$portfolio_number$presentation`. The awareness effect
was also not significant, `r results_aggregation_2$portfolio_number$awareness`.
However, those that that saw a distribution chose to invest in significantly
more projects than those that did not see a distribution,
`r results_aggregation_2$portfolio_number$distribution`.

(ref:plot-aggregation-2-portfolio-number) Mean number of projects chosen in the follow-up for the presentation, awareness, and distribution effects. Note, the condition on the left of each effect is the reference condition (separate presentation, naive awareness, distribution absent). As such, it is identical for the three effects.

```{r plot-aggregation-2-portfolio-number, fig.cap = "(ref:plot-aggregation-2-portfolio-number)"}
plot_aggregation_2$portfolio_number
```

#### Gambles

Figures \@ref(fig:plot-aggregation-2-trials)
and \@ref(fig:plot-aggregation-2-gamble-values) show that the overall people
seemed to prefer gambles with higher probabilities of gain, sometimes regardless
of expected value or value of the gain.

(ref:plot-aggregation-2-trials) Mean project acceptance for the 10 gambles. The format of the labels indicates: (gain probability, gain value; loss probability, loss value).

```{r plot-aggregation-2-trials, fig.cap = "(ref:plot-aggregation-2-trials)"}
plot_aggregation_2$trials
```

(ref:plot-aggregation-2-gamble-values) Mean project acceptance for the gambles' expected value, positive probability, and positive outcome.

```{r plot-aggregation-2-gamble-values, fig.cap = "(ref:plot-aggregation-2-gamble-values)"}
plot_aggregation_2$gamble_values
```
