## Experiment 2 {#anecdotes-2-appendix}

(ref:plot-simulation-anecdotes-2-negative) Anecdotes Experiment 2 predicted data for the negative valence condition

```{r plot-simulation-anecdotes-2-negative, fig.cap = "(ref:plot-simulation-anecdotes-2-negative)"}
anecdotes2::plot_simulation$negative
```

(ref:plot-simulation-anecdotes-2-positive) Anecdotes Experiment 2 predicted data for the positive valence condition

```{r plot-simulation-anecdotes-2-positive, fig.cap = "(ref:plot-simulation-anecdotes-2-positive)"}
anecdotes2::plot_simulation$positive
```

``` {hypothesis, similarity-check-anecdotes-2, name = "Similarity manipulation check for positive anecdote", echo = TRUE}
In the positive valence condition, allocations for the anecdote-only high
similarity condition will be higher than those in the anecdote-only low
similarity condition.
```

I expected to replicate the rating effects found in Experiment 1 in the
Experiment 2 negative valence condition, and to find the reverse effects in the
positive valence condition.


``` {hypothesis, allocation-similarity-anecdotes-2, name = "Relationship between allocation and perceived similarity for positive anecdote", echo = TRUE}
In the positive valence condition, the correlation between allocation and
similarity rating will be positive
```

``` {hypothesis, allocation-specific-relevance-anecdotes-2, name = "Relationship between allocation and specific-relevance for positive anecdote", echo = TRUE}
In the positive valence condition, there will be no correlation between
allocation and specific-relevance rating in the low similarity condition, but a
positive correlation in the high similarity condition.
```

``` {hypothesis, allocation-general-relevance-anecdotes-2, name = "Relationship between allocation and general-relevance for positive anecdote", echo = TRUE}
There will be no significant correlations between allocation and
general-relevance rating
```

