## Experiment 2 {#anecdotes-2-appendix}

Figures \@ref(fig:plot-simulation-anecdotes-2-negative)
and \@ref(fig:plot-simulation-anecdotes-2-positive) show the simulated data for
the negative and positive valence conditions, respectively. These figures are
different from the equivalent figures in the main text. Here, the same
statistics only value was used for both valence conditions, whereas in the main
text the relevant values for each condition were used. Further, the main text
reports the difference score from the relevant statistics only values, whereas
here the raw means are shown.

(ref:plot-simulation-anecdotes-2-negative) Anecdotes Experiment 2 predicted data for the negative valence condition

```{r plot-simulation-anecdotes-2-negative, fig.cap = "(ref:plot-simulation-anecdotes-2-negative)"}
anecdotes2::plot_simulation$negative
```

(ref:plot-simulation-anecdotes-2-positive) Anecdotes Experiment 2 predicted data for the positive valence condition

```{r plot-simulation-anecdotes-2-positive, fig.cap = "(ref:plot-simulation-anecdotes-2-positive)"}
anecdotes2::plot_simulation$positive
```

```{hypothesis, similarity-check-anecdotes-2, name = "Allocation similarity manipulation check for positive anecdote", echo = TRUE}
For positive anecdotes, allocations for the anecdote only high similarity
condition will be higher than those in the anecdote only low similarity
condition.
```

The rating effects found in Experiment 1 were expected to replicate in the
Experiment 2 negative valence condition. The reverse effects were expected to be
found in the positive valence condition.

```{hypothesis, allocation-similarity-anecdotes-2, name = "Relationship between allocation and perceived similarity for positive anecdote", echo = TRUE}
In the positive valence condition, the correlation between allocation and
similarity rating will be positive
```

```{hypothesis, allocation-specific-relevance-anecdotes-2, name = "Relationship between allocation and specific-relevance for positive anecdote", echo = TRUE}
In the positive valence condition, there will be no correlation between
allocation and specific-relevance rating in the low similarity condition, but a
positive correlation in the high similarity condition.
```

```{hypothesis, allocation-general-relevance-anecdotes-2, name = "Relationship between allocation and general-relevance for positive anecdote", echo = TRUE}
There will be no significant correlations between allocation and
general-relevance rating
```

