### Method

#### Participants

##### Power analysis {#power-analysis-anecdotes-2}

I conducted a power analysis through simulation of the effects implied by the
hypotheses in [Experiment 2](#anecdotes-2). I simulated data with the same mean
values as Experiment 1 for the effects that were previously significant (i.e.,
similarity, statistics, and moderation effects), and no effect for the
differences that were non-significant (as shown in
Figures \@ref(fig:plot-simulation-anecdotes-2-negative)
and \@ref(fig:plot-simulation-anecdotes-2-positive)). The null effect is
analysed using the two one-sided tests (TOST) procedure, or *equivalence*
testing [@lakens2018], and setting the smallest effect size of interest to the
smallest difference that leads to a significant equivalence between the combined
low similarity and statistics-only conditions in Experiment 1.
Figure \@ref(fig:power-analysis-anecdotes-2) shows the results of this analysis.
The analysis suggests a total sample size of `r anecdotes2::power$n_total`
(`r anecdotes2::power$n` $\times$ 2).

\newpage

\blandscape

(ref:power-analysis-anecdotes-2) Anecdotes Experiment 2 power curve. Labels indicate lowest sample size above 80% power.

```{r power-analysis-anecdotes-2, fig.width = 13, fig.height = 7, fig.cap = "(ref:power-analysis-anecdotes-2)"}
anecdotes2::power$power_curve
```

\elandscape

\newpage

#### Materials

##### Instructions {#instructions-materials-anecdotes-2-appendix}

Figure \@ref(fig:general-instructions-materials-anecdotes-2) shows the general
instructions all participants received, and
Figures \@ref(fig:specific-instructions-anecdote-only-materials-anecdotes-2), \@ref(fig:specific-instructions-combined-materials-anecdotes-2),
and \@ref(fig:specific-instructions-statistics-only-materials-anecdotes-2) show
the condition-specific instructions.

(ref:general-instructions-materials-anecdotes-2) General instructions for Experiment 1. Border added for clarity.

```{r general-instructions-materials-anecdotes-2, fig.cap = "(ref:general-instructions-materials-anecdotes-2)"}
here(
  materials_anecdotes_2,
  "general_instructions.png"
) %>%
  image_read() %>%
  image_trim()
```

(ref:specific-instructions-anecdote-only-materials-anecdotes-2) Experiment 2 specific instructions for those in the anecdotes only condition.

```{r specific-instructions-anecdote-only-materials-anecdotes-2, fig.cap = "(ref:specific-instructions-anecdote-only-materials-anecdotes-2)"}
here(
  materials_anecdotes_2,
  "specific_instructions_anecdote_condition_anecdote_only.png"
) %>%
  image_read() %>%
  image_trim()
```

(ref:specific-instructions-combined-materials-anecdotes-2) Experiment 2 specific instructions for those in the combined condition.

```{r specific-instructions-combined-materials-anecdotes-2, fig.cap = "(ref:specific-instructions-combined-materials-anecdotes-2)"}
here(
  materials_anecdotes_2,
  "specific_instructions_anecdote_condition_combined.png"
) %>%
  image_read() %>%
  image_trim()
```

(ref:specific-instructions-statistics-only-materials-anecdotes-2) Experiment 2 specific instructions for those in the statistics only condition.

```{r specific-instructions-statistics-only-materials-anecdotes-2, fig.cap = "(ref:specific-instructions-statistics-only-materials-anecdotes-2)"}
here(
  materials_anecdotes_2,
  "specific_instructions_anecdote_condition_statistics_only.png"
) %>%
  image_read() %>%
  image_trim()
```

##### Allocation task {#allocation-anecdotes-2-appendix}

The following were counterbalanced: 1. project variation (five latin square
variations; the association of each display content with each within-subject
condition); 2. anecdote variation (two variations), which is the association of
each project display and being either the target or comparison project. The
following were randomised: 1. table column order, and 2. project display order.

##### Follow-up questions {#follow-up-materials-anecdotes-2}

Figure \@ref(fig:follow-up-materials-anecdotes-2) shows the follow-up questions.

(ref:follow-up-materials-anecdotes-2) An example of one of the follow-up question displays in Experiment 2.

```{r follow-up-materials-anecdotes-2, fig.cap = "(ref:follow-up-materials-anecdotes-2)"}
here(
  materials_anecdotes_2,
  "follow_up_1.png"
) %>%
  image_read() %>%
  image_trim()
```

##### Interstitial display {#interstitial-materials-anecdotes-2}

(ref:interstitial-materials-anecdotes-2) An example of an interstitial display in Experiment 2.

```{r interstitial-materials-anecdotes-2, fig.cap = "(ref:interstitial-materials-anecdotes-2)"}
here(
  materials_anecdotes_2,
  "interstitial_1.png"
) %>%
  image_read() %>%
  image_trim()
```
