### Method {#method-anecdotes-1-appendix}

#### Participants

##### Power analysis {#power-analysis-anecdotes-1}

I determined the sample size for Experiment 1 by conducting power analyses using
the `Superpower` package [@lakens2019]. The package uses experimental design,
and predicted means and standard deviation, to conduct a priori power
calculations. I used data from @wainberg2018, @jaramillo2019, and @hoeken2009
[Study 3] to determine realistic means and standard deviations for the evidence
and similarity factors, and then calculated the sample size that would allow for
an expected power of at least 80% according to the power functions.

I used data from @wainberg2018 to determine the predicted means for the anecdote
conditions. Specifically, I used the values from the anecdote + statistics,
anecdote + enhanced statistics, and statistics only conditions as the values for
my high similarity condition (because in @wainberg2018 the anecdote was always
of a similar case) for the corresponding anecdote conditions. @wainberg2018 did
not use an anecdote only condition, but @wainberg2013 did and found no
significant differences between the anecdote only condition and the anecdote +
statistics condition. As such, I used the same mean value for both these
conditions.

I hypothesised that there will only be an effect of similarity for the anecdote
only and anecdote + statistics conditions. As such, I used the data from
@hoeken2009 [Study 3] to determine the corresponding mean values for the low
similarity condition. Specifically, I multiplied each predicted mean by the
Cohen's $d_z$ of the similarity effect in @hoeken2009 [Study 3].

To determine the predicted standard deviation, I re-analysed the data from
@jaramillo2019 [Experiment 2] and @hoeken2009 [Study 3] to determine the
coefficient of variation (CV) of each condition. I then converted them to a
standard deviation value in the relevant scale by multiplying the mean of the CV
values by the predicted means from above.

As seen in Figure \@ref(fig:power-analysis-anecdotes-1), the power analysis
suggests that a minimum sample size of `r anecdotes1::power$n_total`
(`r anecdotes1::power$n` $\cdot$ 7) is required for the interaction effect with
an expected power of at least 80%.

(ref:power-analysis-anecdotes-1) Power curves for the similarity and anecdote effects.

```{r power-analysis-anecdotes-1, fig.cap = "(ref:power-analysis-anecdotes-1)"}
anecdotes1::power$plot_ANOVA
```

#### Method

##### Instructions {#instructions-materials-anecdotes-1-appendix}

Figure \@ref(fig:general-instructions-materials-anecdotes-1) shows the general
instructions all participants received, and
Figures \@ref(fig:specific-instructions-anecdote-only-materials-anecdotes-1), \@ref(fig:specific-instructions-combined-materials-anecdotes-1), \@ref(fig:specific-instructions-enhanced-materials-anecdotes-1),
and \@ref(fig:specific-instructions-statistics-only-materials-anecdotes-1) show
the condition-specific instructions.

(ref:general-instructions-materials-anecdotes-1) Experiment 1 general instructions. Note, the two boxes were split between two separate web-pages.

```{r general-instructions-materials-anecdotes-1, fig.cap = "(ref:general-instructions-materials-anecdotes-1)"}
general_instructions_1 <- here(
  materials_anecdotes_1,
  "general_instructions_1.png"
) %>%
  image_read()

general_instructions_2 <- here(
  materials_anecdotes_1,
  "general_instructions_2.png"
) %>%
  image_read()

c(
  general_instructions_1,
  general_instructions_2
) %>%
  image_trim() %>%
  image_append(stack = TRUE)
```

(ref:specific-instructions-anecdote-only-materials-anecdotes-1) Experiment 1 specific instructions for those in the anecdotes only condition.

```{r specific-instructions-anecdote-only-materials-anecdotes-1, fig.cap = "(ref:specific-instructions-anecdote-only-materials-anecdotes-1)"}
here(
  materials_anecdotes_1,
  "specific_instructions_anecdote_condition_anecdote_only.png"
) %>%
  image_read() %>%
  image_trim()
```

(ref:specific-instructions-combined-materials-anecdotes-1) Experiment 1 specific instructions for those in the anecdote + statistics condition.

```{r specific-instructions-combined-materials-anecdotes-1, fig.cap = "(ref:specific-instructions-combined-materials-anecdotes-1)"}
here(
  materials_anecdotes_1,
  "specific_instructions_anecdote_condition_combined.png"
) %>%
  image_read() %>%
  image_trim()
```

(ref:specific-instructions-enhanced-materials-anecdotes-1) Experiment 1 specific instructions for those in the anecdote + enhanced statistics condition.

```{r specific-instructions-enhanced-materials-anecdotes-1, fig.cap = "(ref:specific-instructions-enhanced-materials-anecdotes-1)"}
here(
  materials_anecdotes_1,
  "specific_instructions_anecdote_condition_enhanced.png"
) %>%
  image_read() %>%
  image_trim()
```

(ref:specific-instructions-statistics-only-materials-anecdotes-1) Experiment 1 specific instructions for those in the statistics only condition.

```{r specific-instructions-statistics-only-materials-anecdotes-1, fig.cap = "(ref:specific-instructions-statistics-only-materials-anecdotes-1)"}
here(
  materials_anecdotes_1,
  "specific_instructions_anecdote_condition_statistics_only.png"
) %>%
  image_read() %>%
  image_trim()
```

##### Allocation task {#allocation-materials-anecdotes-1}

A horizontally integrated company is one which is made up of multiple businesses
that operate in similar markets, and may have previously been competitors
(@gaughan2012). A vertically integrated company, on the other hand, is one which
is made up of multiple business than operate in the same market, but in
different levels of the supply chain (@gaughan2012a). A centralised
organisational structure is one in which a company decisions tend to come from a
specific business unit or leader, whereas a decentralised structure is one in
which decisions can be made by separate units or people independently
(@kenton2021).

##### Follow-up {#follow-up-materials-anecdotes-1}

Figure \@ref(fig:follow-up-materials-anecdotes-1) shows the follow-up questions.

(ref:follow-up-materials-anecdotes-1) Follow-up questions in Experiment 1.

```{r follow-up-materials-anecdotes-1, fig.cap = "(ref:follow-up-materials-anecdotes-1)"}
here(
  materials_anecdotes_1,
  "follow_up.png"
) %>%
  image_read() %>%
  image_trim()
```
