### Method {#method-anecdotes-1-appendix}

#### Participants

##### Power analysis {#power-analysis-anecdotes-1}

The sample size for Experiment 1 was determined by conducting power analyses
using the `Superpower` package [@lakens2019]. The package uses experimental
design, and predicted means and standard deviation, to conduct a priori power
calculations. Data from @wainberg2018, @jaramillo2019, and @hoeken2009 [Study 3]
was used to determine realistic means and standard deviations for the evidence
and similarity factors. According to the power functions, the resulting sample
size is assumed to allow for an expected power of at least 80%.

Data from @wainberg2018 were used to determine the predicted means for the
anecdote conditions. Specifically, the values for the high similarity condition
were taken from the anecdote & statistics, anecdote & enhanced statistics, and
statistics only conditions for the corresponding anecdote conditions. This was
done because in @wainberg2018 the anecdote was always of a similar case.
@wainberg2018 did not use an anecdote only condition, but @wainberg2013 did and
found no significant differences between the anecdote only condition and the
anecdote & statistics condition. As such, the same mean value was used for both
conditions.

It was hypothesised that there will only be an effect of similarity for the
anecdote only and anecdote & statistics conditions. As such, the data from
@hoeken2009 [Study 3] were used to determine the corresponding mean values for
the low similarity condition. Specifically, each predicted mean was multiplied
by the Cohen's $d_z$ of the similarity effect in @hoeken2009 [Study 3].

To determine the predicted standard deviation, the data from @jaramillo2019
[Experiment 2] and @hoeken2009 [Study 3] were re-analysed to determine the
coefficient of variation (CV) of each condition. Each CV was then converted to a
standard deviation value in the relevant scale by multiplying the mean of the CV
values by the predicted means from above.

As seen in Figure \@ref(fig:power-analysis-anecdotes-1), the power analysis
suggested that a minimum sample size of `r anecdotes1::power$n_total`
(`r anecdotes1::power$n` $\cdot$ 7) is required for the interaction effect with
an expected power of at least 80%.

(ref:power-analysis-anecdotes-1) Power curves for the similarity and anecdote effects.

```{r power-analysis-anecdotes-1, fig.cap = "(ref:power-analysis-anecdotes-1)"}
anecdotes1::power$plot_ANOVA
```

#### Method

##### Instructions {#instructions-materials-anecdotes-1-appendix}

Figure \@ref(fig:general-instructions-materials-anecdotes-1) shows the general
instructions all participants received, and
Figures \@ref(fig:specific-instructions-anecdote-only-materials-anecdotes-1), \@ref(fig:specific-instructions-combined-materials-anecdotes-1), \@ref(fig:specific-instructions-enhanced-materials-anecdotes-1),
and \@ref(fig:specific-instructions-statistics-only-materials-anecdotes-1) show
the condition-specific instructions.

(ref:general-instructions-materials-anecdotes-1) Experiment 1 general instructions. The two boxes were split between two separate web-pages.

```{r general-instructions-materials-anecdotes-1, fig.cap = "(ref:general-instructions-materials-anecdotes-1)"}
general_instructions_1 <- file.path(
  materials_anecdotes_1,
  "general_instructions_1.png"
) %>%
  image_read()

general_instructions_2 <- file.path(
  materials_anecdotes_1,
  "general_instructions_2.png"
) %>%
  image_read()

c(
  general_instructions_1,
  general_instructions_2
) %>%
  image_trim() %>%
  image_append(stack = TRUE)
```

(ref:specific-instructions-anecdote-only-materials-anecdotes-1) Experiment 1 specific instructions for those in the anecdotes only condition.

```{r specific-instructions-anecdote-only-materials-anecdotes-1, fig.cap = "(ref:specific-instructions-anecdote-only-materials-anecdotes-1)"}
file.path(
  materials_anecdotes_1,
  "specific_instructions_anecdote_condition_anecdote_only.png"
) %>%
  image_read() %>%
  image_trim()
```

(ref:specific-instructions-combined-materials-anecdotes-1) Experiment 1 specific instructions for those in the anecdote & statistics condition.

```{r specific-instructions-combined-materials-anecdotes-1, fig.cap = "(ref:specific-instructions-combined-materials-anecdotes-1)"}
file.path(
  materials_anecdotes_1,
  "specific_instructions_anecdote_condition_combined.png"
) %>%
  image_read() %>%
  image_trim()
```

(ref:specific-instructions-enhanced-materials-anecdotes-1) Experiment 1 specific instructions for those in the anecdote & enhanced statistics condition.

```{r specific-instructions-enhanced-materials-anecdotes-1, fig.cap = "(ref:specific-instructions-enhanced-materials-anecdotes-1)"}
file.path(
  materials_anecdotes_1,
  "specific_instructions_anecdote_condition_enhanced.png"
) %>%
  image_read() %>%
  image_trim()
```

(ref:specific-instructions-statistics-only-materials-anecdotes-1) Experiment 1 specific instructions for those in the statistics only condition.

```{r specific-instructions-statistics-only-materials-anecdotes-1, fig.cap = "(ref:specific-instructions-statistics-only-materials-anecdotes-1)"}
file.path(
  materials_anecdotes_1,
  "specific_instructions_anecdote_condition_statistics_only.png"
) %>%
  image_read() %>%
  image_trim()
```

##### Allocation task {#allocation-materials-anecdotes-1}

A horizontally integrated company is one which is made up of multiple businesses
that operate in similar markets, and may have previously been competitors
[@gaughan2012]. A vertically integrated company, on the other hand, is one which
is made up of multiple business than operate in the same market, but in
different levels of the supply chain [@gaughan2012a]. A centralised
organisational structure is one in which a company decisions tend to come from a
specific business unit or leader, whereas a decentralised structure is one in
which decisions can be made by separate units or people independently
[@kenton2021].

##### Follow-up {#follow-up-materials-anecdotes-1}

Figure \@ref(fig:follow-up-materials-anecdotes-1) shows the follow-up questions.

(ref:follow-up-materials-anecdotes-1) Follow-up questions in Experiment 1.

```{r follow-up-materials-anecdotes-1, fig.cap = "(ref:follow-up-materials-anecdotes-1)"}
file.path(
  materials_anecdotes_1,
  "follow_up.png"
) %>%
  image_read() %>%
  image_trim()
```
