### Results {#results-anecdotes-1-appendix}

#### Allocation

A two-way ANOVA was conducted to investigate the interaction of similarity (low
and high) and anecdote conditions (anecdote only, statistics + anecdote,
anecdote + enhanced statistics). I found a main effect of anecdote type,
`r results_anecdotes_1$allocation$anecdote`; and a main effect of similarity,
`r results_anecdotes_1$allocation$alignment`. interaction was not significant,
`r results_anecdotes_1$allocation$anecdote_alignment`. The difference between
the anecdote only condition and the anecdote + enhanced statistics condition was
not significant when excluding the anecdote + statistics condition,
`r results_anecdotes_1$allocation$anecdote_enhanced_high_low`.

#### Manipulation check

Figure \@ref(fig:plot-anecdotes-1-similarity-rating) shows participants' ratings
of the similarity of the anecdote to the target project. As intended,
participants in the high similarity condition rated the anecdote as more similar
to the target project than those in the low similarity condition,
`r results_anecdotes_1$similarity$alignment`. Table shows participants'
justifications for these ratings.

(ref:plot-anecdotes-1-similarity-rating) Mean similarity rating of Project A (the target project) to the anecdote. Error bars represent 95% confidence intervals.

```{r plot-anecdotes-1-similarity-rating, fig.cap = "(ref:plot-anecdotes-1-similarity-rating)"}
plot_anecdotes_1$similarity
```

#### Follow-up

Figure \@ref(fig:plot-anecdotes-1-relevance-specific) shows participants' ratings
of the specific relevance question. I did not find a significant effect of
evidence type `r results_anecdotes_1$relevance_specific$anecdote`; or
similarity, `r results_anecdotes_1$relevance_specific$alignment`. The
interaction was also not significant,
`r results_anecdotes_1$relevance_specific$anecdote_alignment`.

(ref:plot-anecdotes-1-relevance-specific) Mean rating of how relevant participants thought the anecdote was to Project A (the target project). Error bars represent 95% confidence intervals.

```{r plot-anecdotes-1-relevance-specific, fig.cap = "(ref:plot-anecdotes-1-relevance-specific)"}
plot_anecdotes_1$relevance_specific
```

Figure \@ref(fig:plot-anecdotes-1-relevance-general) shows participants' ratings
of the general relevance question. There was no main effect of similarity,
`r results_anecdotes_1$relevance_general$alignment`, or interaction of
similarity and evidence type,
`r results_anecdotes_1$relevance_general$anecdote_alignment`. However, there was
an unexpected main effect of evidence type,
`r results_anecdotes_1$relevance_general$anecdote`. A contrast analysis with
Bonferroni correction revealed that there was a the anecdote only condition had
significantly higher rating than the anecdote + statistics condition,
`r results_anecdotes_1$relevance_general$anecdote_combined`. However, the
difference between the two anecdote + statistics conditions was not significant,
`r results_anecdotes_1$relevance_general$combined_enhanced`.

(ref:plot-anecdotes-1-relevance-general) Mean rating of how relevant participants thought the anecdote was to other oil projects. Error bars represent 95% confidence intervals.

```{r plot-anecdotes-1-relevance-general, fig.cap = "(ref:plot-anecdotes-1-relevance-general)"}
plot_anecdotes_1$relevance_general
```

I conducted regression analyses to determine the relationship between
allocations and the follow-up ratings of similarity and relevance. As seen in
Figure \@ref(fig:plot-anecdotes-1-lm-allocation-similarity), similarity ratings
are negatively correlated to allocations,
`r results_anecdotes_1$lm$allocation_similarity`. Finally, as seen in
Figure \@ref(fig:plot-anecdotes-1-lm-relevance-specific-similarity) similarity
ratings are positively correlated to specific relevance ratings,
`r results_anecdotes_1$lm$relevance_specific_similarity`.

(ref:plot-anecdotes-1-lm-allocation-similarity) Mean allocations to the target project by similarity rating

```{r plot-anecdotes-1-lm-allocation-similarity, fig.cap = "(ref:plot-anecdotes-1-lm-allocation-similarity)"}
plot_anecdotes_1$lm$allocation_similarity
```

(ref:plot-anecdotes-1-lm-relevance-specific-similarity) Rating of how relevant participants considered the anecdote to the target project, by similarity rating

```{r plot-anecdotes-1-lm-relevance-specific-similarity, fig.cap = "(ref:plot-anecdotes-1-lm-relevance-specific-similarity)"}
plot_anecdotes_1$lm$relevance_specific_similarity
```

