### Results {#results-anecdotes-1-appendix}

#### Allocation

A two-way ANOVA was conducted to investigate the interaction of similarity (low
and high) and anecdote conditions (anecdote only, statistics & anecdote,
anecdote & enhanced statistics). The main text reports the more relevant
interaction that excludes the enhanced statistics condition. There was a main
effect of anecdote type, `r results_anecdotes_1$allocation$anecdote`; and a main
effect of similarity, `r results_anecdotes_1$allocation$alignment`. However, the
interaction was not significant,
`r results_anecdotes_1$allocation$anecdote_alignment`. The difference between
the anecdote only condition and the anecdote & enhanced statistics condition was
not significant, `r results_anecdotes_1$allocation$anecdote_enhanced_high_low`.

#### Manipulation check

Figure \@ref(fig:plot-anecdotes-1-similarity-rating) shows participants' ratings
of the similarity of the anecdote to the target project. As intended,
participants in the high similarity condition rated the anecdote as more similar
to the target project than those in the low similarity condition,
`r results_anecdotes_1$similarity$alignment`.

(ref:plot-anecdotes-1-similarity-rating) Mean similarity rating of Project A (the target project) to the anecdote. Error bars represent 95% confidence intervals.

```{r plot-anecdotes-1-similarity-rating, fig.cap = "(ref:plot-anecdotes-1-similarity-rating)"}
plot_anecdotes_1$similarity
```

#### Follow-up

Figure \@ref(fig:plot-anecdotes-1-relevance-specific) shows participants'
ratings of the specific relevance question. There was no significant effect of
evidence type `r results_anecdotes_1$relevance_specific$anecdote`; or
similarity, `r results_anecdotes_1$relevance_specific$alignment`. The
interaction was also not significant, `r
results_anecdotes_1$relevance_specific$anecdote_alignment`.

(ref:plot-anecdotes-1-relevance-specific) Mean rating of how relevant participants thought the anecdote was to Project A (the target project). Error bars represent 95% confidence intervals.

```{r plot-anecdotes-1-relevance-specific, fig.cap = "(ref:plot-anecdotes-1-relevance-specific)"}
plot_anecdotes_1$relevance_specific
```

Figure \@ref(fig:plot-anecdotes-1-relevance-general) shows participants' ratings
of the general relevance question. There was no main effect of similarity,
`r results_anecdotes_1$relevance_general$alignment`, or interaction of
similarity and evidence type, `r
results_anecdotes_1$relevance_general$anecdote_alignment`. However, there was an
unexpected main effect of evidence type,
`r results_anecdotes_1$relevance_general$anecdote`. A contrast analysis with
Bonferroni correction revealed that the anecdote only condition was rated
significantly higher than the anecdote & statistics condition,
`r results_anecdotes_1$relevance_general$anecdote_combined`. However, the
difference between the two anecdote & statistics conditions was not significant,
`r results_anecdotes_1$relevance_general$combined_enhanced`.

(ref:plot-anecdotes-1-relevance-general) Mean rating of how relevant participants thought the anecdote was to other oil projects. Error bars represent 95% confidence intervals.

```{r plot-anecdotes-1-relevance-general, fig.cap = "(ref:plot-anecdotes-1-relevance-general)"}
plot_anecdotes_1$relevance_general
```

Regression analyses were conducted to determine the relationship between
allocations and the follow-up ratings of similarity and relevance. As shown in
Figure \@ref(fig:plot-anecdotes-1-lm-allocation-similarity), similarity ratings
were negatively correlated to allocations,
`r results_anecdotes_1$lm$allocation_similarity`. Finally, as shown in
Figure \@ref(fig:plot-anecdotes-1-lm-relevance-specific-similarity) similarity
ratings were positively correlated to specific relevance ratings,
`r results_anecdotes_1$lm$relevance_specific_similarity`.

(ref:plot-anecdotes-1-lm-allocation-similarity) Mean allocation to the target
project by similarity rating. The shading represents 95% confidence intervals.

```{r plot-anecdotes-1-lm-allocation-similarity, fig.cap = "(ref:plot-anecdotes-1-lm-allocation-similarity)"}
plot_anecdotes_1$lm$allocation_similarity
```

(ref:plot-anecdotes-1-lm-relevance-specific-similarity) Rating of how relevant participants considered the anecdote to the target project, by similarity rating. The shading represents 95% confidence intervals.

```{r plot-anecdotes-1-lm-relevance-specific-similarity, fig.cap = "(ref:plot-anecdotes-1-lm-relevance-specific-similarity)"}
plot_anecdotes_1$lm$relevance_specific_similarity
```

Participants' justifications for the ratings were not analysed, so are not reported.

