### Method {#method-anecdotes-1}

#### Participants

`r descriptives_anecdotes_1$apa` Table \@ref(tab:condition-allocation-anecdotes-1)
shows the between-subjects condition allocation.
Appendix \@ref(power-analysis-anecdotes-1) describes the power analysis
conducted to arrive at this sample size.

```{r condition-allocation-anecdotes-1}
descriptives_anecdotes_1$condition_allocation_table %>%
  apa_table("Experiment 1 group allocation.")
```

#### Materials {#materials-anecdotes-1}

##### Instructions {#instructions-materials-anecdotes-1}

All participants initially saw general instructions that explained the task. The
subsequent instructions that participants saw depended on their experimental
condition. Those in the anecdote only condition were told that they will see a
case study of a failed project and an analysis of why it failed. Those in the
statistics only condition were told that they will see NPV and reliability
information as a part of the descriptions of the two focal projects.
Participants were explained that these values were sourced from a study with a
large sample. Those in the anecdote & statistics condition were given both of
these instructions, and were also told that the information in the anecdote is
subsumed in the data of the aggregated study. Those in the anecdote & enhanced
statistics condition saw the same as those in the anecdote & statistics
condition, but were subsequently given the explanation of scientific thinking
that @wainberg2018 used.
Appendix \@ref(instructions-materials-anecdotes-1-appendix) shows the
instructions used in Experiment 1.

##### Allocation task

In the allocation task, participants allocated a percentage of a hypothetical
budget between two projects that come from different businesses within a
company. In this chapter, these two projects will be referred to as the *focal*
projects. One of these projects will be referred to in this chapter as the
*target* project and the other as the *comparison* project. The target project
was used as a reference for the similarity manipulation. That is, the anecdote
was either high or low in similarity compared to the target project. Further,
the data analyses presented in Section \@ref(results-anecdotes-1) used
allocations to the target project as the DV.

Participants were presented with information about each business' name,
location, integration (vertical or horizontal), and organisational structure
(centralised or decentralised). See
Appendix \@ref(allocation-materials-anecdotes-1) for an explanation of these
terms. Further, participants were presented with information about features of
each project that they were told were available to managers before the time of
investment. Participants in the anecdote only condition saw just this
information (see
Figure \@ref(fig:project-allocation-anecdote-only-materials-anecdotes-1)), while
those in the statistics conditions saw this information along with measures of
NPV and "Overall reliability rating" (see
Figure \@ref(fig:project-allocation-statistics-materials-anecdotes-1)).
Participants entered their allocation data underneath this table, in two
textboxes labelled *Project A allocation* and *Project B allocation*,
respectively.

(ref:project-allocation-anecdote-only-materials-anecdotes-1) Focal project display for the anecdote only condition in Experiment 1.

```{r project-allocation-anecdote-only-materials-anecdotes-1, fig.cap = "(ref:project-allocation-anecdote-only-materials-anecdotes-1)"}
file.path(
  materials_anecdotes_1,
  "project_allocation_anecdote_only.png"
) %>%
  image_read() %>%
  image_trim()
```

(ref:project-allocation-statistics-materials-anecdotes-1) Focal project display for the statistics only, anecdote & statistics, and anecdote & enhanced statistics conditions in Experiment 1.

```{r project-allocation-statistics-materials-anecdotes-1, fig.cap = "(ref:project-allocation-statistics-materials-anecdotes-1)"}
file.path(
  materials_anecdotes_1,
  "project_allocation_statistics.png"
) %>%
  image_read() %>%
  image_trim()
```

##### Anecdote

Participants that were presented with an anecdote (those in either the anecdote
only, anecdote & statistics, or anecdote & enhanced statistics conditions) saw a
description of a business project and an accompanying "analysis".
Figures \@ref(fig:anecdote-similarity-high-materials-anecdotes-1)
and \@ref(fig:anecdote-similarity-low-materials-anecdotes-1) show the anecdote
display for those in the high and low similarity conditions, respectively. The
project description had a similar layout to that of the focal projects. That is,
it contained information about the business name, location, integration, and
organisational structure of the business. It also detailed several predicted
features of the project. Underneath this description was a paragraph of text
that participants were told was an analysis of why the project failed. This text
referenced each of the features in the description in order to justify the
project failing.

Those in the high similarity condition saw a description of a project from a
business with the same type of investment as the target project (labelled
Project A). All categorical attributes were identical to those in this target
project, and the numerical attributes were all made to be lower. In the
analysis, the numerical attributes were explained to have failed because they
were not as high as certain cut-offs. Critically, these cut-offs were made to
all be higher than the relevant values in Project A. This was done to make sure
that the numerical attributes in the anecdote seem more relevant to those in
Project A. For instance, for Project A, oil extraction was 2200L an hour, for
the anecdote it was 2000L an hour, and the cutoff was 3000L an hour. As such, a
failure of the anecdote because of an insufficient oil extraction rated will
seem more relevant since they both share the state of being lower than the
cut-off in the analysis. Note, however, that there was uncertainty about the
generalisability of these cut-off values because the participants did not
receive a explicit indication of whether these values were meant to generalise
to other cases.

(ref:anecdote-similarity-high-materials-anecdotes-1) Anecdote display for those in the high alignment condition in Experiment 1.

```{r anecdote-similarity-high-materials-anecdotes-1, fig.cap = "(ref:anecdote-similarity-high-materials-anecdotes-1)"}
file.path(
  materials_anecdotes_1,
  "anecdote_similarity_high.png"
) %>%
  image_read() %>%
  image_trim()
```

(ref:anecdote-similarity-low-materials-anecdotes-1) Anecdote display for those in the low alignment condition in Experiment 1.

```{r anecdote-similarity-low-materials-anecdotes-1, fig.cap = "(ref:anecdote-similarity-low-materials-anecdotes-1)"}
file.path(
  materials_anecdotes_1,
  "anecdote_similarity_low.png"
) %>%
  image_read() %>%
  image_trim()
```

##### Follow-up questions

Participants that saw the anecdote were subsequently presented with follow-up
questions. They were asked how similar they believe the anecdote was to the
target project, how relevant it was for their allocations, and how relevant it
would be for judgements about other projects of that type.
Figure \@ref(fig:follow-up-materials-anecdotes-1) in the appendix shows these
questions.

#### Procedure

Participants were introduced to the study through the general instructions and
the specific instructions relevant to their condition. They were then presented
with the allocation task, which included the anecdote analysis and description
(for those not in the statistics condition) and the focal projects description.
Those that saw an anecdote were subsequently shown the follow-up questions.
