### Method {#method-anecdotes-1}

#### Participants

`r descriptives_anecdotes_1$apa` Table \@ref(tab:condition-allocation-anecdotes-1)
shows the allocation of participants to the different conditions.
Appendix \@ref(power-analysis-anecdotes-1) describes the power analysis
conducted to arrive at this sample size.

```{r condition-allocation-anecdotes-1}
descriptives_anecdotes_1$condition_allocation_table %>%
  apa_table("Experiment 1 group allocation.")
```

#### Materials {#materials-anecdotes-1}

##### Instructions {#instructions-materials-anecdotes-1}

All participants were first shown general instructions explaining the task.
Subsequent instructions shown to participants depended on their experimental
condition. Those in the anecdote only condition were told that they would be
shown a case study of a failed project and an analysis of why it failed. Those
in the statistics only condition were told that they would be shown NPV and
reliability information for two focal projects. They were told that these values
were sourced from a study with a large sample. Those in the anecdote &
statistics condition were shown both of these instructions and were also told
that the information in the anecdote had been included in the aggregated study
data. Those in the anecdote & enhanced statistics condition were shown the same
instructions as those in the anecdote & statistics condition, but were also
provided with the explanation of scientific thinking used by @wainberg2018.
Appendix \@ref(instructions-materials-anecdotes-1-appendix) shows the
instructions used in Experiment 1.

##### Allocation Task

In the allocation task, participants were asked to allocate a hypothetical
budget to one of two projects from two different businesses. In this chapter,
these projects are referred to as the *focal* projects, with one being the
*target* project and the other the *comparison* project. The target project was
used as the reference for the similarity manipulation. That is, the anecdote was
either high or low in similarity to the target project. Further, the data
analyses presented in Section \@ref(results-anecdotes-1) used allocations to the
target project as the dependent variable. The comparison project was simply the
other focal project to which participants were allocating. It was always a
different type of project to both the target and anecdote projects.

Participants were presented with information about the name, location,
integration (vertical or horizontal), and organisational structure (centralised
or decentralised) of each business (see
Appendix \@ref(allocation-materials-anecdotes-1) for an explanation of these
terms). Further, they were presented with information about the features of each
project that are typically available to managers prior to investment.
Participants in the anecdote only condition were shown only this information
(see Figure \@ref(fig:project-allocation-anecdote-only-materials-anecdotes-1)).
Those in the anecdote & statistics, anecdote & enhanced statistics, and
statistics only conditions were shown this information along with measures of
NPV and overall reliability rating (see
Figure \@ref(fig:project-allocation-statistics-materials-anecdotes-1)).
Participants entered their allocation data beneath this table in two text boxes
labelled *Project A allocation* and *Project B allocation*, respectively.

(ref:project-allocation-anecdote-only-materials-anecdotes-1) Focal project display for the anecdote only condition in Experiment 1. Here, Project A was the target project and Project B was the comparison project.

```{r project-allocation-anecdote-only-materials-anecdotes-1, fig.cap = "(ref:project-allocation-anecdote-only-materials-anecdotes-1)"}
file.path(
  materials_anecdotes_1,
  "project_allocation_anecdote_only.png"
) %>%
  image_read() %>%
  image_trim()
```

(ref:project-allocation-statistics-materials-anecdotes-1) Focal project display for the statistics only, anecdote & statistics, and anecdote & enhanced statistics conditions in Experiment 1. Here, Project A was the target project and Project B was the comparison project.

```{r project-allocation-statistics-materials-anecdotes-1, fig.cap = "(ref:project-allocation-statistics-materials-anecdotes-1)"}
file.path(
  materials_anecdotes_1,
  "project_allocation_statistics.png"
) %>%
  image_read() %>%
  image_trim()
```

##### Anecdote

Participants who were presented with an anecdote (those in either the anecdote
only, anecdote & statistics, or anecdote & enhanced statistics conditions) were
shown a description of another business project and an accompanying analysis.
Figures \@ref(fig:anecdote-similarity-high-materials-anecdotes-1)
and \@ref(fig:anecdote-similarity-low-materials-anecdotes-1) show the anecdotes
for those in the high and low similarity conditions, respectively. The project
description had a similar layout to that of the focal projects. That is, it
contained information about the business name, location, integration, and
organisational structure of the business. It also detailed several predicted
features of the project. Beneath this description was a paragraph presenting an
analysis of why the project had failed. This paragraph referenced each of the
features in the description to justify the failure of the project.

Participants in the high similarity condition were shown a description of a
project from a business with the same type of investment as the target project
(Project A). All categorical attributes were identical to those in Project A,
but all numerical attributes were lower. The analysis explained that the
numerical attributes had failed because they had not reached certain cut-offs.
Critically, these cut-offs were all higher than the matching values in
Project A. This was done to ensure that the numerical attributes in the anecdote
appeared more relevant than those in Project A. For instance, in Project A, oil
extraction was set at 2,200 L/hr, and in the anecdote it was 2,000 L/hr, while
the cut-off was set at 3,000 L/hr. Thus, the failure of the anecdotal project
arising from insufficient oil extraction would appear more relevant because the
oil extraction in both the anecdotal project and Project A was lower than the
cut-off value. Note, however, that there was uncertainty about the
generalisability of these cut-off values because the participants did not
receive an explicit indication of whether these values were meant to generalise
to other cases.

(ref:anecdote-similarity-high-materials-anecdotes-1) Anecdote for participants in the high similarity condition in Experiment 1.

```{r anecdote-similarity-high-materials-anecdotes-1, fig.cap = "(ref:anecdote-similarity-high-materials-anecdotes-1)"}
file.path(
  materials_anecdotes_1,
  "anecdote_similarity_high.png"
) %>%
  image_read() %>%
  image_trim()
```

(ref:anecdote-similarity-low-materials-anecdotes-1) Anecdote for participants in the low similarity condition in Experiment 1.

```{r anecdote-similarity-low-materials-anecdotes-1, fig.cap = "(ref:anecdote-similarity-low-materials-anecdotes-1)"}
file.path(
  materials_anecdotes_1,
  "anecdote_similarity_low.png"
) %>%
  image_read() %>%
  image_trim()
```

##### Follow-up Questions

Participants who were shown the anecdote were subsequently presented with
follow-up questions. They were asked about how similar they believed the
anecdote was to the target project, how relevant it was to their allocations and
how relevant it would be for their judgements about other projects of that type
(see Appendix \@ref(follow-up-materials-anecdotes-1)).

#### Procedure

Participants were introduced to the study through the general instructions
followed by the specific instructions for their condition. Participants were
then presented with the allocation task and a description of the focal projects.
All participants except those in the statistics only condition were also
presented with the anecdote description and analysis, and the follow-up
questions.
