### Method {#method-anecdotes-1}

#### Participants

`r descriptives_anecdotes_1$apa` Table \@ref(tab:condition-allocation-anecdotes-1)
shows the between-subjects condition allocation.
Appendix \@ref(power-analysis-anecdotes-1) describes the power analysis
conducted to arrive at this sample size.

```{r condition-allocation-anecdotes-1}
descriptives_anecdotes_1$condition_allocation_table %>%
  apa_table("Experiment 1 group allocation.")
```

#### Materials {#materials-anecdotes-1}

##### Instructions

All participants initially saw general instructions that explained the task. The
subsequent instructions that participants saw depended on their experimental
condition. Those in the anecdote only condition were told that they will see a
case study of a failed project and an analysis of why it failed. Those in the
statistics only condition were told that they will see NPV and reliability
information as a part of their target project descriptions, and were explained
that these values were sourced from a study with a large sample. Those in the
anecdote + statistics condition were given both of these instructions, and were
also told that the information in the anecdote is subsumed in the data of the
aggregated study. Those in the anecdote + enhanced statistics condition saw the
same as those in the anecdote + statistics condition, but were subsequently
given the explanation of scientific thinking that @wainberg2018 used.
Appendix \@ref(instructions-materials-anecdotes-1-appendix) shows the
instructions used in Experiment 1.

##### Allocation task

In the allocation task, participants allocated a percentage of a hypothetical
budget between two target projects that come from different businesses within a
company. Participants were presented with information about each business' name,
location, integration (vertical or horizontal), and organisational structure
(centralised or decentralised). See
Appendix \@ref(allocation-materials-anecdotes-1) for an explanation of these
terms. Further, participants were presented with information about features of
each project that they were told were available to managers before the time of
investment. Participants in the anecdote only condition saw just this
information (see
Figure \@ref(fig:project-allocation-anecdote-only-materials-anecdotes-1)), while
those in the statistics conditions saw this information along with measures of
NPV and "Overall reliability rating" (see
Figure \@ref(fig:project-allocation-statistics-materials-anecdotes-1)).
Participants entered their allocation data underneath this table, in two
textboxes labelled *Project A allocation* and *Project B allocation*,
respectively.

(ref:project-allocation-anecdote-only-materials-anecdotes-1) Project display for the anecdote only condition in Experiment 1.

```{r project-allocation-anecdote-only-materials-anecdotes-1, fig.cap = "(ref:project-allocation-anecdote-only-materials-anecdotes-1)"}
here(
  materials_anecdotes_1,
  "project_allocation_anecdote_only.png"
) %>%
  image_read() %>%
  image_trim()
```

(ref:project-allocation-statistics-materials-anecdotes-1) Project display for the statistics only, anecdote + statistics, and anecdote + enhanced statistics conditions in Experiment 1.

```{r project-allocation-statistics-materials-anecdotes-1, fig.cap = "(ref:project-allocation-statistics-materials-anecdotes-1)"}
here(
  materials_anecdotes_1,
  "project_allocation_statistics.png"
) %>%
  image_read() %>%
  image_trim()
```

##### Anecdote

Participants that were presented with an anecdote (those in either the anecdote
only, anecdote + statistics , or anecdote + enhanced statistics conditions) saw
a description of a business project and an accompanying "analysis".
Figures \@ref(fig:anecdote-similarity-high-materials-anecdotes-1)
and \@ref(fig:anecdote-similarity-low-materials-anecdotes-1) show the anecdote
display for those in the high and low similarity conditions, respectively. The
project description had a similar layout to the target projects. That is, it
contained information about the business name, location, integration, and
organisational structure of the business, and detailed predicted features of the
project. Underneath this description was a paragraph of text that participants
were told was an analysis of why the project failed. Therefore, this text
references each of the features in the description in order to justify the
project failing.

Those in the high similarity condition saw a description of a project from a
business with the same type of investment. All categorical attributes were
identical to the relevant target project (Project A), and the numerical
attributes were all made to be lower than those in Project A. In the analysis,
the numerical attributes were explained to have failed because they were not as
high as certain cut-offs. Critically, these cut-offs were made to all be higher
than the relevant values in Project A. This was done to make sure that the
numerical attributes in the anecdote seem more relevant to those in Project A.
For instance, for Project A, oil extraction was 2200L an hour, for the anecdote
it was 2000L an hour, and the cutoff was 3000L an hour. As such, a failure of
the anecdote because of an insufficient oil extraction rated will seem more
relevant since they both share the state of being lower than the cut-off in the
analysis. Note, however, that there was uncertainty about the generalisability
of these cut-off values because the participants did not receive a explicit
indication about whether these values were meant to generalise to other cases.

(ref:anecdote-similarity-high-materials-anecdotes-1) Anecdote display for those in the high alignment condition in Experiment 1.

```{r anecdote-similarity-high-materials-anecdotes-1, fig.cap = "(ref:anecdote-similarity-high-materials-anecdotes-1)"}
here(
  materials_anecdotes_1,
  "anecdote_similarity_high.png"
) %>%
  image_read() %>%
  image_trim()
```

(ref:anecdote-similarity-low-materials-anecdotes-1) Anecdote display for those in the low alignment condition in Experiment 1.

```{r anecdote-similarity-low-materials-anecdotes-1, fig.cap = "(ref:anecdote-similarity-low-materials-anecdotes-1)"}
here(
  materials_anecdotes_1,
  "anecdote_similarity_low.png"
) %>%
  image_read() %>%
  image_trim()
```

##### Follow-up questions

Participants that saw the anecdote were subsequently presented with follow-up
questions. They were asked how similar they believe the anecdote was to the
target project, how relevant it was for their allocations, and how relevant it
would be for judgements about other projects of that type. See
Appendix \@ref(follow-up-materials-anecdotes-1) for a screenshot of the display.

#### Procedure

Participants were introduced to the study through the general instructions and
the specific instructions relevant to the condition. They then saw the
allocation task, which included the anecdote analysis and description (for those
not in the statistics condition), and the target projects description. Those
that saw an anecdote were subsequently shown the follow-up questions.
