### Results {#results-anecdotes-1}

#### The Effect of Similarity on Anecdotal Bias

Anecdotal bias was tested by comparing the statistics only condition with both
the high- and low-similarity anecdote and statistics conditions (see
Figure \@ref(fig:plot-anecdotes-1-allocation-combined)). The omnibus one-way
ANOVA of these three conditions was significant,
`r results_anecdotes_1$allocation$condition`. Planned comparisons show that
participants in the statistics only condition allocated a higher percentage of
their budget to the target project compared with participants in the
high-similarity anecdote with statistics condition,
`r results_anecdotes_1$allocation$combined_high_statistics_NA`; but not
the low-similarity anecdote with statistics condition,
`r results_anecdotes_1$allocation$combined_low_statistics_NA`. These findings
provide evidence of anecdotal bias in the high similarity condition only.

(ref:plot-anecdotes-1-allocation-combined) Mean allocation to the target project for the statistics only condition and the two anecdote & statistics conditions. Error bars represent 95% confidence intervals. Raw data are plotted in the background.

```{r plot-anecdotes-1-allocation-combined, fig.cap = "(ref:plot-anecdotes-1-allocation-combined)"}
plot_anecdotes_1$allocation_combined
```

#### The Effect of Enhanced Statistics

The effect of enhanced statistics was investigated by comparing the difference
between similarity conditions between the anecdote & statistics and anecdote &
enhanced statistics conditions (see
Figure \@ref(fig:plot-anecdotes-1-allocation)). The two-way interaction was not
significant, `r results_anecdotes_1$allocation$combined_enhanced_high_low`.
Further, the difference between the anecdote & statistics condition and the
anecdote & enhanced statistics condition (averaged over similarity condition)
was also not significant, `r results_anecdotes_1$allocation$combined_enhanced`.
This suggests that providing participants with information about how to think
statistically is not sufficient to facilitate a focus on statistics.

(ref:plot-anecdotes-1-allocation) Mean allocation to the target project, by similarity and anecdote conditions (excluding the statistics only condition). Error bars represent 95% confidence intervals. Raw data are plotted in the background.

```{r plot-anecdotes-1-allocation, fig.cap = "(ref:plot-anecdotes-1-allocation)"}
plot_anecdotes_1$allocation
```

#### The Effect of Statistics

To identify the influence of statistics on participants' allocations, a two-way
ANOVA of the interactions between similarity (low and high) and anecdote
(anecdote only and anecdote & statistics conditions, excluding the anecdote &
enhanced statistics condition) was conducted (see
Figure \@ref(fig:plot-anecdotes-1-allocation)). The interaction between anecdote
condition and similarity (excluding the enhanced statistics condition) was
significant, `r results_anecdotes_1$allocation$anecdote_combined_high_low`.
Specifically, the difference in allocations between the anecdote only condition
and the anecdote & statistics condition was greater when the anecdote was
similar, `r results_anecdotes_1$allocation$high_anecdote_combined`; compared
with when it was dissimilar,
`r results_anecdotes_1$allocation$low_anecdote_combined`. These findings provide
evidence of partial anecdotal bias in the high similarity condition because the
anecdote & statistics condition was lower than the statistics only condition
(shown above) but higher than the anecdote only condition.

#### Relevance Ratings

Regression analyses were conducted to determine the relationship between
allocations and the follow-up relevance ratings. As shown in
Figure \@ref(fig:plot-anecdotes-1-lm-allocation-relevance-specific-alignment),
the specific relevance ratings interacted with similarity condition,
`r results_anecdotes_1$lm$allocation_relevance_specific_alignment`. It appears
that specific relevance ratings were related to allocations, but only in the
high similarity condition. Further, there were no significant associations with
the general relevance ratings. This suggests that participants applied reasoning
to the connection between the anecdote and the target project as opposed to
simply reacting to the failed project and associating that with that project's
industry.

(ref:plot-anecdotes-1-lm-allocation-relevance-specific-alignment) Mean allocation to the target project, by specific relevance rating and similarity condition. LOESS method was used for smoothing over trials and the shading represents 95% confidence intervals. Raw data are plotted in the background.

```{r plot-anecdotes-1-lm-allocation-relevance-specific-alignment, fig.cap = "(ref:plot-anecdotes-1-lm-allocation-relevance-specific-alignment)"}
plot_anecdotes_1$lm$allocation_relevance_specific_alignment
```

