### Results {#results-anecdotes-1}

#### The effect of similarity on anecdotal bias

Anecdotal bias was tested by comparing the statistics only condition with both
the high and the low similarity anecdote & (not enhanced) statistics conditions.
Figure \@ref(fig:plot-anecdotes-1-allocation-combined) shows these data. The
omnibus one-way ANOVA test of these three conditions was significant,
`r results_anecdotes_1$allocation$condition`. Planned comparisons revealed that
participants allocated more to the target project when seeing only statistics
than when seeing the high similarity anecdote with statistics,
`r results_anecdotes_1$allocation$combined_high_statistics_NA`; but not compared
to seeing the low similarity anecdote with statistics,
`r results_anecdotes_1$allocation$combined_low_statistics_NA`. These findings
provide evidence of anecdotal bias only in the high similarity condition.

(ref:plot-anecdotes-1-allocation-combined) Mean allocation to the target project for the statistics only condition and the two anecdote & statistics conditions. Error bars represent 95% confidence intervals. Raw data are plotted in the background.

```{r plot-anecdotes-1-allocation-combined, fig.cap = "(ref:plot-anecdotes-1-allocation-combined)"}
plot_anecdotes_1$allocation_combined
```

#### The effect of enhanced statistics

The effect of enhanced statistics was investigated by comparing the conditions
in which participants saw an anecdote with statistics to the conditions in which
they saw the same, but with enhanced statistics.
Figure \@ref(fig:plot-anecdotes-1-allocation) shows these data. The two-way
interaction between similarity and the two types of the anecdote & statistics
condition was not significant,
`r results_anecdotes_1$allocation$combined_enhanced_high_low`. Further, the main
effect of anecdote & statistics condition (averaging over similarity) was also
not significant, `r results_anecdotes_1$allocation$combined_enhanced`. This
suggests that providing participants with instructions on how to think
statistically is not sufficient to facilitate a focus on statistics.

(ref:plot-anecdotes-1-allocation) Mean allocation to the target project, by similarity and anecdote conditions (excluding the statistics only condition). Error bars represent 95% confidence intervals. Raw data are plotted in the background.

```{r plot-anecdotes-1-allocation, fig.cap = "(ref:plot-anecdotes-1-allocation)"}
plot_anecdotes_1$allocation
```

#### The effect of statistics

A two-way ANOVA was conducted to investigate the interaction of similarity (low
and high) and anecdote condition (anecdote only and statistics & anecdote,
excluding the anecdote & enhanced statistics condition).
Figure \@ref(fig:plot-anecdotes-1-allocation) shows these data. This identified
the role of statistics in people's allocations. The interaction between anecdote
condition and similarity (excluding the enhanced statistics condition) was
significant, `r results_anecdotes_1$allocation$anecdote_combined_high_low`.
Specifically, the difference between allocations when only seeing an anecdote
and seeing the anecdote with statistics was greater when the anecdote was
similar,
`r results_anecdotes_1$allocation$high_anecdote_combined`; compared to when it
was dissimilar, `r results_anecdotes_1$allocation$low_anecdote_combined`. These
findings provide evidence of partial anecdotal bias in the high similarity
condition, since the anecdote & statistics condition was lower than the
statistics only condition (shown above), but higher than the anecdote only
condition.

#### Relevance ratings

Regression analyses were conducted to determine the relationship between
allocations and the follow-up relevance ratings. As seen in
Figure \@ref(fig:plot-anecdotes-1-lm-allocation-relevance-specific-alignment)
the specific relevance ratings interacted with similarity condition,
`r results_anecdotes_1$lm$allocation_relevance_specific_alignment`. It appears
that specific relevance ratings were related to allocations, but only in the
high similarity condition. Further, there were no significant associations with
the general relevance ratings. This suggests that people were reasoning about
the connection between the anecdote and target, as opposed to simply reacting to
the failed project and associating that with that project's industry.

(ref:plot-anecdotes-1-lm-allocation-relevance-specific-alignment) Mean allocation to the target project, by specific relevance rating and similarity condition. LOESS method was used for smoothing over trials and the shading represents 95% confidence intervals. Raw data are plotted in the background.

```{r plot-anecdotes-1-lm-allocation-relevance-specific-alignment, fig.cap = "(ref:plot-anecdotes-1-lm-allocation-relevance-specific-alignment)"}
plot_anecdotes_1$lm$allocation_relevance_specific_alignment
```

