### Results {#results-anecdotes-1}

#### The effect of similarity on anecdotal bias

Figure \@ref(fig:plot-anecdotes-1-allocation) shows the results for the
allocation data. I tested anecdotal bias by comparing the statistics only
condition with the high and low similarity anecdote + (not enhanced) statistics
conditions. The omnibus one-way ANOVA test of these three conditions was
significant, `r results_anecdotes_1$allocation$condition`. Planned comparisons
revealed that participants allocated more to the target project when seeing only
statistics than when seeing the high similarity anecdote and statistics,
`r results_anecdotes_1$allocation$combined_high_statistics_NA`; but not compared
to seeing the low similarity anecdote and statistics,
`r results_anecdotes_1$allocation$combined_low_statistics_NA`. Therefore, I
found evidence of anecdotal bias only in the high similarity condition.

#### The effect of enhanced statistics

To investigate the effect of enhanced statistics I compared the conditions in
which participants saw both an anecdote and statistics to the conditions in
which they saw the same, but with enhanced statistics. The two-way interaction
between similarity and the two anecdote + statistics conditions was not
significant, `r results_anecdotes_1$allocation$combined_enhanced_high_low`, as
was the main effect of anecdote + statistics condition (averaging over
similarity), `r results_anecdotes_1$allocation$combined_enhanced`. Therefore, I
did not find evidence that providing participants with instructions with how to
think statistically facilitated a focus on statistics.

#### The effect of statistics

A two-way ANOVA was conducted to investigate the interaction of similarity (low
and high) and anecdote conditions (anecdote only, statistics + anecdote,
excluding anecdote + enhanced statistics). This allowed me to identify the role
of statistics. The interaction between anecdote condition and similarity,
excluding the enhanced condition was significant,
`r results_anecdotes_1$allocation$anecdote_combined_high_low`. Specifically, the
difference between allocations when only seeing an anecdote and seeing the
anecdote + statistics was greater when the anecdote was similar,
`r results_anecdotes_1$allocation$high_anecdote_combined`; compared to when it
was dissimilar, `r results_anecdotes_1$allocation$low_anecdote_combined`.
Therefore, I found evidence of "partial" anecdotal bias in the high similarity
condition, since the anecdote + statistics condition was lower than the
statistics only condition, but higher than the anecdote only condition.

(ref:plot-anecdotes-1-allocation) Mean allocation to Project A (the target project). Error bars represent 95% confidence intervals.

```{r plot-anecdotes-1-allocation, fig.cap = "(ref:plot-anecdotes-1-allocation)"}
plot_anecdotes_1$allocation
```

#### Relevance ratings

I conducted regression analyses to determine the relationship between
allocations and the follow-up relevance ratings. As seen in
Figure \@ref(fig:plot-anecdotes-1-lm-allocation-relevance-specific-alignment)
the specific relevance ratings interact with similarity condition,
`r results_anecdotes_1$lm$allocation_relevance_specific_alignment`. It appears
that specific relevance ratings are related to allocations, but only in the high
similarity condition. Further, there were no significant associations with the
general relevance ratings. This suggests that people are reasoning about the
connection between the anecdote and target, as opposed to simply reacting to the
failed project and associating that with the project industry.

(ref:plot-anecdotes-1-lm-allocation-relevance-specific-alignment) Mean allocations to the target project, by specific relevance rating and similarity condition.

```{r plot-anecdotes-1-lm-allocation-relevance-specific-alignment, fig.cap = "(ref:plot-anecdotes-1-lm-allocation-relevance-specific-alignment)"}
plot_anecdotes_1$lm$allocation_relevance_specific_alignment
```

