### Method

#### Participants

`r descriptives_aggregation_1$apa` Table \@ref(tab:condition-allocation-aggregation-1)
shows the between-subjects condition allocation.

```{r condition-allocation-aggregation-1}
descriptives_aggregation_1$condition_allocation_table %>%
  apa_table("Experiment 1 group allocation.")
```

#### Materials

##### Instructions {#instructions-materials-aggregation-1}

Participants were told to imagine that they are executives in a large company
and that they will need to decide about investing in a number of hypothetical
business projects. Appendix \@ref(instructions-materials-aggregation-1-appendix)
shows a screenshot of these instructions.

##### Risky investment task {#task-aggregation-1}

In the risky investment task, participants saw 10 short descriptions of business
projects, and were asked whether they would invest in that project or not. Each
description included the name of the hypothetical business, the amount they
forecast the project to cost, the amount they forecast the project to make, and
probabilities for these forecasts. I constructed these projects to appear
attractive when aggregated, and unattractive when segregated [see @langer2001].
Project values were different for each project, but followed a set of
constraints for each project's EV and the probability of any loss given the
outcome distribution of all 10 projects ($P(loss)$). Further, there was a
constraint on the gambles' loss aversion coefficient ($\lambda$), which is the
ratio of potential gains over the potential losses. The constraints were:
 
1.  $\text{EV} > 0$;

2.  $\lambda < 2.25$; and

3.  $P(loss) < 0.1$.

As such, each project cannot be considered to be a loss under expected value
theory, but also would not be an easy choice for investment, because of the low
$\lambda$ [made to be lower than the median loss aversion coefficient calculated
in @tversky1992]. Further, since people are especially sensitive to loss
probabilities [@zeisberger2020; @kahneman1979], an arbitrarily low $P(loss)$ was
chosen to make investment in the complete set of projects seem attractive. The
actual probability of a loss given the outcome distribution I used was
`r results_aggregation_1$loss_prob`. This was calculated by summing all
probabilities in the Poisson binomial distribution whose outcomes were less than
zero. For comparison, $P(loss)$ =
`r results_aggregation_1$loss_prob_samuelson` for 10 plays of the @samuelson1963
gamble. Figure \@ref(fig:project-choice-aggregation-1) shows an example of a
description of a project in this task.

(ref:project-choice-aggregation-1) Example of a project choice display in Experiment 1. Border added for clarity.

```{r project-choice-aggregation-1, fig.cap = "(ref:project-choice-aggregation-1)"}
here(
  materials_aggregation_1,
  "project_choice_oil-well_separate_similarity_low_1.png"
) %>%
  image_read() %>%
  image_trim() %>%
  image_border(color = "white", geometry = "5x5") %>%
  image_border(color = "black", geometry = "5x5")
```

In the high similarity condition, these project descriptions were all about one
type of project (in this case an oil well project) and were all from the same
business. In the low similarity condition, each project was from a different
industry. In the joint presentation condition, the 10 projects were all
displayed on the one webpage, whereas in the separate presentation condition
each was displayed on a different webpage. Participants in the aware condition
saw the display shown in Figure \@ref(fig:awareness-aware-aggregation-1) before
their separate presentation display. Those in the naive condition simply
proceeded without this message. Note, the financial and probability values were
identical regardless of condition, and the order of each set of 10 projects was
randomised.

(ref:awareness-aware-aggregation-1) The display seen by those in the aware condition of Experiment 1. Border added for clarity.

```{r awareness-aware-aggregation-1, fig.cap = "(ref:awareness-aware-aggregation-1)"}
here(
  materials_aggregation_1,
  "awareness_aware.png"
) %>%
  image_read() %>%
  image_trim() %>%
  image_border(color = "white", geometry = "5x5") %>%
  image_border(color = "black", geometry = "5x5")
```

Although the project descriptions are succinct, and the decisions in the task
are made quickly, they reflect real decisions in businesses in critical ways.
Companies that consider their forecast estimates probabilistically (i.e., do not
simply use the most likely estimate as the only estimate) do in fact frame their
options as likelihoods of certain monetary outcomes.

##### Outcome distribution decision {#outcome-distribution-materials-aggregation-1}

Participants were asked if they would invest in the last 10 projects they saw
and were provided with a graph of the outcome probability distribution of the 10
projects. Appendix \@ref(outcome-distribution-materials-aggregation-1-appendix)
shows this graph. After collecting data I discovered that there was a coding
error in the generation of gambles, which meant that I could not make use of the
outcome distribution decision data. Therefore, the effect of outcome
distribution will not be discussed until [Experiment 2](#aggregation-2), in
which I fixed this issue. Appendix \@ref(outcome-distribution-aggregation-1)
presents an analysis of this data, and describes the coding error and its
implications.

##### Follow-up gambles

Participants were shown four further sets of gambles (11 total) that functioned
to check participant attention and replicate the gambles from @samuelson1963 and
@redelmeier1992. See Appendix \@ref(follow-up-materials-aggregation-1-appendix)
for details.

#### Procedure

Participants read the instructions and completed the risky investment task,
first in the separate presentation condition, and then in the joint condition.
Participants then made the outcome distribution decision, responded to the 11
follow-up gambles.
