### Method

#### Participants

`r descriptives_aggregation_1$apa` Table \@ref(tab:condition-allocation-aggregation-1)
shows the between-subjects condition allocation.

```{r condition-allocation-aggregation-1}
descriptives_aggregation_1$condition_allocation_table %>%
  apa_table("Experiment 1 group allocation.")
```

#### Materials

##### Instructions {#instructions-materials-aggregation-1}

Participants were told to imagine that they are executives in a large company
and that they will need to decide about investing in a number of hypothetical
business projects. The appendix shows a screenshot of these instructions in
Figure \@ref(fig:instructions-materials-aggregation-1).

##### Risky investment task {#task-aggregation-1}

Participants saw 10 short descriptions of business projects, and were asked
whether they would invest in that project or not. Each description included the
name of the hypothetical business, the amount they forecast the project to cost,
the amount the project is forecast to make, and probabilities for these
forecasts. The project values were selected so that the projects appeared
attractive when aggregated and unattractive when segregated [see @langer2001].
These values were different for each project, but followed a set of constraints
for each project's EV and the probability of any loss given the outcome
distribution of all 10 projects ($P(\text{loss}_{aggregated})$). Further, there
was a constraint on the gambles' loss aversion coefficient ($\lambda$), which is
a measure of people's greater sensitivity to losses compared to gains. The
constraints were:

1.  $\text{EV} > 0$;

2.  $\lambda < 2.25$; and

3.  $P(\text{loss}_{aggregated}) < 0.1$.

As such, each project cannot be considered to be a loss in terms of expected
value, but also would not be an easy choice for investment, because of the low
$\lambda$ [made to be lower than the median loss aversion coefficient calculated
in @tversky1992]. Further, since people are especially sensitive to loss
probabilities [@zeisberger2020; @kahneman1979], an arbitrarily low
$P(\text{loss}_{aggregated})$ was chosen to make investment in the complete set
of projects seem attractive. The actual probability of a loss given the outcome
distribution used in the experiment was `r results_aggregation_1$loss_prob`.
This was calculated by summing all probabilities in the Poisson binomial
distribution whose outcomes were less than zero. For comparison,
$P(\text{loss}_{aggregated})$ = `r results_aggregation_1$loss_prob_samuelson`
for 10 plays of the @samuelson1963 gamble. Note that the highest probability of
a loss for any single gamble ($P(\text{loss}_{single})$) was
`r results_aggregation_1$max_probability_negative`.
Figure \@ref(fig:project-choice-aggregation-1) shows an example of a description
of a project in this task.

(ref:project-choice-aggregation-1) Example of a project choice display in Experiment 1. Border added for clarity.

```{r project-choice-aggregation-1, fig.cap = "(ref:project-choice-aggregation-1)"}
file.path(
  materials_aggregation_1,
  "project_choice_oil-well_separate_similarity_low_1.png"
) %>%
  image_read() %>%
  image_trim() %>%
  image_border(color = "white", geometry = "5x5") %>%
  image_border(color = "black", geometry = "5x5")
```

In the high similarity condition, these project descriptions were all about one
type of project (in this case an oil well project) and were all from the same
business. In the low similarity condition, each project was from a different
industry. In the joint presentation condition, the 10 projects were all
displayed on the one webpage, whereas in the separate presentation condition
each was displayed on a different webpage. Participants in the aware condition
saw the display shown in Figure \@ref(fig:awareness-aware-aggregation-1) before
their separate presentation display. Those in the naive condition simply
proceeded without this message. Note, the financial and probability values were
identical regardless of condition, and the order of each set of 10 projects was
randomised.

(ref:awareness-aware-aggregation-1) The display seen by those in the aware condition of Experiment 1. Border added for clarity.

```{r awareness-aware-aggregation-1, fig.cap = "(ref:awareness-aware-aggregation-1)"}
file.path(
  materials_aggregation_1,
  "awareness_aware.png"
) %>%
  image_read() %>%
  image_trim() %>%
  image_border(color = "white", geometry = "5x5") %>%
  image_border(color = "black", geometry = "5x5")
```

Although the project descriptions are succinct, and the decisions in the task
are made quickly, they reflect real decisions in businesses in critical ways.
Companies that consider their forecast estimates probabilistically (i.e., do not
simply use the most likely estimate as the only estimate) do frame their options
as likelihoods of certain monetary outcomes.

##### Outcome distribution decision {#outcome-distribution-materials-aggregation-1}

Participants were asked if they would invest in the last 10 projects they saw
and were provided with a graph of the outcome probability distribution of the 10
projects. The appendix shows this graph in
Figure \@ref(fig:project-choice-aggregated-aggregation-1). A coding error was
discovered after collecting data. This was an error in the generation of
gambles, which meant that the outcome distribution decision data could not be
used. Therefore, the effect of outcome distribution will not be discussed until
Experiment 2, which fixed this issue.
Appendix \@ref(outcome-distribution-aggregation-1) presents an analysis of this
data, and describes the coding error and its implications.

##### Follow-up gambles

Participants were shown four further sets of gambles (11 total) that functioned
to check participant attention and replicate the gambles from @samuelson1963 and
@redelmeier1992. See Appendix \@ref(follow-up-materials-aggregation-1-appendix)
for details.

#### Procedure

Participants read the instructions and completed the risky investment task,
first in the separate presentation condition, and then in the joint condition.
They then made the outcome distribution decision and responded to the 11
follow-up gambles.
