### Results {#results-aggregation-1}

#### Project choice

A three-way ANOVA was conducted to investigate the effects of similarity,
awareness, and presentation on the proportion of participants' decision to
invest in the 10 projects. As seen in
Figure \@ref(fig:plot-aggregation-1-awareness), participants invested more when
they were told that there will be 10 projects, compared to when they were not
told this, `r results_aggregation_1$awareness`. As seen in
Figure \@ref(fig:plot-aggregation-1-presentation), participants invested more
when viewing the projects jointly, compared to when they viewed them separately,
`r results_aggregation_1$presentation`. Although there was no main effect of
similarity, `r results_aggregation_1$similarity`, the interaction between
similarity and presentation was significant,
`r results_aggregation_1$similarity_presentation` (see
Figure \@ref(fig:plot-aggregation-1-similarity-presentation)). Specifically, the
presentation effect seems stronger in the high similarity condition,
`r results_aggregation_1$highjoint_highseparate`, than in the low similarity
condition, `r results_aggregation_1$lowjoint_lowseparate`. These findings
suggest that it is possible to facilitate risk aggregation through subtle choice
bracketing manipulations.

(ref:plot-aggregation-1-awareness) Mean proportions of decisions to invest in each set of 10 projects, by awareness conditions. Error bars represent 95% confidence intervals.

```{r plot-aggregation-1-awareness, fig.cap = "(ref:plot-aggregation-1-awareness)"}
plot_aggregation_1$awareness
```

(ref:plot-aggregation-1-presentation) Mean proportions of decisions to invest in each set of 10 projects, by presentation conditions. Error bars represent 95% confidence intervals.

```{r plot-aggregation-1-presentation, fig.cap = "(ref:plot-aggregation-1-presentation)"}
plot_aggregation_1$presentation
```

(ref:plot-aggregation-1-similarity-presentation) Mean proportions of decisions to invest in each set of 10 projects, by similarity and presentation conditions. Error bars represent 95% confidence intervals.

```{r plot-aggregation-1-similarity-presentation, fig.cap = "(ref:plot-aggregation-1-similarity-presentation)"}
plot_aggregation_1$similarity_presentation
```

#### Trial-by-trial analysis

Exploratory analyses were conducted into the possible effects of the
manipulations on a trial-by trial basis.
Appendix \@ref(trial-by-trial-aggregation-1) shows the data for all conditions.
The key findings are in the separate presentation. As
Figure \@ref(fig:plot-aggregation-1-trials-separate-awareness) shows, in the
separate condition people are more likely to accept projects over the 10 trials,
but this interacts with awareness,
`r results_aggregation_1$trials_separate_awareness$full_result$awareness1_project_order`.
Specifically, the relationship between choice and trial is stronger in the aware
condition,
`r results_aggregation_1$trials_separate_awareness_slope$aware`, than in the
naive condition,
`r results_aggregation_1$trials_separate_awareness_slope$naive`. It seems that
participants that were told the total number of projects became less risk averse
as the experiment proceeded, regardless of the gamble values.

(ref:plot-aggregation-1-trials-separate-awareness) Proportion of project acceptance in the separate presentation condition, by trial, and awareness conditions. LOESS is used for smoothing over trials and the shading represents 95% confidence intervals.

```{r plot-aggregation-1-trials-separate-awareness, fig.cap = "(ref:plot-aggregation-1-trials-separate-awareness)"}
plot_aggregation_1$trials_separate_awareness
```
