### Results {#results-aggregation-1}

#### Project Choice

A three-way analysis of variance (ANOVA) was conducted to investigate the
effects of similarity, awareness, and presentation on the proportion of
participants' decision to invest in the 10 projects. As seen in
Figure \@ref(fig:plot-aggregation-1-awareness), participants invested more when
they were told that there will be 10 projects, compared to when they were not
told this, `r results_aggregation_1$awareness`. As seen in
Figure \@ref(fig:plot-aggregation-1-presentation), participants invested more
when viewing the projects jointly, compared to when they viewed them separately,
`r results_aggregation_1$presentation`. Although there was no main effect of
similarity, `r results_aggregation_1$similarity`, the interaction between
similarity and presentation was significant,
`r results_aggregation_1$similarity_presentation` (see
Figure \@ref(fig:plot-aggregation-1-similarity-presentation)). Specifically, the
presentation effect was stronger in the high similarity condition,
`r results_aggregation_1$highjoint_highseparate`, than in the low similarity
condition, `r results_aggregation_1$lowjoint_lowseparate`. These findings
suggest that it is possible to facilitate risk aggregation with subtle choice
bracketing manipulations.

(ref:plot-aggregation-1-awareness) Mean proportions of decisions to invest in each set of 10 projects, by awareness condition. Error bars represent 95% confidence intervals. Raw data are plotted in the background.

```{r plot-aggregation-1-awareness, fig.cap = "(ref:plot-aggregation-1-awareness)"}
plot_aggregation_1$awareness
```

(ref:plot-aggregation-1-presentation) Mean proportions of decisions to invest in each set of 10 projects, by presentation condition. Error bars represent 95% confidence intervals. Here, however, the intervals are so narrow that they are sometimes obscured by the mean indicators in the plot. Raw data are plotted in the background.

```{r plot-aggregation-1-presentation, fig.cap = "(ref:plot-aggregation-1-presentation)"}
plot_aggregation_1$presentation
```

(ref:plot-aggregation-1-similarity-presentation) Mean proportions of decisions to invest in each set of 10 projects, by similarity and presentation conditions. In mixed factorial designs, error bars cannot be used to make inferences by "eye" across all conditions. Therefore, error bars are not included. Raw data are plotted in the background.

```{r plot-aggregation-1-similarity-presentation, fig.cap = "(ref:plot-aggregation-1-similarity-presentation)"}
plot_aggregation_1$similarity_presentation
```

#### Trial-by-Trial Analysis

Exploratory analyses were conducted into the possible effects of the
manipulations on a trial-by trial basis. The appendix shows the data for all
conditions (see Figure \@ref(fig:plot-aggregation-1-trials)). The key findings
are in the separate presentation. As
Figure \@ref(fig:plot-aggregation-1-trials-separate-awareness) shows, in the
separate condition people are more likely to accept projects over the 10 trials,
but this interacts with awareness,
`r results_aggregation_1$trials_separate_awareness$full_result$awareness1_project_order`.
Specifically, the relationship between choice and trial is stronger in the aware
condition,
`r results_aggregation_1$trials_separate_awareness_slope$aware`, than in the
naive condition,
`r results_aggregation_1$trials_separate_awareness_slope$naive`. It seems that
participants that were told the total number of projects became less risk averse
as the experiment proceeded, regardless of the gamble values.

(ref:plot-aggregation-1-trials-separate-awareness) Proportion of project acceptance in the separate presentation condition, by trial and awareness conditions. LOESS method was used for smoothing over trials and the shading represents 95% confidence intervals.

```{r plot-aggregation-1-trials-separate-awareness, fig.cap = "(ref:plot-aggregation-1-trials-separate-awareness)"}
plot_aggregation_1$trials_separate_awareness
```
