### Results {#results-aggregation-1}

#### Project choice

I conducted a three-way ANOVA to investigate the effects of similarity,
awareness, and presentation on the proportion of participants' decision to
invest in the 10 projects. As seen in
Figure \@ref(fig:plot-aggregation-1-awareness), participants invested more when
they were told that there will be 10 projects, compared to when they were not
told this, `r results_aggregation_1$awareness`. As seen in
Figure \@ref(fig:plot-aggregation-1-presentation), participants invested more
when viewing the projects jointly, compared to when they viewed them separately,
`r results_aggregation_1$presentation`. Although there was no main effect of
similarity, `r results_aggregation_1$similarity`, the interaction between
similarity and presentation was significant,
`r results_aggregation_1$similarity_presentation` (see
Figure \@ref(fig:plot-aggregation-1-similarity-presentation)). Specifically, the
presentation effect seems stronger in the high similarity condition,
`r results_aggregation_1$highjoint_highseparate`, than in the low similarity
condition, `r results_aggregation_1$lowjoint_lowseparate`.

(ref:plot-aggregation-1-awareness) Mean proportions of decisions to invest in each set of 10 projects, by awareness conditions. Error bars represent 95% confidence intervals.

```{r plot-aggregation-1-awareness, fig.cap = "(ref:plot-aggregation-1-awareness)"}
plot_aggregation_1$awareness
```

(ref:plot-aggregation-1-presentation) Mean proportions of decisions to invest in each set of 10 projects, by presentation conditions. Error bars represent 95% confidence intervals.

```{r plot-aggregation-1-presentation, fig.cap = "(ref:plot-aggregation-1-presentation)"}
plot_aggregation_1$presentation
```

(ref:plot-aggregation-1-similarity-presentation) Mean proportions of decisions to invest in each set of 10 projects, by similarity and presentation conditions. Error bars represent 95% confidence intervals.

```{r plot-aggregation-1-similarity-presentation, fig.cap = "(ref:plot-aggregation-1-similarity-presentation)"}
plot_aggregation_1$similarity_presentation
```

#### Trial-by-trial analysis

I conducted exploratory analyses into the possible effects of the manipulations
on a trial-by trial basis. Appendix \@ref(trial-by-trial-aggregation-1) shows
the data for all conditions. The key findings is in the separate presentation.
As Figure \@ref(fig:plot-aggregation-1-trials-separate-awareness) shows, in the
separate condition people are more likely to accept projects over the 10 trials,
but this interacts with awareness,
`r results_aggregation_1$trials_separate_awareness$full_result$awareness1_project_order`.
Specifically, the relationship between choice and trial is significant in the
aware condition,
`r results_aggregation_1$trials_separate_awareness_slope$aware`; but not in the
naive condition,
`r results_aggregation_1$trials_separate_awareness_slope$naive`.

(ref:plot-aggregation-1-trials-separate-awareness) Proportion of project acceptance in the separate presentation condition, by trial, and awareness conditions. LOESS is used for smoothing over trials, and the shading represents 95% confidence intervals.

```{r plot-aggregation-1-trials-separate-awareness, fig.cap = "(ref:plot-aggregation-1-trials-separate-awareness)"}
plot_aggregation_1$trials_separate_awareness
```
