### Method

#### Participants

`r descriptives_alignment_4$apa` Table \@ref(tab:condition-allocation-alignment-4)
shows the between-subjects condition allocation.

```{r condition-allocation-alignment-4}
descriptives_alignment_4$condition_allocation_table %>%
  apa_table("Experiment 5 group allocation.")
```

#### Materials

##### Risky investment task

The only task that was used was the forecasting task used in Experiment 1,
except that it was fixed by adding the relevant percentage intervals that were
left out in Experiment 1, seen in Figure \@ref(fig:forecasting-alignment-4).

(ref:forecasting-alignment-4) An example of the forecasting task in Experiment 5. Border added for clarity.

```{r forecasting-alignment-4, fig.cap = "(ref:forecasting-alignment-4)"}
file.path(
  materials_alignment_4,
  "forecasting.png"
) %>%
  image_read() %>%
  image_trim() %>%
  image_border(color = "white", geometry = "5x5") %>%
  image_border(color = "black", geometry = "5x5")
```

#### Procedure

The procedure was the same as in Experiment 1, except participants only
completed the forecasting task.
