### Results

#### Forecast mean

A mixed factorial ANOVA was conducted to investigate the effects of alignment
and NPV presence on participants' forecasts. As shown in
Figure \@ref(fig:plot-alignment-4-forecast-mean), the alignment $\times$
reliability amount $\times$ NPV interaction was not significant,
`r results_alignment_4$forecast_mean$alignment_reliability_amount_npv_amount`.
Despite this, as in the previous experiments, the interaction between the linear
NPV trend and NPV presence was significant in the high alignment condition,
`r results_alignment_4$forecast_mean$Absent_Present_linear_high`, but not in the
low alignment condition,
`r results_alignment_4$forecast_mean$Absent_Present_linear_low`.

(ref:plot-alignment-4-forecast-mean) Mean forecasts.

```{r plot-alignment-4-forecast-mean, fig.cap = "(ref:plot-alignment-4-forecast-mean)"}
plot_alignment_4$forecast_mean
```

#### Forecast SD {#forecast-sd-alignment-4}

A mixed factorial ANOVA was conducted to investigate the effects of alignment
and NPV presence on participants' forecast SDs. As shown in
Figure \@ref(fig:plot-alignment-4-forecast-sd), there were no significant
differences between alignment conditions,
`r results_alignment_4$forecast_sd$alignment`. The alignment $\times$
reliability amount $\times$ NPV interaction was not significant,
`r results_alignment_4$forecast_sd$alignment_reliability_amount_npv_amount`.
However, as above, the interaction between the linear NPV trend and NPV presence
was significant in the high alignment condition,
`r results_alignment_4$forecast_sd$Absent_Present_linear_high`, but not in the
low alignment condition, `r results_alignment_4$forecast_sd$Absent_Present_linear_low`.

(ref:plot-alignment-4-forecast-sd) Mean forecast SD.

```{r plot-alignment-4-forecast-sd, fig.cap = "(ref:plot-alignment-4-forecast-sd)"}
plot_alignment_4$forecast_sd
```
