### Method

#### Participants

`r descriptives_anecdotes_2$apa` Table \@ref(tab:condition-allocation-anecdotes-2)
shows the between-subjects condition allocation. Similarity and valence were
manipulated within-subjects. Therefore, each participant was in one of two
between-subjects anecdote conditions, and saw five displays (statistics only,
and one for each of the four similarity and valence conditions).
Appendix \@ref(power-analysis-anecdotes-2) describes the power analysis
conducted to arrive at this sample size.

```{r condition-allocation-anecdotes-2}
descriptives_anecdotes_2$condition_allocation_table %>%
  apa_table("Experiment 2 group allocation.")
```

#### Materials

##### Instructions

Participants were shown similar instructions to Experiment 1 (see
Section \@ref(instructions-materials-anecdotes-1)). The general instructions
page included a test of the basic information expressed in the instructions.
This test also functioned as an attention check. As in Experiment 1,
participants also saw instructions that were specific to their condition. These
were shown on the same page as the rest of the project display, above the case
study and target projects. The instructions clarified both that the anecdote was
sampled randomly and that the anecdotes in the pool were all equally similar to
the target project. Appendix \@ref(instructions-materials-anecdotes-2-appendix)
shows the instructions used in Experiment 2.

##### Allocation task {#allocation-anecdotes-2}

As in Experiment 1, the allocation task included a description and analysis of
an anecdote (except for those in the anecdote only condition) and a project
display with a table describing the two target projects.
Figures \@ref(fig:project-allocation-anecdote-valence-negative-similarity-low-materials-anecdotes-2)
and \@ref(fig:project-allocation-target-valence-negative-similarity-low-materials-anecdotes-2)
show the anecdote and target projects, respectively, for the negative valence
low similarity condition.
Figures \@ref(fig:project-allocation-anecdote-valence-positive-similarity-high-materials-anecdotes-2)
and \@ref(fig:project-allocation-target-valence-positive-similarity-high-materials-anecdotes-2)
show the anecdote and target projects, respectively, for the positive valence
high similarity conditions. In the statistics only condition, participants only
saw the target projects display. Appendix \@ref(allocation-anecdotes-2-appendix)
details the counterbalancing and randomisation used in the experiment.

(ref:project-allocation-anecdote-valence-negative-similarity-low-materials-anecdotes-2) An example of the anecdote display in the negative valence, low similarity condition of Experiment 2.

```{r project-allocation-anecdote-valence-negative-similarity-low-materials-anecdotes-2, fig.cap = "(ref:project-allocation-anecdote-valence-negative-similarity-low-materials-anecdotes-2)"}
file.path(
  materials_anecdotes_2,
  "project_allocation_anecdote_valence_negative_similarity_low.png"
) %>%
  image_read() %>%
  image_trim()
```

(ref:project-allocation-target-valence-negative-similarity-low-materials-anecdotes-2) An example of the target projects in the negative valence, low similarity condition of Experiment 2.

```{r project-allocation-target-valence-negative-similarity-low-materials-anecdotes-2, fig.cap = "(ref:project-allocation-target-valence-negative-similarity-low-materials-anecdotes-2)"}
file.path(
  materials_anecdotes_2,
  "project_allocation_target_valence_negative_similarity_low.png"
) %>%
  image_read() %>%
  image_trim()
```

(ref:project-allocation-anecdote-valence-positive-similarity-high-materials-anecdotes-2) An example of an anecdote display in the positive valence, high similarity condition of Experiment 2.

```{r project-allocation-anecdote-valence-positive-similarity-high-materials-anecdotes-2, fig.cap = "(ref:project-allocation-anecdote-valence-positive-similarity-high-materials-anecdotes-2)"}
file.path(
  materials_anecdotes_2,
  "project_allocation_anecdote_valence_positive_similarity_high.png"
) %>%
  image_read() %>%
  image_trim()
```

(ref:project-allocation-target-valence-positive-similarity-high-materials-anecdotes-2) An example of the target projects in the positive valence, high similarity condition of Experiment 2.

```{r project-allocation-target-valence-positive-similarity-high-materials-anecdotes-2, fig.cap = "(ref:project-allocation-target-valence-positive-similarity-high-materials-anecdotes-2)"}
file.path(
  materials_anecdotes_2,
  "project_allocation_target_valence_positive_similarity_high.png"
) %>%
  image_read() %>%
  image_trim()
```

##### Interstitial

Before each display, participants saw an "interstitial" page, whose role was 1.
to introduce the next display, and 2. to provide an attention check (not
required to answer, so can be skipped if the interstitial text isn't read). See
Figure \@ref(fig:interstitial-materials-anecdotes-2) in the appendix for an
example.

##### Follow-up questions

Participants were shown similar follow-up questions as in Experiment 1, except
that here the rating scales were 1-7, instead of 1-6. See
Figure \@ref(fig:follow-up-materials-anecdotes-2) in the appendix for an example
of the follow-up questions display.

#### Procedure

Participants were introduced to the study through the general instructions page.
They then saw five sets of two pages (in randomised order). Each "set" contained
two pages: the allocation task and a follow-up questions page (except for the
anecdotes only condition, in which participants did not see the follow-up
questions page). Each allocation task page contained specific instructions
relevant to the condition, followed by the anecdote analysis and description,
and the target projects description. The only exception was the statistics only
display, for which there was no anecdote description or analysis.
