### Method

#### Participants

`r descriptives_anecdotes_2$apa` Table \@ref(tab:condition-allocation-anecdotes-2)
shows the between-subjects condition allocation. Similarity and valence were
manipulated within-subjects. Therefore, each participant was in one of two
between-subjects anecdote conditions, and saw five displays (statistics only,
and one for each similarity/valence combination).
Appendix \@ref(power-analysis-anecdotes-2) describes the power analysis
conducted to arrive at this sample size.

```{r condition-allocation-anecdotes-2}
descriptives_anecdotes_2$condition_allocation_table %>%
  apa_table("Experiment 2 group allocation.")
```

#### Materials

##### Instructions

Participants were shown similar instructions to [Experiment
1](#instructions-materials-anecdotes-1). I also included a test of basic
instructions understanding that also functioned as an attention check. As in
Experiment 1, participants also saw instructions that were specific to their
condition. These were shown on the same page as the rest of the project display,
above the case study and target projects. One important difference from
Experiment 1 was that I clarified in the instructions text both that the
anecdote was sampled randomly and that the anecdotes in the pool were all
equally similar to the target project.
Appendix \@ref(instructions-materials-anecdotes-2-appendix) shows screenshots of
these web-pages.

##### Allocation task {#allocation-anecdotes-2}

As in Experiment 1, the allocation task included a description and analysis of
an anecdote (except for those in the anecdote only condition) and a project
display with a table describing the two target projects.
Figures \@ref(fig:project-allocation-anecdote-valence-negative-similarity-low-materials-anecdotes-2)
and \@ref(fig:project-allocation-target-valence-negative-similarity-low-materials-anecdotes-2)
show the anecdote and target projects for the negative valence low similarity
condition, respectively.
Figures \@ref(fig:project-allocation-anecdote-valence-positive-similarity-high-materials-anecdotes-2)
and \@ref(fig:project-allocation-target-valence-positive-similarity-high-materials-anecdotes-2)
show the anecdote and target projects for the positive valence high similarity
conditions, respectively. In the statistics only condition, participants only
saw the target projects display. Appendix \@ref(allocation-anecdotes-2-appendix)
details the counterbalancing and randomisation that I used.

(ref:project-allocation-anecdote-valence-negative-similarity-low-materials-anecdotes-2) An example of the anecdote display in the negative valence, low similarity condition of Experiment 2.

```{r project-allocation-anecdote-valence-negative-similarity-low-materials-anecdotes-2, fig.cap = "(ref:project-allocation-anecdote-valence-negative-similarity-low-materials-anecdotes-2)"}
here(
  materials_anecdotes_2,
  "project_allocation_anecdote_valence_negative_similarity_low.png"
) %>%
  image_read() %>%
  image_trim()
```

(ref:project-allocation-target-valence-negative-similarity-low-materials-anecdotes-2) An example of the target projects in the negative valence, low similarity condition of Experiment 2.

```{r project-allocation-target-valence-negative-similarity-low-materials-anecdotes-2, fig.cap = "(ref:project-allocation-target-valence-negative-similarity-low-materials-anecdotes-2)"}
here(
  materials_anecdotes_2,
  "project_allocation_target_valence_negative_similarity_low.png"
) %>%
  image_read() %>%
  image_trim()
```

(ref:project-allocation-anecdote-valence-positive-similarity-high-materials-anecdotes-2) An example of an anecdote display in the positive valence, high similarity condition of Experiment 2.

```{r project-allocation-anecdote-valence-positive-similarity-high-materials-anecdotes-2, fig.cap = "(ref:project-allocation-anecdote-valence-positive-similarity-high-materials-anecdotes-2)"}
here(
  materials_anecdotes_2,
  "project_allocation_anecdote_valence_positive_similarity_high.png"
) %>%
  image_read() %>%
  image_trim()
```

(ref:project-allocation-target-valence-positive-similarity-high-materials-anecdotes-2) An example of the target projects in the positive valence, high similarity condition of Experiment 2.

```{r project-allocation-target-valence-positive-similarity-high-materials-anecdotes-2, fig.cap = "(ref:project-allocation-target-valence-positive-similarity-high-materials-anecdotes-2)"}
here(
  materials_anecdotes_2,
  "project_allocation_target_valence_positive_similarity_high.png"
) %>%
  image_read() %>%
  image_trim()
```

##### Interstitial

Before each display, participants saw an "interstitial" page, whose role was 1.
to introduce the next display, and 2. to provide an attention check (not
required to answer, so can be skipped if the interstitial text isn't read). See
Appendix \@ref(interstitial-materials-anecdotes-2).

##### Follow-up questions

Participants were shown similar follow-up questions as in Experiment 1, except
that here the rating scales were 1-7, instead of 1-6. See
Appendix \@ref(follow-up-materials-anecdotes-2) for an example of a follow-up
display.

#### Procedure

Following ethics and demographics web-pages, participants were introduced to the
study through the general instructions. They then saw five sets of two web-pages
(in randomised order). Each "set" contained two web-pages: the allocation task
and a follow-up questions page (except for the anecdotes only condition, in
which participants did not see the follow-up questions page). Each allocation
task page contained specific instructions relevant to the condition, followed by
the anecdote analysis and description, and the target projects description. The
only exception was the statistics only display, for which there was no anecdote
description or analysis.
