### Method

#### Participants

`r descriptives_anecdotes_2$apa` Table \@ref(tab:condition-allocation-anecdotes-2)
shows the allocation of participants to the different conditions. Anecdote
similarity and valence were manipulated within subjects. Therefore, each
participant was assigned to one of two between-subjects anecdote conditions and
saw five displays (statistics only, and one of each of the four similarity and
valence conditions). Appendix \@ref(power-analysis-anecdotes-2) describes the
power analysis conducted to arrive at this sample size.

```{r condition-allocation-anecdotes-2}
descriptives_anecdotes_2$condition_allocation_table %>%
  apa_table("Experiment 2 group allocation.")
```

#### Materials

##### Instructions

Participants were shown similar instructions to those in Experiment 1 (see
Section \@ref(instructions-materials-anecdotes-1)). The general instructions
page included a test of the basic information expressed in the instructions.
This test also functioned as an attention check. As in Experiment 1,
participants were also shown instructions that were specific to their condition.
These were shown on the same page as the rest of the project display, above the
case study and focal projects. The instructions clarified that the anecdote had
been randomly sampled and that all anecdotes in the pool were equally similar to
the target project. Appendix \@ref(instructions-materials-anecdotes-2-appendix)
shows the instructions used in Experiment 2.

##### Allocation Task {#allocation-anecdotes-2}

As in Experiment 1, the allocation task included a table describing the two
focal projects and (apart from the statistics only condition) a description and
analysis of an anecdote.
Figures \@ref(fig:project-allocation-anecdote-valence-negative-similarity-low-materials-anecdotes-2)
and \@ref(fig:project-allocation-target-valence-negative-similarity-low-materials-anecdotes-2)
show the anecdote and focal projects, respectively, for the negative valence,
low similarity condition.
Figures \@ref(fig:project-allocation-anecdote-valence-positive-similarity-high-materials-anecdotes-2)
and \@ref(fig:project-allocation-target-valence-positive-similarity-high-materials-anecdotes-2)
show the anecdote and focal projects, respectively, for the positive valence,
high similarity conditions. In the statistics only condition, participants were
only shown the focal projects display.
Appendix \@ref(allocation-anecdotes-2-appendix) details the counterbalancing and
randomisation used in the experiment.

(ref:project-allocation-anecdote-valence-negative-similarity-low-materials-anecdotes-2) An example of the anecdote display in the negative valence, low similarity condition of Experiment 2.

```{r project-allocation-anecdote-valence-negative-similarity-low-materials-anecdotes-2, fig.cap = "(ref:project-allocation-anecdote-valence-negative-similarity-low-materials-anecdotes-2)"}
file.path(
  materials_anecdotes_2,
  "project_allocation_anecdote_valence_negative_similarity_low.png"
) %>%
  image_read() %>%
  image_trim()
```

(ref:project-allocation-target-valence-negative-similarity-low-materials-anecdotes-2) An example of the focal projects in the negative valence, low similarity condition of Experiment 2.

```{r project-allocation-target-valence-negative-similarity-low-materials-anecdotes-2, fig.cap = "(ref:project-allocation-target-valence-negative-similarity-low-materials-anecdotes-2)"}
file.path(
  materials_anecdotes_2,
  "project_allocation_target_valence_negative_similarity_low.png"
) %>%
  image_read() %>%
  image_trim()
```

(ref:project-allocation-anecdote-valence-positive-similarity-high-materials-anecdotes-2) An example of an anecdote display in the positive valence, high similarity condition of Experiment 2.

```{r project-allocation-anecdote-valence-positive-similarity-high-materials-anecdotes-2, fig.cap = "(ref:project-allocation-anecdote-valence-positive-similarity-high-materials-anecdotes-2)"}
file.path(
  materials_anecdotes_2,
  "project_allocation_anecdote_valence_positive_similarity_high.png"
) %>%
  image_read() %>%
  image_trim()
```

(ref:project-allocation-target-valence-positive-similarity-high-materials-anecdotes-2) An example of the focal projects in the positive valence, high similarity condition of Experiment 2.

```{r project-allocation-target-valence-positive-similarity-high-materials-anecdotes-2, fig.cap = "(ref:project-allocation-target-valence-positive-similarity-high-materials-anecdotes-2)"}
file.path(
  materials_anecdotes_2,
  "project_allocation_target_valence_positive_similarity_high.png"
) %>%
  image_read() %>%
  image_trim()
```

##### Interstitial Page

Prior to the display, participants were shown an interstitial page, which was
used to (a) introduce the display and (b) check the participant's attention
(given that no input was required, participants could easily skip the page
without reading the text). See
Appendix \@ref(interstitial-materials-anecdotes-2).

##### Follow-up Questions

Participants were shown similar follow-up questions as in Experiment 1, except
that in Experiment 2, rating scales were 1--7 instead of 1--6. See
Appendix \@ref(follow-up-materials-anecdotes-2) for a sample display of the
follow-up questions.

#### Procedure

Participants were introduced to the study via the general instructions page.
They were then shown five sets (presented in a random order) containing two
pages each: a page showing the allocation task and a page with follow-up
questions (except for the anecdotes only condition, in which participants were
not shown the follow-up questions page). Each allocation task page contained
specific instructions relevant to the condition followed by the anecdote
analysis and description, and the description of the two focal projects. The only
exception was the statistics only display, for which there was no anecdote
description or analysis.
