### Results

This section reports only the data relevant to the Experiment 2 hypotheses. See
Appendix \@ref(results-anecdotes-2-appendix) for manipulation check analyses and
analyses of the follow-up rating data.

#### Overall Effect of Manipulations

As shown in Figure \@ref(fig:plot-anecdotes-2-allocation), the similarity
$\times$ valence $\times$ evidence type interaction (excluding the statistics
only condition) was not significant,
`r results_anecdotes_2$allocation$anecdote_between_similarity_valence`. However,
the similarity $\times$ valence interaction was significant,
`r results_anecdotes_2$allocation$similarity_valence`, as was the evidence type
$\times$ valence interaction,
`r results_anecdotes_2$allocation$anecdote_between_valence`. The analyses below
elaborate on the specific hypothesised effects.

(ref:plot-anecdotes-2-allocation) Mean allocation to the target project, by evidence type, similarity, and valence conditions. In mixed factorial designs, error bars cannot be used to make inferences by "eye" across all conditions. Therefore, error bars are not included. Raw data are plotted in the background.

```{r plot-anecdotes-2-allocation, fig.cap = "(ref:plot-anecdotes-2-allocation)"}
plot_anecdotes_2$allocation
```

#### Anecdotal Bias Depends on Anecdote Similarity

To investigate whether anecdotal bias depended on anecdote similarity, the
differences in budget allocations between the statistics only condition and the
two anecdote & statistics conditions (high and low similarity) were calculated.
The values of the statistics only condition were different for each valence
condition to create equivalent comparisons. For the negative valence condition,
participants allocated more money the high-NPV project; while for the positive
valence condition, participants allocated more money to the low-NPV project. As
shown in Figure \@ref(fig:plot-anecdotes-2-allocation-difference), the
similarity $\times$ valence interaction was significant,
`r results_anecdotes_2$allocation_difference$similarity_valence`, as was the
main effect of valence, `r results_anecdotes_2$allocation_difference$valence`.
The main effect of similarity was not significant,
`r results_anecdotes_2$allocation_difference$similarity`.

The effect of the anecdote is represented differently for each valence
condition. As such, the interaction was further analysed by comparing the two
similarity conditions for each valence condition. For negative anecdotes, the
statistical values (e.g., NPV) associated with the target project were higher
than those for the comparison project. If participants were influenced by the
negative anecdote they would therefore allocate less to the target. For negative
anecdotes, a lower allocation to the target project is represented in
Figure \@ref(fig:plot-anecdotes-2-allocation-difference) as a positive
value---the difference in allocation from when the participant did not see an
anecdote. For positive anecdotes, the statistics were lower for the target
project, so an influence of the anecdote is seen as a negative value in
Figure \@ref(fig:plot-anecdotes-2-allocation-difference). The hypothesised
effect of negative anecdote similarity on anecdotal bias would suggest a higher
difference score in high similarity than in low similarity. That is, more
influence of the anecdote when it is similar than when it is dissimilar. For
positive anecdotes a the hypothesised effect would suggest the reverse: a higher
difference score in low similarity than in high similarity.

For negative anecdotes, the allocation difference was greater when the anecdote
was similar to the target project than when it was dissimilar,
`r results_anecdotes_2$allocation_difference$negative_low_high`. For positive
anecdotes, the allocation difference was greater when the anecdote was
dissimilar to the target project than when it was similar,
`r results_anecdotes_2$allocation_difference$positive_low_high`. This provides
evidence that anecdotal bias depends on anecdote similarity for both negative
and positive anecdotes. Participants appeared to be sensitive to the relevance
of the anecdote to the target problem.

(ref:plot-anecdotes-2-allocation-difference) Mean allocation difference between the statistics only condition and the anecdote & statistics condition, by similarity and valence conditions. The horizontal dashed line shows the point in which the two allocations were equivalent. Values above this line show the higher allocation to the target project when participants were shown statistics only compared with when they were shown statistics with an anecdote. Error bars represent 95% confidence intervals, calculated from the within-subjects standard errors using the method from @cousineau2014. Raw data are plotted in the background.

```{r plot-anecdotes-2-allocation-difference, fig.cap = "(ref:plot-anecdotes-2-allocation-difference)"}
plot_anecdotes_2$allocation_difference
```

#### Effect of Statistics

As in Experiment 1, Experiment 2 investigated the extent to which statistical
information influenced participants' allocations. As shown in
Figure \@ref(fig:plot-anecdotes-2-allocation), for negative anecdotes,
participants in the high-similarity anecdote & statistics condition allocated
more to the target project than those in the high-similarity anecdote only
condition,
`r results_anecdotes_2$allocation$similarity_high_anecdote$valence_negative`.
For positive anecdotes, participants in the high-similarity anecdote only
condition allocated more to the target project than those in the high-similarity
anecdote & statistics condition,
`r results_anecdotes_2$allocation$similarity_high_anecdote$valence_positive`.
This provides evidence for the influence of statistics on participants'
allocations for both negative and positive anecdotes.

#### Relevance Ratings

Regression analyses were conducted to determine the relationship between
allocations and the follow-up relevance ratings.
Figure \@ref(fig:plot-anecdotes-2-lm-allocation-relevance-specific-similarity)
shows these data. While the specific relevance ratings for negative anecdotes
showed the same trends as in Experiment 1, the interaction was not significant.
Similarly, the ratings trends for positive anecdotes were as hypothesised, but
their interaction not significant. It appears that specific relevance ratings
were related to allocations, but only in the high similarity condition. Further,
there were no significant associations with the general relevance ratings. This
provides limited evidence that people were reasoning about the connection
between the anecdote and target.

(ref:plot-anecdotes-2-lm-allocation-relevance-specific-similarity) Mean allocation to the target project, by specific relevance rating, similarity condition, and valence condition. LOESS method was used for smoothing over trials and the shading represents 95% confidence intervals. Raw data are plotted in the background.

```{r plot-anecdotes-2-lm-allocation-relevance-specific-similarity, fig.cap = "(ref:plot-anecdotes-2-lm-allocation-relevance-specific-similarity)"}
plot_anecdotes_2$lm$allocation_relevance_specific_similarity
```
