### Results

Only the data that were relevant to the Experiment 2 hypotheses are reported
here. See Appendix \@ref(results-anecdotes-2-appendix) for manipulation check
analyses, and analyses of the follow-up rating data.

#### Overall effect of manipulations

As seen in Figures \@ref(fig:plot-anecdotes-2-allocation-negative)
and \@ref(fig:plot-anecdotes-2-allocation-positive), the similarity $\times$
valence $\times$ anecdote interaction (excluding the statistics only condition)
was not significant,
`r results_anecdotes_2$anecdote_between_similarity_valence`.
However, the similarity $\times$ valence interaction was significant,
`r results_anecdotes_2$similarity_valence` as was the anecdote $\times$ valence
interaction, `r results_anecdotes_2$anecdote_between_valence`. The analyses
below investigated the specific hypothesised effects.

#### Anecdotal bias moderated by similarity

To investigate whether anecdotal bias was moderated by similarity, allocations
were compared between each of the two anecdote & statistics conditions (high and
low similarity) conditions and the statistics only condition. For negative
anecdotes, participants allocated more in the statistics only condition
than in the high similarity anecdote & statistics condition,
`r results_anecdotes_2$combined$valence_negative$similarity_high_statistics_only`.
Participants allocated more when they saw the low similarity anecdote &
statistics display than when they saw the high similarity anecdote & statistics
display,
`r results_anecdotes_2$combined$valence_negative$similarity_high_similarity_low`.
However, the difference between allocations in the statistics only display and
the low similarity anecdote & statistics display was not significant,
`r results_anecdotes_2$combined$valence_negative$similarity_low_statistics_only`.
This provides evidence for the moderation of anecdotal bias by similarity for
negative anecdotes. People seem to be sensitive to the relevance of the anecdote
to the target problem.

For positive anecdotes, allocations were higher in the statistics only condition
than in the low similarity anecdote & statistics condition,
`r results_anecdotes_2$combined$valence_positive$similarity_low_statistics_only`.
Allocations were also higher in the high similarity anecdote & statistics
condition than in the low similarity anecdote & statistics condition,
`r results_anecdotes_2$combined$valence_positive$similarity_high_similarity_low`.
Further, allocations were higher in the statistics only condition than in the
high similarity anecdote & statistics condition,
`r results_anecdotes_2$combined$valence_positive$similarity_high_statistics_only`.
This provides evidence for the moderation of anecdotal bias by similarity for
positive anecdotes as for negative anecdotes.

#### Effect of statistics

As in Experiment 1, Experiment 2 investigated the extent to which the
statistical information influenced participants' allocations. For negative
anecdotes, participants allocated more to the high similarity anecdote &
statistics project than those in the high similarity anecdote only condition,
`r results_anecdotes_2$similarity_high_anecdote$valence_negative`.
When in the positive valence condition, they allocated more to the high
similarity anecdote only condition than those in the high similarity anecdote &
statistics condition,
`r results_anecdotes_2$similarity_high_anecdote$valence_positive`.
This provides evidence for the influence of statistics on participants'
allocations for both negative and positive anecdotes.

(ref:plot-anecdotes-2-allocation-negative) Mean allocation in Experiment 2 for the negative valence condition.

```{r plot-anecdotes-2-allocation-negative, fig.cap = "(ref:plot-anecdotes-2-allocation-negative)"}
plot_anecdotes_2$allocation$negative
```

(ref:plot-anecdotes-2-allocation-positive) Mean allocation in Experiment 2 for the positive valence condition.

```{r plot-anecdotes-2-allocation-positive, fig.cap = "(ref:plot-anecdotes-2-allocation-positive)"}
plot_anecdotes_2$allocation$positive
```
