### Results

Only the data that were relevant to the Experiment 2 hypotheses are reported
here. See Appendix \@ref(results-anecdotes-2-appendix) for manipulation check
analyses, and analyses of the follow-up rating data.

#### Overall effect of manipulations

As seen in Figure \@ref(fig:plot-anecdotes-2-allocation), the similarity
$\times$ valence $\times$ anecdote interaction (excluding the statistics only
condition) was not significant,
`r results_anecdotes_2$allocation$anecdote_between_similarity_valence`. However,
the similarity $\times$ valence interaction was significant,
`r results_anecdotes_2$allocation$similarity_valence`, as was the anecdote
$\times$ valence interaction,
`r results_anecdotes_2$allocation$anecdote_between_valence`. The analyses below investigated the specific hypothesised effects.

(ref:plot-anecdotes-2-allocation) Mean allocation to the target project in Experiment 2. Error bars represent 95% confidence intervals, calculated from the model-based standard error. Note that due to the mixed within-between design, these error bars do not permit inferences "by eye" across repeated-measures factors.

```{r plot-anecdotes-2-allocation, fig.cap = "(ref:plot-anecdotes-2-allocation)"}
plot_anecdotes_2$allocation
```

#### Anecdotal bias moderated by similarity

To investigate whether anecdotal bias was moderated by similarity, a difference
measure was calculated between each participant's allocation to the statistics
only condition and their allocation to each of the two anecdote & statistics
conditions conditions (high and low similarity). The statistics only comparison
value was different for each valence condition to create equivalent comparisons.
For negative valence, the allocation to the high NPV project was used; while for
positive valence, the allocation to the low NPV project was used.
Figure \@ref(fig:plot-anecdotes-2-allocation-difference) shows these data. The
similarity $\times$ valence interaction was significant,
`r results_anecdotes_2$allocation_difference$similarity_valence`, as was the
main effect of valence,
`r results_anecdotes_2$allocation_difference$valence`. The main effect of
similarity was not significant,
`r results_anecdotes_2$allocation_difference$similarity`.

The interaction was analysed further by comparing the two similarity conditions
for each valence condition. For negative anecdotes, the allocation difference
was greater when the anecdote was similar to the target than when it was
dissimilar, `r results_anecdotes_2$allocation_difference$negative_low_high`. For
positive anecdotes, the allocation difference was greater when the anecdote was
dissimilar to the target than when it was similar,
`r results_anecdotes_2$allocation_difference$positive_low_high`. This provides
evidence for the moderation of anecdotal bias by similarity for both negative
and positive anecdotes. People seem to be sensitive to the relevance of the
anecdote to the target problem.

(ref:plot-anecdotes-2-allocation-difference) Mean allocation difference in Experiment 2 between the statistics only condition and the anecdote & statistics condition. The horizontal dashed line shows the point in which the two allocations were equivalent. Values that are higher than this line represent participants that allocated more when seeing only the statistics than when seeing the statistics with an anecdote. Error bars represent 95% confidence intervals, calculated from the within-subjects SEs using the method from @cousineau2014.

```{r plot-anecdotes-2-allocation-difference, fig.cap = "(ref:plot-anecdotes-2-allocation-difference)"}
plot_anecdotes_2$allocation_difference
```

#### Effect of statistics

As in Experiment 1, Experiment 2 investigated the extent to which the
statistical information influenced participants' allocations. As seen in
Figure \@ref(fig:plot-anecdotes-2-allocation), for negative anecdotes,
participants allocated more to the high similarity anecdote & statistics project
than those in the high similarity anecdote only condition,
`r results_anecdotes_2$allocation$similarity_high_anecdote$valence_negative`.
When in the positive valence condition, they allocated more to the high
similarity anecdote only condition than those in the high similarity anecdote &
statistics condition,
`r results_anecdotes_2$allocation$similarity_high_anecdote$valence_positive`.
This provides evidence for the influence of statistics on participants'
allocations for both negative and positive anecdotes.
