### Results

I analysed the allocation data that was relevant to the Experiment 2 hypotheses.
See Appendix \@ref(results-anecdotes-2-appendix) for manipulation check
analyses, and analyses of the follow-up rating data.

#### Overall effect of manipulations

As seen in Figures \@ref(fig:plot-anecdotes-2-allocation-negative)
and \@ref(fig:plot-anecdotes-2-allocation-positive), the similarity $\times$
valence $\times$ anecdote interaction (excluding the statistics-only condition)
was not significant,
`r results_anecdotes_2$anecdote_between_similarity_valence`.
However, the similarity $\times$ valence interaction was significant,
`r results_anecdotes_2$similarity_valence` as was the anecdote $\times$ valence
interaction, `r results_anecdotes_2$anecdote_between_valence`.

#### Anecdotal bias moderated by similarity

To investigate whether anecdotal bias was moderated by similarity, I compared
allocations between the anecdote + statistics high and low similarity conditions and the
statistics-only condition. I found that in the negative valence condition,
participants allocated more in the statistics-only condition than in the
anecdote + statistics high similarity condition,
`r results_anecdotes_2$combined$valence_negative$similarity_high_statistics_only`.
Participants in the anecdote + statistics low similarity allocated more than when they saw
the anecdote + statistics high similarity display,
`r results_anecdotes_2$combined$valence_negative$similarity_high_similarity_low`.
However, the difference between responses to the statistics-only projects and
the anecdote + statistics low similarity projects was not significant,
`r results_anecdotes_2$combined$valence_negative$similarity_low_statistics_only`
This provides evidence for the moderation of anecdotal bias by similarity for
negative anecdotes.

In the positive valence condition, allocations were higher in the statistics-only
condition than in the anecdote + statistics low similarity condition,
`r results_anecdotes_2$combined$valence_positive$similarity_low_statistics_only`.
Allocations were also higher in the anecdote + statistics high similarity condition than in
the anecdote + statistics low similarity condition,
`r results_anecdotes_2$combined$valence_positive$similarity_high_similarity_low`.
Further, allocations were higher in the statistics-only condition than in the
anecdote + statistics high similarity condition,
`r results_anecdotes_2$combined$valence_positive$similarity_high_statistics_only`.
This provides evidence for the moderation of anecdotal bias by similarity for
positive anecdotes.

#### Effect of statistics

As in Experiment 1, I investigated the extent to which the statistical
information influenced participants' allocations. When in the negative valence
condition, participants allocated more to the high similarity anecdote +
statistics project than those in the high similarity anecdote-only condition,
`r results_anecdotes_2$similarity_high_anecdote$valence_negative`.
When in the positive valence condition, they allocated more to the high similarity
anecdote-only condition than those in the high similarity anecdote + statistics condition,
`r results_anecdotes_2$similarity_high_anecdote$valence_positive`. This provides
evidence for the influence of statistics on participants' allocations for both
negative and positive anecdotes.

(ref:plot-anecdotes-2-allocation-negative) Mean allocation in Experiment 2 for the positive valence condition.

```{r plot-anecdotes-2-allocation-negative, fig.cap = "(ref:plot-anecdotes-2-allocation-negative)"}
plot_anecdotes_2$allocation$negative
```

(ref:plot-anecdotes-2-allocation-positive) Mean allocation in Experiment 2 for the positive valence condition.

```{r plot-anecdotes-2-allocation-positive, fig.cap = "(ref:plot-anecdotes-2-allocation-positive)"}
plot_anecdotes_2$allocation$positive
```
