### Results

Only the data that were relevant to the Experiment 2 hypotheses are reported
here. See Appendix \@ref(results-anecdotes-2-appendix) for manipulation check
analyses, and analyses of the follow-up rating data.

#### Overall effect of manipulations

As seen in Figure \@ref(fig:plot-anecdotes-2-allocation), the similarity
$\times$ valence $\times$ anecdote interaction (excluding the statistics only
condition) was not significant,
`r results_anecdotes_2$allocation$anecdote_between_similarity_valence`. However,
the similarity $\times$ valence interaction was significant,
`r results_anecdotes_2$allocation$similarity_valence`, as was the anecdote
$\times$ valence interaction,
`r results_anecdotes_2$allocation$anecdote_between_valence`. The analyses below investigated the specific hypothesised effects.

(ref:plot-anecdotes-2-allocation) Mean allocation to the target project, by similarity and valence conditions. In mixed factorial designs, error bars cannot be used to make inferences by "eye" across all conditions. Therefore, error bars are not included. Raw data are plotted in the background.

```{r plot-anecdotes-2-allocation, fig.cap = "(ref:plot-anecdotes-2-allocation)"}
plot_anecdotes_2$allocation
```

#### Anecdotal bias moderated by similarity

To investigate whether anecdotal bias was moderated by similarity, a difference
measure was calculated between each participant's allocation to the statistics
only condition and their allocation to each of the two anecdote & statistics
conditions (high and low similarity). The statistics only comparison value was
different for each valence condition to create equivalent comparisons. For
negative valence, the allocation to the high NPV project was used; while for
positive valence, the allocation to the low NPV project was used.
Figure \@ref(fig:plot-anecdotes-2-allocation-difference) shows these data. The
similarity $\times$ valence interaction was significant,
`r results_anecdotes_2$allocation_difference$similarity_valence`, as was the
main effect of valence,
`r results_anecdotes_2$allocation_difference$valence`. The main effect of
similarity was not significant,
`r results_anecdotes_2$allocation_difference$similarity`.

The effect of the anecdote is represented differently for each valence
condition. As such, the interaction was analysed further by comparing the two
similarity conditions for each valence condition. For negative anecdotes, the
statistical values (e.g., NPV) associated with the target project were higher
than those for the comparison project. If participants were influenced by the
negative anecdote they would therefore allocate less to the target. For negative
anecdotes, a lower allocation to the target project is represented in
Figure \@ref(fig:plot-anecdotes-2-allocation-difference) as a positive
value---the difference in allocation from when the participant did not see an
anecdote. For positive anecdotes, the statistics were lower for the target
project, so an influence of the anecdote is seen as a negative value in
Figure \@ref(fig:plot-anecdotes-2-allocation-difference). A moderation of the
anecdotal bias effect by similarity for negative anecdotes would suggest a
higher difference score in high similarity than in low similarity. That is, more
influence of the anecdote when it is similar than when it is dissimilar. For
positive anecdotes a moderation would suggest the reverse: a higher difference
score in low similarity than in high similarity.

For negative anecdotes, the allocation difference
was greater when the anecdote was similar to the target than when it was
dissimilar, `r results_anecdotes_2$allocation_difference$negative_low_high`. For
positive anecdotes, the allocation difference was greater when the anecdote was
dissimilar to the target than when it was similar,
`r results_anecdotes_2$allocation_difference$positive_low_high`. This provides
evidence for the moderation of anecdotal bias by similarity for both negative
and positive anecdotes. People seem to be sensitive to the relevance of the
anecdote to the target problem.

(ref:plot-anecdotes-2-allocation-difference) Mean allocation difference between the statistics only condition and the anecdote & statistics condition, by similarity and valence conditions. The horizontal dashed line shows the point in which the two allocations were equivalent. Values that are higher than this line represent participants that allocated more when seeing only the statistics than when seeing the statistics with an anecdote. Error bars represent 95% confidence intervals, calculated from the within-subjects SEs using the method from @cousineau2014. Raw data are plotted in the background.

```{r plot-anecdotes-2-allocation-difference, fig.cap = "(ref:plot-anecdotes-2-allocation-difference)"}
plot_anecdotes_2$allocation_difference
```

#### Effect of statistics

As in Experiment 1, Experiment 2 investigated the extent to which the
statistical information influenced participants' allocations. As seen in
Figure \@ref(fig:plot-anecdotes-2-allocation), for negative anecdotes,
participants allocated more to the high similarity anecdote & statistics project
than those in the high similarity anecdote only condition,
`r results_anecdotes_2$allocation$similarity_high_anecdote$valence_negative`.
When in the positive valence condition, they allocated more to the high
similarity anecdote only condition than those in the high similarity anecdote &
statistics condition,
`r results_anecdotes_2$allocation$similarity_high_anecdote$valence_positive`.
This provides evidence for the influence of statistics on participants'
allocations for both negative and positive anecdotes.

#### Relevance ratings

Regression analyses were conducted to determine the relationship between
allocations and the follow-up relevance ratings.
Figure \@ref(fig:plot-anecdotes-2-lm-allocation-relevance-specific-similarity)
shows these data. While the specific relevance ratings for negative anecdotes
showed the same trends as in Experiment 1, the interaction was not significant.
Similarly, the ratings trends for positive anecdotes were as hypothesised, but
their interaction not significant. It appears that specific relevance ratings
were related to allocations, but only in the high similarity condition. Further,
there were no significant associations with the general relevance ratings. This
provides limited evidence that people were reasoning about the connection
between the anecdote and target.

(ref:plot-anecdotes-2-lm-allocation-relevance-specific-similarity) Mean allocation to the target project, by specific relevance rating, similarity condition, and valence condition. LOESS method was used for smoothing over trials and the shading represents 95% confidence intervals. Raw data are plotted in the background.

```{r plot-anecdotes-2-lm-allocation-relevance-specific-similarity, fig.cap = "(ref:plot-anecdotes-2-lm-allocation-relevance-specific-similarity)"}
plot_anecdotes_2$lm$allocation_relevance_specific_similarity
```
