### Method

#### Participants

`r descriptives_aggregation_4$apa` Table \@ref(tab:condition-allocation-aggregation-4)
shows the allocation of participants to the different conditions.

```{r condition-allocation-aggregation-4}
descriptives_aggregation_4$condition_allocation_table %>%
  apa_table("Experiment 4 group allocation.")
```

#### Materials

##### Instructions

Participants were shown similar instructions to Experiment 1 (see
Section \@ref(instructions-materials-aggregation-1)), except that the awareness
manipulation was incorporated into the text. Participants in the naive condition
saw the instructions in Figure \@ref(fig:instructions-naive-aggregation-4), and
those in the aware condition saw the instructions in
Figure \@ref(fig:instructions-aware-aggregation-4).

(ref:instructions-naive-aggregation-4) Instructions for those in the naive condition of Experiment 4.

```{r instructions-naive-aggregation-4, fig.cap = "(ref:instructions-naive-aggregation-4)"}
file.path(
  materials_aggregation_4,
  "instructions2_naive.png"
) %>%
  image_read() %>%
  image_trim() %>%
  image_border(color = "white", geometry = "5x5") %>%
  image_border(color = "black", geometry = "5x5")
```

(ref:instructions-aware-aggregation-4) Instructions for those in the aware condition of Experiment 4.

```{r instructions-aware-aggregation-4, fig.cap = "(ref:instructions-aware-aggregation-4)"}
file.path(
  materials_aggregation_4,
  "instructions2_aware.png"
) %>%
  image_read() %>%
  image_trim() %>%
  image_border(color = "white", geometry = "5x5") %>%
  image_border(color = "black", geometry = "5x5")
```

##### Risky Investment Task

Participants saw similar displays to those in Experiment 3 (see
Section \@ref(task-aggregation-3)). However, here participants viewed 20
projects, so while the gamble constrains explained above were still applied, the
actual gamble values were different. Further, those in the aware condition saw
an added sentence that identified the number of the project they were currently
considering in the context of the total 20. See
Figure \@ref(fig:project-choice-aggregation-4) for an example. Those in the
naive condition saw the same display without this sentence.

(ref:project-choice-aggregation-4) An example of a project display in Experiment 4.

```{r project-choice-aggregation-4, fig.cap = "(ref:project-choice-aggregation-4)"}
file.path(
  materials_aggregation_4,
  "project_choice_aware_oil-well_1.png"
) %>%
  image_read() %>%
  image_trim() %>%
  image_border(color = "white", geometry = "5x5") %>%
  image_border(color = "black", geometry = "5x5")
```

##### Follow-up

The follow-up questions were identical to those in Experiment 3 (see
Section \@ref(follow-up-aggregation-3)), except that the portfolio number
question identified the number of projects they saw as 20.

#### Procedure

Participants read the instructions and completed the risky investment task in
their respective conditions. After seeing the individual projects, participants
were then asked the four follow-up questions.
