### Results

#### Project investment

The project investment data was analysed as in
[Experiment 2](#results-aggregation-2). 
Figures \@ref(fig:plot-aggregation-4-choice)
and \@ref(fig:plot-aggregation-4-proportion) show the choice and proportion
data, respectively. The difference between
awareness conditions was not significant, both in the logistic regression
`r results_aggregation_4$choice$full_result[[2]]`, and in the t-test,
`r results_aggregation_4$proportion`.

(ref:plot-aggregation-4-choice) Mean project acceptance for the awareness effect.

```{r plot-aggregation-4-choice, fig.cap = "(ref:plot-aggregation-4-choice)"}
plot_aggregation_4$choice_binary
```

(ref:plot-aggregation-4-proportion) Mean proportion of project acceptance for the awareness effect.

```{r plot-aggregation-4-proportion, fig.cap = "(ref:plot-aggregation-4-proportion)"}
plot_aggregation_4$choice_proportion
```

Further, Figure \@ref(fig:plot-aggregation-4-choice-trials) shows the choice
data as a function of the order of the project in the sequence. As
Table \@ref(tab:awareness-project-order) shows, there were no main effects or
interactions.

(ref:plot-aggregation-4-choice-trials) Mean project acceptance by awareness and trial.

```{r plot-aggregation-4-choice-trials, fig.cap = "(ref:plot-aggregation-4-choice-trials)"}
plot_aggregation_4$choice_trials
```

```{r awareness-project-order}
results_aggregation_4$awareness_project_order$table %>%
  apa_table("Logistic regression table of project acceptance by awareness and trial.")
```

#### Follow-up

##### Project expectation

We asked participants how many projects they expected to see. 
Figure \@ref(fig:plot-aggregation-4-project-expectation) shows that those in
the aware condition reportedly expect to see more,
`r results_aggregation_4$project_expectation`. However, this is likely to be due to
the fact that they were told how many projects there were.

(ref:plot-aggregation-4-project-expectation) Number of projects participants expected to see, by awareness.

```{r plot-aggregation-4-project-expectation, fig.cap = "(ref:plot-aggregation-4-project-expectation)"}
plot_aggregation_4$project_expectation
```

##### Project number

We asked participants how many projects they think they saw.
Figure \@ref(fig:plot-aggregation-4-project-number) shows that overall people
correctly estimate the number of projects, with higher accuracy for those in the
aware condition.

(ref:plot-aggregation-4-project-number) Number of projects participants reported seeing, by awareness.

```{r plot-aggregation-4-project-number, fig.cap = "(ref:plot-aggregation-4-project-number)"}
plot_aggregation_4$project_number
```

##### Portfolio choice - binary

Participants were then asked if they would rather invest in all or none of the
projects. As Figure \@ref(fig:plot-aggregation-4-portfolio-binary), there was no
significant difference between awareness conditions in wanting to invest
in all of the projects,
`r results_aggregation_4$portfolio_binary$full_result[[2]]`.

(ref:plot-aggregation-4-portfolio-binary) Mean choice of investing in all 20 projects for the awareness effect. 
```{r plot-aggregation-4-portfolio-binary, fig.cap = "(ref:plot-aggregation-4-portfolio-binary)"}
plot_aggregation_4$portfolio_binary
```

##### Portfolio choice - number

Subsequently, we asked participants how many projects they would invest in out
of the 20 that they saw. As
Figure \@ref(fig:plot-aggregation-4-portfolio-number) shows, the difference
between awareness conditions was not significant,
`r results_aggregation_4$portfolio_number`.

(ref:plot-aggregation-4-portfolio-number) Mean number of projects chosen in the follow-up for the awareness effect.

```{r plot-aggregation-4-portfolio-number, fig.cap = "(ref:plot-aggregation-4-portfolio-number)"}
plot_aggregation_4$portfolio_number
```

#### Gambles

Figures \@ref(fig:plot-aggregation-4-trials)
and \@ref(fig:plot-aggregation-4-gamble-values) show the
overall people seemed to prefer gambles with higher probabilities of gain,
sometimes regardless of expected value or value of the gain.

(ref:plot-aggregation-4-trials) Mean project acceptance for the 20 gambles. The format of the labels indicate: (gain probability, gain value; loss probability, loss value).

```{r plot-aggregation-4-trials, fig.cap = "(ref:plot-aggregation-4-trials)"}
plot_aggregation_4$trials
```

(ref:plot-aggregation-4-gamble-values) Mean project acceptance for the gambles' expected value, positive probability, and positive outcome.

```{r plot-aggregation-4-gamble-values, fig.cap = "(ref:plot-aggregation-4-gamble-values)"}
plot_aggregation_4$gamble_values
```
